### 2013-09-19 latex-template.tex
Add notation.

\documentclass[12pt]{amsart}   % LaTeX with AMS style; 12 point for old eyes

\usepackage{amssymb,amsfonts}   % For better support of math
\usepackage{graphicx}	        % Enable for eps and pdf figures, if they occur
\usepackage{hyperref}           % Enable embedded hyperlinks.

% Commands to force sequential numbering:

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{examples}[theorem]{Examples}
\newtheorem{remarks}[theorem]{Remarks}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{conjecture}[theorem]{Conjecture}

\begin{document}

\title[The 18.821 report]{The 18.821 Mathematics Project Lab Report 
[Replace this with your own short descriptive title!]} 
% the first [...] gives a brief version of the title, which is long!

\author{Jonathan Allen, John Wang}
\date{\today}              % or an actual date

\newcommand{\C}{\mathbb C} % blackboard bold , for ``complex,'' etc
\newcommand{\R}{\mathbb R} 
\newcommand{\Z}{\mathbb Z}
\newcommand{\Q}{\mathbb Q}
\newcommand{\N}{\mathbb N}

\begin{abstract}
This is a \LaTeX\ template for 18.821, which you can use for your
own reports. 
\end{abstract}

\maketitle

\section{Introduction\label{sec:intro}}

%Your introduction section should convey the motivation and main point of the project. Avoid generalized philosophical or
%historical remarks (``Ever since the beginning of human culture \dots''), or lists of known results. Technical definitions are better kept out of the introduction. The aim should be to get the right
%informal picture into the reader's head. This may take some effort.

This brief document shows some examples of the use of \LaTeX\  
and indicates some special features of the Math Lab report style.
The \href{http://stellar.mit.edu/S/course/18/sp13/18.821/}{course website}
contains links to several \LaTeX\ manuals.

End the introduction by describing the contents of the paper section by section, and which
team member(s) wrote each of them. For instance, Section \ref{sec:bibliography} discusses referencing, and is written by P. Gurps.

\section{\LaTeX\ Examples\label{sec:examples}}

Here are some ways of producing mathematical symbols. Some are pre-defined either in \LaTeX\ or in the AMS package which
this document loads. For instance, sums and integrals, $\sum_{i=1}^n 1 = n$, $\int_0^n x \, dx = n^2/2$.
We've defined a few other symbols at the start of the document, for instance $\N,\Q,\Z,\R$. You can make marginal notes for yourself or your co-authors like this:
\marginpar{Unfinished here?}

If you want to typeset equations, there are many choices, with or without numbering:
\[
\int_0^1 x\, dx = 1/2,
\]
or
$$
\sum_{i = 1}^\infty i = -\frac{1}{12}
$$
or
\begin{equation*}
1 - 1 + 1 - \cdots = \frac{1}{2}.
\end{equation*}
If you want a number for an equation, do it like this:
\begin{equation}\label{eq:first-equation}
\lim_{n \to \infty}\, \sum_{k = 1}^n \frac{1}{k^2} = \frac{\pi}{6}.
\end{equation} %
This can then be referred to as \eqref{eq:first-equation}, which is much easier than
keeping track of numbers by hand. To group several equations, aligning on the $=$ sign, do
it like this:
\begin{align*}
x_1 + 2x_2 + 3x_3 &= 7 \\ y &= mx + c \\ &= 4x - 9.
\end{align*}

You can easily embed hyperlinks into the output .pdf document: 
\href{http://stellar.mit.edu/S/course/18/sp13/18.821/}{click here} for example.

\section{Images}
Figure \ref{fig:2} is an example of a .pdf image put into a floating environment, which means LaTeX will draw it wherever there's enough space left in your manuscript.  %To draw images which can be saved as .pdf, use your favorite graphics program such as (under Linux or Unix) xfig or gimp.
%\begin{figure}
%\begin{center}
%\includegraphics[width=4in]{spiral.eps}
%\end{center}
%\vspace{-.2in} % corrects bad spacing
%\caption{My first .eps figure.\label{fig:2}}
%\end{figure}
Look at the .tex original to see how to insert a figure like this. 
%Alternatively, you can insert .pdf files using the same syntax:

\begin{figure}
\begin{center}
%\includegraphics[width=4in]{spiral.pdf}
\end{center}
\vspace*{-.5in} % corrects bad spacing
\caption{My first .pdf figure.\label{fig:2}}
\end{figure}

%An advantage of using .pdf figures is that you can produce .pdf files 
%from latex in one step, using the command {\tt pdflatex}, rather than
%the three-step process described below.

\section{Theorems and such}

An example of a ``conjecture environment'' is given below, in Conjecture
\ref{conj:vaught}.  Theorems, lemmas, propositions, definitions, and
such all use the same command with the appropriate name changed.
In fact, if you look at the top of this .tex file, you can see where we've defined
these environments.

\begin{conjecture}[Vaught's Conjecture]\label{conj:vaught}
Let $T$ be a countable complete theory.  If $T$ has fewer than
$2^{\aleph_0}$ many countable models (up to isomorphism), then it has
countably many countable models.
\end{conjecture}

\begin{theorem}
When it rains it pours.
\end{theorem}

\proof Well, yes. \qed

\section{Filetypes used by LaTeX \label{sec:files}}

You will write your text as a .tex file using any text editor (though WYSIWYG 
editors are troublesome).
Traditionally one then runs \LaTeX\ and obtains a .dvi file, which
can be viewed on the screen using a dvi viewer. To include images, and then prepare the file for printing or submission,
one typically translates the .dvi into either .ps (Postscript) or .pdf (Adobe PDF).

Your report will be submitted to Stellar as a .pdf document.
The {\tt pdflatex} command
produces a .pdf file directly from a .tex file. This command works well with 
included .pdf files, but does not handle .eps files. 
An .eps file can be converted to a .pdf file by viewing it 
and saving as a .pdf file, or by {\tt ps2pdf filename.eps}, which produces
{\tt filename.pdf}.
Under MikTeX with WinEdt, all necessary commands will appear under ``Accessories'' in the WinEdt menu.

%Under Linux or Unix for example, the commands are
%\begin{quote}
%{\tt latex filename.tex}
%\end{quote}
%which produces {\tt filename.dvi}, and then
%\begin{quote}
%{\tt dvips -f filename.dvi > filename.ps}
%\end{quote}
%followed by
%\begin{quote}
%{{\tt ps2pdf filename.ps}.}
%\end{quote}
%If the file does not contain embedded Postscript images,
%.pdf output can be obtained directly using
%\begin{quote}
%{{\tt pdflatex filename.tex}.}
%\end{quote}

Finally, Matlab can be made to produce .eps files by typing
\begin{quote}
{\tt print -deps filename}
\end{quote}
at the prompt.

\section{Quoting sources\label{sec:bibliography}}

In your work, keep notes of the literature you've used, including websites. Cite the references you use; failure to do so constitutes plagiarism. Every bibliography item should be referenced somewhere in the paper.
Quote as precisely as possible: \cite[pages 76--78]{gurps} rather than \cite{gurps}. \cite{wildlife} was a useful background reference, too.

\bibliographystyle{plain}
\begin{thebibliography}{9}
\bibitem{gurps}
Gurps, P., Care and feeding of maths professors. Cambridge Univ. Press, 2008.
\bibitem{wildlife}
Burps, X. Terrors and errors of project lab. {\em Journal of Wildlife and Conservation} 21 (2008), 112--134.
\end{thebibliography}

\section*{Appendix}
Appendices are useful for putting in code or data.

\end{document}

From Spring 2011 or before; revised by Miller, Spring 2013.

### 2013-09-23 paper.tex
Begining to write some definitions.
Most of these definitions concern paths.

\documentclass[12pt]{amsart}   % LaTeX with AMS style; 12 point for old eyes

\usepackage{amsmath,amssymb,amsfonts}   % For better support of math
\usepackage{graphicx}	        % Enable for eps and pdf figures, if they occur
\usepackage{hyperref} % Enable embedded hyperlinks.
\hypersetup{
	hidelinks, colorlinks, linkcolor=black, citecolor=black, urlcolor=red
}

% Commands to force sequential numbering:

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{examples}[theorem]{Examples}
\newtheorem{remarks}[theorem]{Remarks}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{conjecture}[theorem]{Conjecture}

% Define abs norm, paren, bracket, cbracket, and innerproduct
\usepackage{mathtools}
\DeclarePairedDelimiter\tempabs{\lvert}{\rvert}
\DeclarePairedDelimiter\tempnorm{\lVert}{\rVert}
\DeclarePairedDelimiter\tempinnerproduct{\langle}{\rangle}
\DeclarePairedDelimiter\tempparen{(}{)}
\DeclarePairedDelimiter\tempbracket{[}{]}
\DeclarePairedDelimiter\tempcbracket{\{}{\}}

% Swap * functionality
\makeatletter
\def\abs{\@ifstar{\tempabs}{\tempabs*}}
\def\norm{\@ifstar{\tempnorm}{\tempnorm*}}
\def\innerproduct{\@ifstar{\tempinnerproduct}{\tempinnerproduct*}}
\def\paren{\@ifstar{\tempparen}{\tempparen*}}
\def\bracket{\@ifstar{\tempbracket}{\tempbracket*}}
\def\cbracket{\@ifstar{\tempcbracket}{\tempcbracket*}}
\makeatother

\begin{document}

\title[The 18.821 report]{The 18.821 Mathematics Project Lab Report 
[Proofs]} 
% the first [...] gives a brief version of the title, which is long!

\author{Jonathan Allen}
\date{\today}              % or an actual date

\newcommand{\C}{\mathbb C} % blackboard bold , for ``complex,'' etc
\newcommand{\R}{\mathbb R} 
\newcommand{\Z}{\mathbb Z}
\newcommand{\Q}{\mathbb Q}
\newcommand{\N}{\mathbb N}

\maketitle

\section{Theorems}

\subsection{Notation\label{sec:notation}}

\begin{description}
    \item[$t$] Time
    \item[$l$] Path length
    \item[$s$] Speed
    \item[$a_t$] Tangential acceleration
    \item[$a_c$] Centripetal acceleration
    \item[$\vec{x}$] Position
    \item[$\vec{v}$] Velocity
    \item[$\vec{a}$] Acceleration
\end{description}

\section{Coordinates}

\subsection{Scalar Calculus}

\begin{align}
s& = \frac{dl}{dt}\\
%
a_t& = \frac{ds}{dt}\\
\end{align}

\subsection{Vector Calculus}

\begin{align}
\boldsymbol{x}& = r \boldsymbol{\hat{r}}\\
%
\boldsymbol{\vec{v}}& = \dot{r} \boldsymbol{\hat{r}} + r \dot{\phi} \boldsymbol{\hat{\phi}}\\
%
\boldsymbol{\vec{a}}& = \paren{\ddot{r} - r \dot{\phi}^2} \boldsymbol{\hat{r}} + \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}} \boldsymbol{\hat{\phi}}
\end{align}

\subsection{Relations}

\begin{align}
l& = \int_{t=0}^{T} \norm{\boldsymbol{\vec{v}} \, } \; dt\\
%
s& = \boldsymbol{\vec{v}}\\
%
a_t& = \norm{\boldsymbol{\vec{a}}\,} \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}\,}}
\end{align}

\section{Traveling Between Points}

\begin{definition}
  A path $\gamma: \mathrm{R} \to \mathrm{R}^2$ is a function which maps some time $t$ to a position $\gamma(t) \in \mathrm{R}^2$. The path is defined from time $t = 0$ until the end time of the path, denoted as $T_{f}(\gamma)$.
\end{definition}

\begin{definition}
  A valid path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$ and conditions $\mathrm{C}$ is some path which at all times $t$ such that $0 \leq t \leq T_f(\gamma)$, all conditions in $\mathrm{C}$ are satisfied.
\end{definition}

\begin{definition}
  A valid targetted path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$, conditions $\mathrm{C}$, starting point $\vec{x_1}$, and ending point $\vec{x_2}$ is a valid path where $\gamma(t) = \vec{x_1}$ and $\gamma(T_f(\gamma)) = \vec{x_2}$. In other words, it is a valid path which starts at $\vec{x_1}$ and ends at $\vec{x_2}$.
\end{definition}

\begin{definition}
  A fastest path $\hat{\gamma}: \mathrm{R} \to \mathrm{R}^2$ for a particular point mass $p$, a starting point $\vec{x_1}$, a destination point $\vec{x_2}$, and some set of conditions $\mathrm{C}$ is a valid targetted path $\hat{\gamma}$ such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid targetted paths $\gamma$ with the same $p$, $\vec{x_1}$, $\vec{x_2}$, and $\mathrm{C}$.
\end{definition}

\begin{theorem}
  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a point mass $p$ whose initial position is $(x_1, y_1)$ which moves with tangential acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
  \begin{eqnarray}
    y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
  \end{eqnarray}
\end{theorem}
\proof Let's transform the problem. We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis. In this new coordinate system, we have transformed the following:
\begin{eqnarray}
  (x_1, y_1) &\to& (0,0) \\
  (x_2, y_2) &\to& (x_2', 0)
\end{eqnarray}

For convenience of notation, we will now refer to $x_2'$ as $x_2$.
\qed

\begin{corollary}
  The fastest path between two points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ is unique.
\end{corollary}

\bibliographystyle{plain}
\begin{thebibliography}{9}
\bibitem{wiki_pcoords}
\url{http://en.wikipedia.org/wiki/Polar_coordinate_system}
\end{thebibliography}

\end{document}

From Spring 2011 or before; revised by Miller, Spring 2013.

### 2013-09-23 paper.tex

@@
   \begin{theorem}
-  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a point mass $p$ whose initial position is $(x_1, y_1)$ which moves with tangential acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
+  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a point mass $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
   \begin{eqnarray}
@@
 For convenience of notation, we will now refer to $x_2'$ as $x_2$.
+
+Now let us examine the particle's motion in the $x$ direction.
+Let $a_t(t)$ be the tangential acceleration at time $t$ in the $x$ direction.
+Then we can obtain the speed of the particle $s(t)$ at time $t$ in the $x$ direction like so:
+\begin{eqnarray}
+  s(t) = \int_0^t a_t(t_1) dt_1
+\end{eqnarray}
+
+To find the distance $d(t)$ travelled up to time $t$ in the $x$ direction, we can use the relation:
+\begin{eqnarray}
+  d(t) &=& \int_0^t s(t_2) dt_2 \\
+       &=& \int_0^t \int_0^t a_t(t_1) dt_1 dt_2
+\end{eqnarray}
+
+Recall that the acceleration of the point mass $p$ is bounded by $\bar{a}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
+\begin{eqnarray}
+  d(t) &\leq& \int_0^t \int_0^t \bar{a} dt_1 dt_2 \\
+       &=& \frac{\bar{a} t^2}{2}
+\end{eqnarray}
+
+Thus, in order to travel a distance of $d(T_f) = x_2$, it needs to be the case that $T_f \geq \sqrt{\frac{2 x_2}{\bar{a}}}$.
+Moreover, equality holds if and only if $a_t(t) = \bar{a}$ for all $t \in [0, T_f(\gamma)]$.
+
+If the point mass travels for time $t < \sqrt{\frac{2 x_2}{\bar{a}}}$, then it is impossible for the point mass to reach $(x_2, 0)$ when starting at $(0,0)$.
+This is because $p$ cannot reach $(x_2, 0)$ in the $x$ direction when $t < \sqrt{\frac{2 x_2}{\bar{a}}}$ and any acceleration in the $y$ direction would not enable this either.
+
+This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$.
+Let us examine the path taken by the point mass $p$ on this fastest path.
+Recall that $a_t(t) = \bar{a}$ for all $t$ along the fastest path.
+This means that there was no centripetal acceleration $|a_c| = 0$.
+In other words, the point mass never turned on its way to reaching the destination point.
+The only way this could have happened is if it travelled along the $x$ axis in a straight line.
+
+Now, we have seen that the fastest path in the transformed coordinates travels exactly on the $x$ axis so that $y = 0$ anywhere along the fastest path.
+Notice, however, that the $x$ axis in the transformed coordinates is given exactly by the following line:
+\begin{eqnarray}
+  y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
+\end{eqnarray}
+
+Thus, we see that the fastest path in the original coordinates follows the above equation, which is what we wanted to show.
 \qed

### 2013-09-27 paper.tex
Quadrilateral theroems.

@@
 
+\section{Turning Around a Cone - Constant Velocity}
+
+\subsection{Quadrilateral}
+
+Before we attempt to tackle the problem of finding the optimal path around a cone at constant velocity, we may want to find some intuition for the problem with a simple, but related problem.
+In particular, if a particle is traveling around a cone, we would like to know what circle it traces as it goes around the cone.
+
+To make a simple model of this problem, we will use a quadrilateral to model a path around a cone.
+We will construct a quadrilateral with particular constaints that models the constraints of a path around a cone, and we will try to find the parameters that minimize the perimeter around the quadrilateral.
+Let us call the sides of the quadrilateral $s_1, s_2, s_3$ and $s_4$.
+Imagine that $s_1$ and $s_2$ are on opposite sides of the quadrilateral with fixed lengths $l_1$ and $l_2$ respectively.
+Now we will constrain the problem to be related to the problem of a particle traveling around a cone: imagine $s_1$ and $s_2$ are connected by a bar $s_b$ of length $d$.
+The bar will be perpendicular to $s_1$.
+The angle that $s_b$ forms with $s_2$ will be called $\theta$.
+We will try to find the optimal $\theta$ that minimizes the perimeter around the quadrilateral.
+\begin{figure}
+\end{figure}
+
+\subsection{Symmetric Quadrilateral}
+
+Let us begin by solving the simplest version of this problem.
+Let us imagine that $s_b$ is connected to the midpoints of $s_1$ and $s_2$.
+We know that the perimeter will be given by $l_1 + l_2 + l_3 + l_4$ where $l_3$ and $l_4$ are the lengths of the sides of $s_3$ and $s_4$, respectively.
+We are given $l_1$ and $l_2$, but we will need to compute $l_3$ and $l_4$ as functions of $l_1, l_2,d, $ and $\theta$.
+
+We can find $l_3$ by using the fact that it forms a right triangle.
+We know that $l_3^2 = m^2 + n^2$.
+Finding $l_4$ is similar.
+Therefore, we just need to find $m$ and $n$.
+This can be done by using the fact that $m = \frac{l_1}{2} - \frac{l_2}{2} \sin \theta$.
+This is just the upper half of $s_1$ minus the projection of $s_2$ onto $s_1$.
+We can find $n$ similarly: $n = d - \frac{l_2}{2} \cos \theta$.
+This is just the bar $s_b$ minus the projection of $s_2$ onto the bar.
+Thus by substituting, we have:
+\begin{eqnarray}
+  l_3 = \sqrt{ \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d - \frac{l_2}{2} \cos \theta \right)^2 }
+\end{eqnarray}
+
+We can do a similar analysis on $l_4$, only remembering that $n$ for $l_4$ gets extended by the projection onto $s_4$ instead of shrunken. We therefore have:
+\begin{eqnarray}
+  l_4 = \sqrt{ \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2 }
+\end{eqnarray}
+
+Now, to minimize the perimeter with respect to $\theta$, we want to minimize $l_1 + l_2 + l_3 + l_4$.
+Since we know that $l_1$ and $l_2$ are fixed, we really want to minimize $l_3 + l_4$ with respect to $\theta$.
+The other thing to note is that we're minimizing positive distances.
+We will invoke the following lemma so that we can simplify our expression for $\min l_3 + l_4$:
+
+\begin{lemma}
+  If $f(t), g(t) > 0$ for all $t$, then $\argmin_t \sqrt{f(t)} + \sqrt{g(t)} = \argmin_t f(t) + g(t)$.
+  \label{lemma:minsqrt}
+\end{lemma}
+\proof Let $t_1, t_2$ be such that $f(t_1) + g(t_1) < f(t_2) + g(t_2)$.
+Then we can show that $\sqrt{f(t_1)} + \sqrt{g(t_1)} < \sqrt{f(t_2)} + \sqrt{g(t_2)}$.
+To do this, let's define $k(t) = t^{1/2}$ as the square root function.
+Then $\sqrt{f(t))} = k(f(t))$.
+Now we know that $k(t)$ is a strictly monotonically increasing function when $t > 0$, which means that $k(x) < k(y)$ if and only if $x < y$ (assuming we can confine $x, y$ to be non-negative).
+
+Because this is the case, we see that $k(f(x)) < k(f(y))$ if and only if $f(x) < f(y)$ (the same goes for $g$).
+Thus, we see that if we have found the minimum $t_m$ to $\min_t k(f(t)) + k(g(t))$, then it is the case that $k(f(t_m)) + k(g(t_m)) < k(f(t)) + k(g(t))$ for all $t \neq t_m$ (again where $t > 0$).
+Following our train of logic, we see that $f(t_m) + g(t_m) < f(t) + g(t)$ for all $t \neq t_m$, which means that $t_m$ is a minimum of $f(t) + g(t)$.
+Thus by finding a minimum $t_m$ to $k(f(t)) + k(g(t)) = \sqrt{f(t)} + \sqrt{g(t)}$, we also found a minimum to $f(t) + g(t)$.
+\qed
+
+Since we've proven this lemma, we can invoke it upon $\min l_3 + l_4$.
+
 \bibliographystyle{plain}

### 2013-09-27 paper.tex
Finishing up the symmetrical quadrilateral proof.

@@
 \begin{lemma}
-  If $f(t), g(t) > 0$ for all $t$, then $\argmin_t \sqrt{f(t)} + \sqrt{g(t)} = \argmin_t f(t) + g(t)$.
+  If $f(t), g(t) > 0$ and $k(t) > 0$ is a strictly monotonically increasing function for all $t$, then $\argmin_t k(f(t)) + k(g(t)) = \argmin_t f(t) + g(t)$.
   \label{lemma:minsqrt}
@@
 \proof Let $t_1, t_2$ be such that $f(t_1) + g(t_1) < f(t_2) + g(t_2)$.
-Then we can show that $\sqrt{f(t_1)} + \sqrt{g(t_1)} < \sqrt{f(t_2)} + \sqrt{g(t_2)}$.
-To do this, let's define $k(t) = t^{1/2}$ as the square root function.
-Then $\sqrt{f(t))} = k(f(t))$.
-Now we know that $k(t)$ is a strictly monotonically increasing function when $t > 0$, which means that $k(x) < k(y)$ if and only if $x < y$ (assuming we can confine $x, y$ to be non-negative).
+In this proof, we will show that $k(f(t_1)) + k(g(t_1)) < \sqrt{f(t_2)} + \sqrt{g(t_2)}$.
+Since $k(t)$ is a strictly monotonically increasing function when $t > 0$, we know that $k(x) < k(y)$ if and only if $x < y$ (assuming we can confine $x, y$ to be non-negative).
 
 Because this is the case, we see that $k(f(x)) < k(f(y))$ if and only if $f(x) < f(y)$ (the same goes for $g$).
-Thus, we see that if we have found the minimum $t_m$ to $\min_t k(f(t)) + k(g(t))$, then it is the case that $k(f(t_m)) + k(g(t_m)) < k(f(t)) + k(g(t))$ for all $t \neq t_m$ (again where $t > 0$).
+Thus, we see that if we have found the minimum $t_m$ to $\argmin_t k(f(t)) + k(g(t))$, then it is the case that $k(f(t_m)) + k(g(t_m)) < k(f(t)) + k(g(t))$ for all $t \neq t_m$ (again where $t > 0$).
 Following our train of logic, we see that $f(t_m) + g(t_m) < f(t) + g(t)$ for all $t \neq t_m$, which means that $t_m$ is a minimum of $f(t) + g(t)$.
-Thus by finding a minimum $t_m$ to $k(f(t)) + k(g(t)) = \sqrt{f(t)} + \sqrt{g(t)}$, we also found a minimum to $f(t) + g(t)$.
+Thus by finding a minimum $t_m$ to $k(f(t)) + k(g(t))$, we also found a minimum to $f(t) + g(t)$.
 \qed
@@
 Since we've proven this lemma, we can invoke it upon $\min l_3 + l_4$.
+Since $l_3 = \sqrt{z_3}$ and $l_4 = \sqrt{z_4}$, we can use $k(t) = \sqrt{t}$ and we can write $\min l_3 + l_4 = \min z_3 + z_4$ by using our lemma.
+Thus, we now want to solve the problem:
+\begin{eqnarray}
+  \argmin_{\theta} 2 \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d - \frac{l_2}{2} \cos \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2
+\end{eqnarray}
+
+Now, we can expand out our expression and use the fact that $\sin^2 \theta + \cos^2 \theta = 1$ to obtain a much simpler (but equivalent) minimization problem:
+\begin{eqnarray}
+  \argmin_{\theta} \frac{l_1^2}{2} + \frac{l_2^2}{2} + 2d^2 - l_1 l_2 \sin \theta
+\end{eqnarray}
+
+We note that $l_1, l_2,$ and $d$ are all constants which are given to us in the problem. Therefore, the minimization problem really boils down to
+\begin{eqnarray}
+  \argmin_{\theta} - l_1 l_2 \sin \theta = \argmax_{\theta} \sin \theta
+\end{eqnarray}
+
+Thus, we see that $\theta = \frac{\pi}{2}$ minimizes the perimeter of the quadrilateral in the symmetric case.
 

### 2013-09-28 paper.tex
Changing the definitions.

@@
 \begin{definition}
-  A path $\gamma: \mathrm{R} \to \mathrm{R}^2$ is a function which maps some time $t$ to a position $\gamma(t) \in \mathrm{R}^2$.
-The path is defined from time $t = 0$ until the end time of the path, denoted as $T_{f}(\gamma)$.
+  A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^2$ and its derivatives at some time $t$.
+In other words, we define $D(t) = \{ \vec{x}(t), \frac{d \vec{x}}{dt}(t), \frac{d^2 \vec{x}}{d t^2}(t), \ldots \}$.
 \end{definition}
@@
 \begin{definition}
-  A valid path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$ and conditions $\mathrm{C}$ is some path which at all times $t$ such that $0 \leq t \leq T_f(\gamma)$, all conditions in $\mathrm{C}$ are satisfied.
+  A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$ and outputs that either the condition is true or false.
+\end{definition}
+
+\begin{definition}
+A path $\gamma: \mathrm{R} \to \mathrm{R}^2$ is a function which maps some time $t$ to a position $\gamma(t) \in \mathrm{R}^2$.
+The path is defined from time $t = 0$ until the end time of the path, denoted as $T_{f, \gamma}$.
+\end{definition}
+
+\begin{definition}
+  A valid path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some particle $p$ and conditions $\mathrm{C}$ is some path which at all times $t$ such that $0 \leq t \leq T_{f, \gamma}$, all conditions in $\mathrm{C}$ on the particle are satisfied.
 \end{definition}

### 2013-09-28 paper.tex
Argmin and argmax command definitions.
Formatting of equation.
Uniqueness of fastest path.

@@
 \DeclarePairedDelimiter\tempcbracket{\{}{\}}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 \begin{definition}
-  A valid targetted path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$, conditions $\mathrm{C}$, starting point $\vec{x_1}$, and ending point $\vec{x_2}$ is a valid path where $\gamma(t) = \vec{x_1}$ and $\gamma(T_f(\gamma)) = \vec{x_2}$.
+  A valid targetted path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some particle $p$, conditions $\mathrm{C}$, starting point $\vec{x_1}$, and ending point $\vec{x_2}$ is a valid path where $\gamma(t) = \vec{x_1}$ and $\gamma(T_f(\gamma)) = \vec{x_2}$.
 In other words, it is a valid path which starts at $\vec{x_1}$ and ends at $\vec{x_2}$.
@@
 \begin{definition}
-  A fastest path $\hat{\gamma}: \mathrm{R} \to \mathrm{R}^2$ for a particular point mass $p$, a starting point $\vec{x_1}$, a destination point $\vec{x_2}$, and some set of conditions $\mathrm{C}$ is a valid targetted path $\hat{\gamma}$ such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid targetted paths $\gamma$ with the same $p$, $\vec{x_1}$, $\vec{x_2}$, and $\mathrm{C}$.
+  A fastest path $\hat{\gamma}: \mathrm{R} \to \mathrm{R}^2$ for a particular particle $p$, a starting point $\vec{x_1}$, a destination point $\vec{x_2}$, and some set of conditions $\mathrm{C}$ is a valid targetted path $\hat{\gamma}$ such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid targetted paths $\gamma$ with the same $p$, $\vec{x_1}$, $\vec{x_2}$, and $\mathrm{C}$.
 \end{definition}
@@
   \begin{theorem}
-  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a point mass $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
+  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
   \begin{eqnarray}
@@
 \begin{corollary}
-  The fastest path between two points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ is unique.
+  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ is unique.
 \end{corollary}
+\proof We have already shown that any fastest path between $(x_1, y_1)$ and $(x_2, y_2)$ follows the straight line given by $y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1$.
+Moreover, we showed that when travelling along the fastest path, the particle must have acceleration along the straight line of $\bar{a}$.
+Since we have starting position $(x_1, y_1)$ and initial speed of $0$, the acceleration of the particle $a(t)$ uniquely defines a path for the particle.
+
+There is only a single function $a(t) = \bar{a}$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
+\qed
 
@@
 \begin{eqnarray}
-  \argmin_{\theta} 2 \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d - \frac{l_2}{2} \cos \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2
+  \argmin_{\theta} &2& \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 \\
+  &+& \left( d - \frac{l_2}{2} \cos \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2
 \end{eqnarray}
@@
 
+\subsection{Non-Symmetric Quadrilateral}
+
 \bibliographystyle{plain}

### 2013-09-28 paper.tex
Including a figure as reference.
Reorganizing the paper. Moving notation into the appendix.

@@
 
-\section{Theorems}
+\section{Introduction}
 
-\subsection{Notation\label{sec:notation}}
+\section{Background and Definitions}
 
-\begin{description}
-    \item[$t$] Time
-    \item[$l$] Path length
-    \item[$s$] Speed
-    \item[$a_t$] Tangential acceleration
-    \item[$a_c$] Centripetal acceleration
-    \item[$\vec{x}$] Position
-    \item[$\vec{v}$] Velocity
-    \item[$\vec{a}$] Acceleration
-\end{description}
-
-\section{Coordinates}
-
-\subsection{Scalar Calculus}
-
-\begin{align}
-s& = \frac{dl}{dt}\\
-%
-a_t& = \frac{ds}{dt}\\
-\end{align}
-
-\subsection{Vector Calculus}
-
-\begin{align}
-\boldsymbol{x}& = r \boldsymbol{\hat{r}}\\
-%
-\boldsymbol{\vec{v}}& = \dot{r} \boldsymbol{\hat{r}} + r \dot{\phi} \boldsymbol{\hat{\phi}}\\
-%
-\boldsymbol{\vec{a}}& = \paren{\ddot{r} - r \dot{\phi}^2} \boldsymbol{\hat{r}} + \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}} \boldsymbol{\hat{\phi}}
-\end{align}
-
-\subsection{Relations}
-
-\begin{align}
-l& = \int_{t=0}^{T} \norm{\boldsymbol{\vec{v}} \, } \; dt\\
-%
-s& = \boldsymbol{\vec{v}}\\
-%
-a_t& = \norm{\boldsymbol{\vec{a}}\,} \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}\,}}
-\end{align}
-
-\section{Traveling Between Points}
+In this section, we will make some basic definitions about particles and paths.
+These should lay the groundwork for thinking about optimal paths.
+We will begin by defining the description of a particle and then define various types of paths that a particle can take.
 
@@
 \end{definition}
+
+\section{Traveling Between Points}
 
@@
 We will try to find the optimal $\theta$ that minimizes the perimeter around the quadrilateral.
+
+We will use figure \label{fig:quadrilateral} as reference.
+
 \begin{figure}
+  \includegraphics[width=3in]{figures/quad.eps}
+  \caption{Minimizing perimeter around a quadrilateral}
 \end{figure}
@@
 
+\section{Appendix}
+
+\subsection{Notation\label{sec:notation}}
+
+\begin{description}
+    \item[$t$] Time
+    \item[$l$] Path length
+    \item[$s$] Speed
+    \item[$a_t$] Tangential acceleration
+    \item[$a_c$] Centripetal acceleration
+    \item[$\vec{x}$] Position
+    \item[$\vec{v}$] Velocity
+    \item[$\vec{a}$] Acceleration
+\end{description}
+
+\section{Coordinates}
+
+\subsection{Scalar Calculus}
+
+\begin{align}
+s& = \frac{dl}{dt}\\
+%
+a_t& = \frac{ds}{dt}\\
+\end{align}
+
+\subsection{Vector Calculus}
+
+\begin{align}
+\boldsymbol{x}& = r \boldsymbol{\hat{r}}\\
+%
+\boldsymbol{\vec{v}}& = \dot{r} \boldsymbol{\hat{r}} + r \dot{\phi} \boldsymbol{\hat{\phi}}\\
+%
+\boldsymbol{\vec{a}}& = \paren{\ddot{r} - r \dot{\phi}^2} \boldsymbol{\hat{r}} + \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}} \boldsymbol{\hat{\phi}}
+\end{align}
+
+\subsection{Relations}
+
+\begin{align}
+l& = \int_{t=0}^{T} \norm{\boldsymbol{\vec{v}} \, } \; dt\\
+%
+s& = \boldsymbol{\vec{v}}\\
+%
+a_t& = \norm{\boldsymbol{\vec{a}}\,} \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}\,}}
+\end{align}
+
 \bibliographystyle{plain}

### 2013-09-28 cone_theorems.tex
Add definitions and notation. Start adding 3 cones proof.

--- 2013-09-28 paper.tex
@@
-\documentclass[12pt]{amsart}   % LaTeX with AMS style; 12 point for old eyes
-
-\usepackage{amsmath,amssymb,amsfonts}   % For better support of math
-\usepackage{graphicx}	        % Enable for eps and pdf figures, if they occur
-\usepackage{hyperref} % Enable embedded hyperlinks.
-\hypersetup{
-	hidelinks, colorlinks, linkcolor=black, citecolor=black, urlcolor=red
-}
-
-% Commands to force sequential numbering:
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{examples}[theorem]{Examples}
-\newtheorem{remarks}[theorem]{Remarks}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{conjecture}[theorem]{Conjecture}
-
-% Define abs norm, paren, bracket, cbracket, and innerproduct
-\usepackage{mathtools}
-\DeclarePairedDelimiter\tempabs{\lvert}{\rvert}
-\DeclarePairedDelimiter\tempnorm{\lVert}{\rVert}
-\DeclarePairedDelimiter\tempinnerproduct{\langle}{\rangle}
-\DeclarePairedDelimiter\tempparen{(}{)}
-\DeclarePairedDelimiter\tempbracket{[}{]}
-\DeclarePairedDelimiter\tempcbracket{\{}{\}}
-
-% Swap * functionality
-\makeatletter
-\def\abs{\@ifstar{\tempabs}{\tempabs*}}
-\def\norm{\@ifstar{\tempnorm}{\tempnorm*}}
-\def\innerproduct{\@ifstar{\tempinnerproduct}{\tempinnerproduct*}}
-\def\paren{\@ifstar{\tempparen}{\tempparen*}}
-\def\bracket{\@ifstar{\tempbracket}{\tempbracket*}}
-\def\cbracket{\@ifstar{\tempcbracket}{\tempcbracket*}}
-\makeatother
-
-\begin{document}
-
-\title[The 18.821 report]{The 18.821 Mathematics Project Lab Report 
-[Proofs]} 
-% the first [...] gives a brief version of the title, which is long!
-
-\author{Jonathan Allen}
-\date{\today}              % or an actual date
-
-\newcommand{\C}{\mathbb C} % blackboard bold , for ``complex,'' etc
-\newcommand{\R}{\mathbb R} 
-\newcommand{\Z}{\mathbb Z}
-\newcommand{\Q}{\mathbb Q}
-\newcommand{\N}{\mathbb N}
-
-\maketitle
-
-\section{Theorems}
-
-\subsection{Notation\label{sec:notation}}
-
-\begin{description}
-    \item[$t$] Time
-    \item[$l$] Path length
-    \item[$s$] Speed
-    \item[$a_t$] Tangential acceleration
-    \item[$a_c$] Centripetal acceleration
-    \item[$\vec{x}$] Position
-    \item[$\vec{v}$] Velocity
-    \item[$\vec{a}$] Acceleration
-\end{description}
-
-\section{Coordinates}
-
-\subsection{Scalar Calculus}
-
-\begin{align}
-s& = \frac{dl}{dt}\\
-%
-a_t& = \frac{ds}{dt}\\
-\end{align}
-
-\subsection{Vector Calculus}
-
-\begin{align}
-\boldsymbol{x}& = r \boldsymbol{\hat{r}}\\
-%
-\boldsymbol{\vec{v}}& = \dot{r} \boldsymbol{\hat{r}} + r \dot{\phi} \boldsymbol{\hat{\phi}}\\
-%
-\boldsymbol{\vec{a}}& = \paren{\ddot{r} - r \dot{\phi}^2} \boldsymbol{\hat{r}} + \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}} \boldsymbol{\hat{\phi}}
-\end{align}
-
-\subsection{Relations}
-
-\begin{align}
-l& = \int_{t=0}^{T} \norm{\boldsymbol{\vec{v}} \, } \; dt\\
-%
-s& = \boldsymbol{\vec{v}}\\
-%
-a_t& = \norm{\boldsymbol{\vec{a}}\,} \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}\,}}
-\end{align}
-
-\section{Traveling Between Points}
-
-\begin{definition}
-  A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^2$ and its derivatives at some time $t$.
-In other words, we define $D(t) = \{ \vec{x}(t), \frac{d \vec{x}}{dt}(t), \frac{d^2 \vec{x}}{d t^2}(t), \ldots \}$.
-\end{definition}
-
-\begin{definition}
-  A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$ and outputs that either the condition is true or false.
-\end{definition}
-
-\begin{definition}
-A path $\gamma: \mathrm{R} \to \mathrm{R}^2$ is a function which maps some time $t$ to a position $\gamma(t) \in \mathrm{R}^2$.
-The path is defined from time $t = 0$ until the end time of the path, denoted as $T_{f, \gamma}$.
-\end{definition}
-
-\begin{definition}
-  A valid path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some particle $p$ and conditions $\mathrm{C}$ is some path which at all times $t$ such that $0 \leq t \leq T_{f, \gamma}$, all conditions in $\mathrm{C}$ on the particle are satisfied.
-\end{definition}
-
-\begin{definition}
-  A valid targetted path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$, conditions $\mathrm{C}$, starting point $\vec{x_1}$, and ending point $\vec{x_2}$ is a valid path where $\gamma(t) = \vec{x_1}$ and $\gamma(T_f(\gamma)) = \vec{x_2}$.
-In other words, it is a valid path which starts at $\vec{x_1}$ and ends at $\vec{x_2}$.
-\end{definition}
-
-\begin{definition}
-  A fastest path $\hat{\gamma}: \mathrm{R} \to \mathrm{R}^2$ for a particular point mass $p$, a starting point $\vec{x_1}$, a destination point $\vec{x_2}$, and some set of conditions $\mathrm{C}$ is a valid targetted path $\hat{\gamma}$ such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid targetted paths $\gamma$ with the same $p$, $\vec{x_1}$, $\vec{x_2}$, and $\mathrm{C}$.
-\end{definition}
-
-  \begin{theorem}
-  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a point mass $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
-  \begin{eqnarray}
-    y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
-  \end{eqnarray}
-\end{theorem}
-\proof Let's transform the problem.
-We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis.
-In this new coordinate system, we have transformed the following:
-\begin{eqnarray}
-  (x_1, y_1) &\to& (0,0) \\
-  (x_2, y_2) &\to& (x_2', 0)
-\end{eqnarray}
-
-For convenience of notation, we will now refer to $x_2'$ as $x_2$.
-
-Now let us examine the particle's motion in the $x$ direction.
-Let $a_t(t)$ be the tangential acceleration at time $t$ in the $x$ direction.
-Then we can obtain the speed of the particle $s(t)$ at time $t$ in the $x$ direction like so:
-\begin{eqnarray}
-  s(t) = \int_0^t a_t(t_1) dt_1
-\end{eqnarray}
-
-To find the distance $d(t)$ travelled up to time $t$ in the $x$ direction, we can use the relation:
-\begin{eqnarray}
-  d(t) &=& \int_0^t s(t_2) dt_2 \\
-       &=& \int_0^t \int_0^t a_t(t_1) dt_1 dt_2
-\end{eqnarray}
-
-Recall that the acceleration of the point mass $p$ is bounded by $\bar{a}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
-\begin{eqnarray}
-  d(t) &\leq& \int_0^t \int_0^t \bar{a} dt_1 dt_2 \\
-       &=& \frac{\bar{a} t^2}{2}
-\end{eqnarray}
-
-Thus, in order to travel a distance of $d(T_f) = x_2$, it needs to be the case that $T_f \geq \sqrt{\frac{2 x_2}{\bar{a}}}$.
-Moreover, equality holds if and only if $a_t(t) = \bar{a}$ for all $t \in [0, T_f(\gamma)]$.
-
-If the point mass travels for time $t < \sqrt{\frac{2 x_2}{\bar{a}}}$, then it is impossible for the point mass to reach $(x_2, 0)$ when starting at $(0,0)$.
-This is because $p$ cannot reach $(x_2, 0)$ in the $x$ direction when $t < \sqrt{\frac{2 x_2}{\bar{a}}}$ and any acceleration in the $y$ direction would not enable this either.
-
-This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$.
-Let us examine the path taken by the point mass $p$ on this fastest path.
-Recall that $a_t(t) = \bar{a}$ for all $t$ along the fastest path.
-This means that there was no centripetal acceleration $|a_c| = 0$.
-In other words, the point mass never turned on its way to reaching the destination point.
-The only way this could have happened is if it travelled along the $x$ axis in a straight line.
-
-Now, we have seen that the fastest path in the transformed coordinates travels exactly on the $x$ axis so that $y = 0$ anywhere along the fastest path.
-Notice, however, that the $x$ axis in the transformed coordinates is given exactly by the following line:
-\begin{eqnarray}
-  y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
-\end{eqnarray}
-
-Thus, we see that the fastest path in the original coordinates follows the above equation, which is what we wanted to show.
-\qed
-
-\begin{corollary}
-  The fastest path between two points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ is unique.
-\end{corollary}
-
-\section{Turning Around a Cone - Constant Velocity}
-
 \subsection{Quadrilateral}
@@
 In particular, if a particle is traveling around a cone, we would like to know what circle it traces as it goes around the cone.
+
+\includefig{quad.eps}{Quadrilateral path. A $\to$ B $\to$ C $\to$ D}{quad}
 
@@
 We will try to find the optimal $\theta$ that minimizes the perimeter around the quadrilateral.
-\begin{figure}
-\end{figure}
 
@@
 
-\bibliographystyle{plain}
-\begin{thebibliography}{9}
-\bibitem{wiki_pcoords}
-\url{http://en.wikipedia.org/wiki/Polar_coordinate_system}
-\end{thebibliography}
+% -----------------------------------------------------------------------------
 
-\end{document}
+% 3 cones, constant speed
+\begin{theorem}
 
-From Spring 2011 or before; revised by Miller, Spring 2013.
+Given a cone setup consisting of 3 cones at locations $X_A$, $X_B$, and $X_C$.
+
+\includefig{cones_fix_s.eps}{A}{cones-fix-s}
+
+\begin{align}
+dB& = \sqrt{x_B + y_B}\\
+\intertext{Applying the triangle inequality...}
+d_c& = \alpha_c - \tan^{-1}\paren{\frac{y_B}{x_B}}\\
+\end{align}
+
+\includefig{cones_fix_s_2.eps}{A}{cones-fix-s-2}
+
+\begin{align}
+l_1& = \sqrt{d_c - r}\\
+x_c = x_B - r \cos{\alpha_c}\\
+y_c = y_B - r \sin{\alpha_c}\\
+d_c& = \alpha_c - \tan^{-1}\paren{\frac{y_c}{x_c}}\\
+\end{align}
+
+\end{theorem}
+
+\proof

### 2013-09-28 math_review.tex
Add definitions and notation. Start adding 3 cones proof.

\subsection{Coordinate Systems\label{sec:notation}}

\subsubsection{Time Derivatives}

\begin{align*}
\dot{a}& = \frac{da}{dt}\\
%
\ddot{a}& = \frac{d^2a}{dt^2}
\end{align*}

\subsubsection{Radius of Curvature}

The radius of curvature, $R$, of a curve at a point is a measure of the radius of the circular arc which best approximates the curve at that point.

\begin{align}
R& = \abs{\frac{\paren{\dot{x}^2 + \dot{y}^2}^{3/2}}{\dot{x}\ddot{y} - \dot{y}{\ddot{x}}}}\\
%
&= \abs{\frac{s^2}{a_t}}\tag{for $a_c = $}
\end{align}

\subsection{Scalar Calculus in Polar Coordinates}

\begin{align}
s& = \frac{dl}{dt}\\
%
a_t& = \frac{ds}{dt}\\
\end{align}

\subsection{Vector Calculus in Polar Coordinates}

\begin{align}
\boldsymbol{x}& = r \boldsymbol{\hat{r}}\\
%
\boldsymbol{\vec{v}}& = \dot{r} \boldsymbol{\hat{r}} + r \dot{\phi} \boldsymbol{\hat{\phi}}\\
%
\label{eq:a_vec_def}\boldsymbol{\vec{a}}& = \paren{\ddot{r} - r \dot{\phi}^2} \boldsymbol{\hat{r}} + \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}} \boldsymbol{\hat{\phi}}
\end{align}

\subsection{Relations}

\begin{align}
l& = \int_{t=0}^{T} \norm{\boldsymbol{\vec{v}} \, } \; dt\\
%
s& = \norm{\boldsymbol{\vec{v}}}\\
%
a_t& = \norm{\boldsymbol{\vec{a}}} \cdot \boldsymbol{\hat{v}} = \norm{\boldsymbol{\vec{a}}} \cdot \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}}}\\
%
a_c& = \norm{\boldsymbol{\vec{a}}} \times \boldsymbol{\hat{v}} = \norm{\boldsymbol{\vec{a}}} \times \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}}}
\end{align}

### 2013-09-28 paper.tex
Add definitions and notation. Start adding 3 cones proof.

--- 2013-09-28 paper.tex
@@
 \usepackage{graphicx}	        % Enable for eps and pdf figures, if they occur
+\usepackage{caption}
+\usepackage{float}
+\usepackage{subcaption}
 \usepackage{hyperref} % Enable embedded hyperlinks.
@@
 \DeclarePairedDelimiter\tempcbracket{\{}{\}}
-
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
 % Swap * functionality
@@
 
+% blackboard bold , for ``complex,'' etc
+\newcommand{\C}{\mathbb C} 
+\newcommand{\R}{\mathbb R} 
+\newcommand{\Z}{\mathbb Z}
+\newcommand{\Q}{\mathbb Q}
+\newcommand{\N}{\mathbb N}
+
+% Add fig with caption command. Inputs: {path}{caption}{label}
+\newcommand{\includefig}[3]{
+  \begin{figure}[H]
+    \begin{center}
+      \includegraphics[width=4in,height=3in,keepaspectratio]{#1}
+    \end{center}
+  \vspace{-.2in} % corrects bad spacing
+  \caption{#2.\label{fig:#3}}
+  \end{figure}
+}
+
+\newcommand{\bvec}[1]{\mathbf{#1}}
+\newcommand{\bhat}[1]{\mathbf{\hat{#1}}}
+
 \begin{document}
+
+\graphicspath{ {figures/} }
 
@@
 
-\author{Jonathan Allen}
-\date{\today}              % or an actual date
-
-\newcommand{\C}{\mathbb C} % blackboard bold , for ``complex,'' etc
-\newcommand{\R}{\mathbb R} 
-\newcommand{\Z}{\mathbb Z}
-\newcommand{\Q}{\mathbb Q}
-\newcommand{\N}{\mathbb N}
+\author{Jonathan Allen, John Wang}
+\date{\today}
 
@@
 
-\section{Theorems}
+\section{Introduction}
+\input{introduction.tex}
 
-\subsection{Notation\label{sec:notation}}
+\section{Notation}
+\input{notation.tex}
 
-\begin{description}
-    \item[$t$] Time
-    \item[$l$] Path length
-    \item[$s$] Speed
-    \item[$a_t$] Tangential acceleration
-    \item[$a_c$] Centripetal acceleration
-    \item[$\vec{x}$] Position
-    \item[$\vec{v}$] Velocity
-    \item[$\vec{a}$] Acceleration
-\end{description}
-
-\section{Coordinates}
-
-\subsection{Scalar Calculus}
-
-\begin{align}
-s& = \frac{dl}{dt}\\
-%
-a_t& = \frac{ds}{dt}\\
-\end{align}
-
-\subsection{Vector Calculus}
-
-\begin{align}
-\boldsymbol{x}& = r \boldsymbol{\hat{r}}\\
-%
-\boldsymbol{\vec{v}}& = \dot{r} \boldsymbol{\hat{r}} + r \dot{\phi} \boldsymbol{\hat{\phi}}\\
-%
-\boldsymbol{\vec{a}}& = \paren{\ddot{r} - r \dot{\phi}^2} \boldsymbol{\hat{r}} + \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}} \boldsymbol{\hat{\phi}}
-\end{align}
-
-\subsection{Relations}
-
-\begin{align}
-l& = \int_{t=0}^{T} \norm{\boldsymbol{\vec{v}} \, } \; dt\\
-%
-s& = \boldsymbol{\vec{v}}\\
-%
-a_t& = \norm{\boldsymbol{\vec{a}}\,} \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}\,}}
-\end{align}
+\section{Particles and Paths}
+\input{particle_definitions.tex}
 
 \section{Traveling Between Points}
+\input{path_theorems.tex}
 
-\begin{definition}
-  A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^2$ and its derivatives at some time $t$.
-In other words, we define $D(t) = \{ \vec{x}(t), \frac{d \vec{x}}{dt}(t), \frac{d^2 \vec{x}}{d t^2}(t), \ldots \}$.
-\end{definition}
+\section{Turning Around Cones}
+\input{cone_theorems.tex}
 
-\begin{definition}
-  A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$ and outputs that either the condition is true or false.
-\end{definition}
-
-\begin{definition}
-A path $\gamma: \mathrm{R} \to \mathrm{R}^2$ is a function which maps some time $t$ to a position $\gamma(t) \in \mathrm{R}^2$.
-The path is defined from time $t = 0$ until the end time of the path, denoted as $T_{f, \gamma}$.
-\end{definition}
-
-\begin{definition}
-  A valid path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some particle $p$ and conditions $\mathrm{C}$ is some path which at all times $t$ such that $0 \leq t \leq T_{f, \gamma}$, all conditions in $\mathrm{C}$ on the particle are satisfied.
-\end{definition}
-
-\begin{definition}
-  A valid targetted path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$, conditions $\mathrm{C}$, starting point $\vec{x_1}$, and ending point $\vec{x_2}$ is a valid path where $\gamma(t) = \vec{x_1}$ and $\gamma(T_f(\gamma)) = \vec{x_2}$.
-In other words, it is a valid path which starts at $\vec{x_1}$ and ends at $\vec{x_2}$.
-\end{definition}
-
-\begin{definition}
-  A fastest path $\hat{\gamma}: \mathrm{R} \to \mathrm{R}^2$ for a particular point mass $p$, a starting point $\vec{x_1}$, a destination point $\vec{x_2}$, and some set of conditions $\mathrm{C}$ is a valid targetted path $\hat{\gamma}$ such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid targetted paths $\gamma$ with the same $p$, $\vec{x_1}$, $\vec{x_2}$, and $\mathrm{C}$.
-\end{definition}
-
-  \begin{theorem}
-  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a point mass $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
-  \begin{eqnarray}
-    y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
-  \end{eqnarray}
-\end{theorem}
-\proof Let's transform the problem.
-We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis.
-In this new coordinate system, we have transformed the following:
-\begin{eqnarray}
-  (x_1, y_1) &\to& (0,0) \\
-  (x_2, y_2) &\to& (x_2', 0)
-\end{eqnarray}
-
-For convenience of notation, we will now refer to $x_2'$ as $x_2$.
-
-Now let us examine the particle's motion in the $x$ direction.
-Let $a_t(t)$ be the tangential acceleration at time $t$ in the $x$ direction.
-Then we can obtain the speed of the particle $s(t)$ at time $t$ in the $x$ direction like so:
-\begin{eqnarray}
-  s(t) = \int_0^t a_t(t_1) dt_1
-\end{eqnarray}
-
-To find the distance $d(t)$ travelled up to time $t$ in the $x$ direction, we can use the relation:
-\begin{eqnarray}
-  d(t) &=& \int_0^t s(t_2) dt_2 \\
-       &=& \int_0^t \int_0^t a_t(t_1) dt_1 dt_2
-\end{eqnarray}
-
-Recall that the acceleration of the point mass $p$ is bounded by $\bar{a}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
-\begin{eqnarray}
-  d(t) &\leq& \int_0^t \int_0^t \bar{a} dt_1 dt_2 \\
-       &=& \frac{\bar{a} t^2}{2}
-\end{eqnarray}
-
-Thus, in order to travel a distance of $d(T_f) = x_2$, it needs to be the case that $T_f \geq \sqrt{\frac{2 x_2}{\bar{a}}}$.
-Moreover, equality holds if and only if $a_t(t) = \bar{a}$ for all $t \in [0, T_f(\gamma)]$.
-
-If the point mass travels for time $t < \sqrt{\frac{2 x_2}{\bar{a}}}$, then it is impossible for the point mass to reach $(x_2, 0)$ when starting at $(0,0)$.
-This is because $p$ cannot reach $(x_2, 0)$ in the $x$ direction when $t < \sqrt{\frac{2 x_2}{\bar{a}}}$ and any acceleration in the $y$ direction would not enable this either.
-
-This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$.
-Let us examine the path taken by the point mass $p$ on this fastest path.
-Recall that $a_t(t) = \bar{a}$ for all $t$ along the fastest path.
-This means that there was no centripetal acceleration $|a_c| = 0$.
-In other words, the point mass never turned on its way to reaching the destination point.
-The only way this could have happened is if it travelled along the $x$ axis in a straight line.
-
-Now, we have seen that the fastest path in the transformed coordinates travels exactly on the $x$ axis so that $y = 0$ anywhere along the fastest path.
-Notice, however, that the $x$ axis in the transformed coordinates is given exactly by the following line:
-\begin{eqnarray}
-  y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
-\end{eqnarray}
-
-Thus, we see that the fastest path in the original coordinates follows the above equation, which is what we wanted to show.
-\qed
-
-\begin{corollary}
-  The fastest path between two points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ is unique.
-\end{corollary}
-
-\section{Turning Around a Cone - Constant Velocity}
-
-\subsection{Quadrilateral}
-
-Before we attempt to tackle the problem of finding the optimal path around a cone at constant velocity, we may want to find some intuition for the problem with a simple, but related problem.
-In particular, if a particle is traveling around a cone, we would like to know what circle it traces as it goes around the cone.
-
-To make a simple model of this problem, we will use a quadrilateral to model a path around a cone.
-We will construct a quadrilateral with particular constaints that models the constraints of a path around a cone, and we will try to find the parameters that minimize the perimeter around the quadrilateral.
-Let us call the sides of the quadrilateral $s_1, s_2, s_3$ and $s_4$.
-Imagine that $s_1$ and $s_2$ are on opposite sides of the quadrilateral with fixed lengths $l_1$ and $l_2$ respectively.
-Now we will constrain the problem to be related to the problem of a particle traveling around a cone: imagine $s_1$ and $s_2$ are connected by a bar $s_b$ of length $d$.
-The bar will be perpendicular to $s_1$.
-The angle that $s_b$ forms with $s_2$ will be called $\theta$.
-We will try to find the optimal $\theta$ that minimizes the perimeter around the quadrilateral.
-\begin{figure}
-\end{figure}
-
-\subsection{Symmetric Quadrilateral}
-
-Let us begin by solving the simplest version of this problem.
-Let us imagine that $s_b$ is connected to the midpoints of $s_1$ and $s_2$.
-We know that the perimeter will be given by $l_1 + l_2 + l_3 + l_4$ where $l_3$ and $l_4$ are the lengths of the sides of $s_3$ and $s_4$, respectively.
-We are given $l_1$ and $l_2$, but we will need to compute $l_3$ and $l_4$ as functions of $l_1, l_2,d, $ and $\theta$.
-
-We can find $l_3$ by using the fact that it forms a right triangle.
-We know that $l_3^2 = m^2 + n^2$.
-Finding $l_4$ is similar.
-Therefore, we just need to find $m$ and $n$.
-This can be done by using the fact that $m = \frac{l_1}{2} - \frac{l_2}{2} \sin \theta$.
-This is just the upper half of $s_1$ minus the projection of $s_2$ onto $s_1$.
-We can find $n$ similarly: $n = d - \frac{l_2}{2} \cos \theta$.
-This is just the bar $s_b$ minus the projection of $s_2$ onto the bar.
-Thus by substituting, we have:
-\begin{eqnarray}
-  l_3 = \sqrt{ \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d - \frac{l_2}{2} \cos \theta \right)^2 }
-\end{eqnarray}
-
-We can do a similar analysis on $l_4$, only remembering that $n$ for $l_4$ gets extended by the projection onto $s_4$ instead of shrunken. We therefore have:
-\begin{eqnarray}
-  l_4 = \sqrt{ \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2 }
-\end{eqnarray}
-
-Now, to minimize the perimeter with respect to $\theta$, we want to minimize $l_1 + l_2 + l_3 + l_4$.
-Since we know that $l_1$ and $l_2$ are fixed, we really want to minimize $l_3 + l_4$ with respect to $\theta$.
-The other thing to note is that we're minimizing positive distances.
-We will invoke the following lemma so that we can simplify our expression for $\min l_3 + l_4$:
-
-\begin{lemma}
-  If $f(t), g(t) > 0$ and $k(t) > 0$ is a strictly monotonically increasing function for all $t$, then $\argmin_t k(f(t)) + k(g(t)) = \argmin_t f(t) + g(t)$.
-  \label{lemma:minsqrt}
-\end{lemma}
-\proof Let $t_1, t_2$ be such that $f(t_1) + g(t_1) < f(t_2) + g(t_2)$.
-In this proof, we will show that $k(f(t_1)) + k(g(t_1)) < \sqrt{f(t_2)} + \sqrt{g(t_2)}$.
-Since $k(t)$ is a strictly monotonically increasing function when $t > 0$, we know that $k(x) < k(y)$ if and only if $x < y$ (assuming we can confine $x, y$ to be non-negative).
-
-Because this is the case, we see that $k(f(x)) < k(f(y))$ if and only if $f(x) < f(y)$ (the same goes for $g$).
-Thus, we see that if we have found the minimum $t_m$ to $\argmin_t k(f(t)) + k(g(t))$, then it is the case that $k(f(t_m)) + k(g(t_m)) < k(f(t)) + k(g(t))$ for all $t \neq t_m$ (again where $t > 0$).
-Following our train of logic, we see that $f(t_m) + g(t_m) < f(t) + g(t)$ for all $t \neq t_m$, which means that $t_m$ is a minimum of $f(t) + g(t)$.
-Thus by finding a minimum $t_m$ to $k(f(t)) + k(g(t))$, we also found a minimum to $f(t) + g(t)$.
-\qed
-
-Since we've proven this lemma, we can invoke it upon $\min l_3 + l_4$.
-Since $l_3 = \sqrt{z_3}$ and $l_4 = \sqrt{z_4}$, we can use $k(t) = \sqrt{t}$ and we can write $\min l_3 + l_4 = \min z_3 + z_4$ by using our lemma.
-Thus, we now want to solve the problem:
-\begin{eqnarray}
-  \argmin_{\theta} 2 \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d - \frac{l_2}{2} \cos \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2
-\end{eqnarray}
-
-Now, we can expand out our expression and use the fact that $\sin^2 \theta + \cos^2 \theta = 1$ to obtain a much simpler (but equivalent) minimization problem:
-\begin{eqnarray}
-  \argmin_{\theta} \frac{l_1^2}{2} + \frac{l_2^2}{2} + 2d^2 - l_1 l_2 \sin \theta
-\end{eqnarray}
-
-We note that $l_1, l_2,$ and $d$ are all constants which are given to us in the problem. Therefore, the minimization problem really boils down to
-\begin{eqnarray}
-  \argmin_{\theta} - l_1 l_2 \sin \theta = \argmax_{\theta} \sin \theta
-\end{eqnarray}
-
-Thus, we see that $\theta = \frac{\pi}{2}$ minimizes the perimeter of the quadrilateral in the symmetric case.
+\section*{Appendix}
+\input{math_review.tex}
 

### 2013-09-28 particle_definitions.tex
Add definitions and notation. Start adding 3 cones proof.

\begin{definition}
A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $0 \ge t \ge T_{f, \gamma}$, to a position $\bvec{X} \in \mathrm{R}^n$. 
\end{definition}

\begin{definition}
  A n-dimensional particle, $p$, is an object with zero volume that travels along a n-dimensional path. The particle may have conditions on its position, velocity, and acceleration in $\R^n$.
\end{definition}

\begin{definition}
  A valid path $\gamma(t)$ for a particle $p$ is a path such that all conditions on the particle are satisfied at every point along the path.
\end{definition}

\begin{definition}
  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$ where $\gamma(0) = \bvec{X_1}$ and $\gamma(T_{f, \gamma}) = \bvec{X_2}$.
\end{definition}

\begin{definition}
  For a given particle, $p$, a fastest path, $\hat{\gamma}(t)$, between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
\end{definition}

\begin{definition}
  The centripetal acceleration, $\bvec{a_c}$, of a particle, $p$, is the component of the acceleration of $p$ perpendicular to its direction of motion, $\bhat{v}$. The sign of $a_c$ is difined as the sign of the projection of $\bhat{a_c}$ onto $\bhat{r}$.
\end{definition}

\begin{definition}
  The tangential acceleration, $\bvec{a_t}$, of a particle, $p$, is the component of the acceleration of $p$ in its direction of motion, $\bhat{v}$.
\end{definition}

### 2013-09-28 path_theorems.tex
Add definitions and notation. Start adding 3 cones proof.

% -----------------------------------------------------------------------------

\begin{theorem}
  Given points, $X_1, X_2 \in \R^2$ and a particle $p$ initially at $X_1$ with infinite centripetal acceleration bounded tangential acceleration, $\abs{a_t} \le \bar{a}$, then the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $X_1$ to $X_2$ is the line segment from $X_1$ to $X_2$.
\end{theorem}

\proof

Let's transform the problem. We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis. In this new coordinate system, we have transformed the following:
\begin{eqnarray}
  (x_1, y_1) &\to& (0,0) \\
  (x_2, y_2) &\to& (x_2', 0)
\end{eqnarray}

For convenience of notation, we will now refer to $x_2'$ as $x_2$.

Now let us examine the particle's motion in the $x$ direction. Let $a_t(t)$ be the tangential acceleration at time $t$ in the $x$ direction. Then we can obtain the speed of the particle $s(t)$ at time $t$ in the $x$ direction like so:
\begin{eqnarray}
  s(t) = \int_0^t a_t(t_1) dt_1
\end{eqnarray}

To find the distance $d(t)$ travelled up to time $t$ in the $x$ direction, we can use the relation:
\begin{eqnarray}
  d(t) &=& \int_0^t s(t_2) dt_2 \\
       &=& \int_0^t \int_0^t a_t(t_1) dt_1 dt_2
\end{eqnarray}

Recall that the acceleration of the particle $p$ is bounded by $\bar{a}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
\begin{eqnarray}
  d(t) &\leq& \int_0^t \int_0^t \bar{a} dt_1 dt_2 \\
       &=& \frac{\bar{a} t^2}{2}
\end{eqnarray}

Thus, in order to travel a distance of $d(T_f) = x_2$, it needs to be the case that $T_f \geq \sqrt{\frac{2 x_2}{\bar{a}}}$. Moreover, equality holds if and only if $a_t(t) = \bar{a}$ for all $t \in [0, T_f(\gamma)]$.

If the particle travels for time $t < \sqrt{\frac{2 x_2}{\bar{a}}}$, then it is impossible for the particle to reach $(x_2, 0)$ when starting at $(0,0)$. This is because $p$ cannot reach $(x_2, 0)$ in the $x$ direction when $t < \sqrt{\frac{2 x_2}{\bar{a}}}$ and any acceleration in the $y$ direction would not enable this either.

This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$. Let us examine the path taken by the particle $p$ on this fastest path. Recall that $a_t(t) = \bar{a}$ for all $t$ along the fastest path. This means that there was no centripetal acceleration $|a_c| = 0$. In other words, the particle never turned on its way to reaching the destination point. The only way this could have happened is if it travelled along the $x$ axis in a straight line.

Now, we have seen that the fastest path in the transformed coordinates travels exactly on the $x$ axis so that $y = 0$ anywhere along the fastest path. Notice, however, that the $x$ axis in the transformed coordinates is given exactly by the following line:
\begin{eqnarray}
  y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
\end{eqnarray}

Thus, we see that the fastest path in the original coordinates follows the above equation, which is what we wanted to show.
\qed

% -----------------------------------------------------------------------------

\begin{corollary}
  The fastest path between two points $(x_1, y_1), (x_2, y_2) \in \R^2$ is unique.
\end{corollary}

% -----------------------------------------------------------------------------

\includefig{polar_param.eps}{Particle parameters in polar coordinates. B is center of coordinate system, and p is the particle.}{polar-param}

\begin{lemma}
  For a particle, $p$,
  \begin{align*}
    \frac{dr(t)}{dt} = -s(t) \, \cos\paren{\phi(t) + \theta(t)}\\
    \frac{d\phi(t)}{dt} = -s(t) \, \sin\paren{\phi(t) + \theta(t)}
  \end{align*}
\end{lemma}

\begin{lemma}\label{theta-deriv}
  For a particle, $p$,
  \[
  \frac{d\theta(t)}{dt} = -\frac{a_c(t)}{s(t)}
  \]
\end{lemma}

\begin{lemma}
  For a particle, $p$, with bounded centripetal and tangential acceleration, than the functions $\phi(t)$ and $\theta(t)$ are continuous. Furthermore, for two times $t_1$ and $t_2$, s.t. $t_1 \le t_2$, $\phi(t_1) + \theta(t_1) > a$ and  
\end{lemma}

\proof

The proof follows directly from the fact that the derivatives of $\phi(t)$ and $\theta(t)$ exist: \ref{theta-deriv}).

\begin{lemma}
  For a particle, $p$, with nonzero speed, and no centripetal acceleration for $t \ge t_0$, then
  \[
    \begin{cases}
      \phi(t) \to \theta(t_0) \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
      \phi(t) = 0 \quad \text{for} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
    \end{cases}
  \]
\end{lemma}

### 2013-09-28 particle_definitions.tex
Remove jon-proofs.

@@
 \begin{definition}
-A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $0 \ge t \ge T_{f, \gamma}$, to a position $\bvec{X} \in \mathrm{R}^n$. 
+A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [0, T_{f, \gamma}]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
 \end{definition}
@@
 \end{definition}
+
+% -----------------------------------------------------------------------------
+
+\subsection{Particle Motion in Polar Coordinates}
+
+The motion of the 2-dimensional particles in this paper will typically be described in the polar coordinate system, shown in figure \ref{fig:polar-param}.
+
+\includefig{polar_param.eps}{A particle moving in 2-dimensional polar coordinate system centered at B}{polar-param}
+
+\begin{lemma}
+The time derivative of $\theta$ is given by
+\[
+\frac{d\beta}{dt} = \frac{a_c}{s}
+\]
+\end{lemma}
+
+\begin{proof}
+
+\includefig{theta_deriv.eps}{Tangential acceleration}{theta-deriv}
+
+If we look at a point, $p$, subject to only a centripetal acceleration, $a_c$, the change in $\bvec{v}$ over an infinitesimal time, $dt$, is shown in the figure \ref{fig:theta-deriv} (the two vectors, $\bvec{v}$ and $\bvec{v}+\bvec{dv}$, are superimposed).
+From the definition of $a_c$
+
+\[
+\frac{dv}{dt} = a_c
+\]
+
+So...
+\[
+\frac{d\beta}{dt} = \frac{a_c}{s}
+\]
+\end{proof}
+
+The proof of the lemma in the case where $a_t$ is also nonzero is very similar, since the component of $\bvec{dv}$ in the direction $\bhat{v}$ is negligeable compared to $v$.
+
+Returning again to figure \ref{fig:polar-param}, the following equations can be derived
+
+\begin{align}
+  \frac{dr(t)}{dt}& = -s(t) \, \cos\paren{\theta(t)}\\
+  \frac{d\phi(t)}{dt}& = s(t) \, \sin\paren{\theta(t)}\\
+  \frac{d\theta(t)}{dt}& = \frac{d\phi(t)}{dt} - \frac{a_c(t)}{s(t)}\label{eq:theta-deriv}\\
+  \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{ds(t)}{dt} \cos\paren{\theta(t)} + s(t) \sin\paren{\theta(t)} \frac{d\theta(t)}{dt}
+\end{align}
+
+\begin{lemma}
+  For a particle, $p$, with bounded centripetal and tangential acceleration, then:
+
+  (1) The functions $\phi(t)$ and $\theta(t)$ are continuous.
+
+  (2) For two times $t_1$ and $t_2$, s.t. $t_1 < t_2$, $\theta(t_1) > a$ and $\theta(t_2) < a$, then $\theta(t_c) = a$ for some $t_c \in [t_1, t_2]$.
+\end{lemma}
+
+\begin{proof}
+First off, it should be noted that a solution to \ref{eq:theta-deriv} exists because the rhs is Lipschitz continuous.
+The proof of (1) follows directly from the fact that the derivative of $\theta(t)$ exist and is bounded.
+(2) is just a restatement of the intermediate value theorem.
+\end{proof}
+
+\begin{lemma}
+  For a particle, $p$, with nonzero speed, and no centripetal acceleration for $t \ge t_0$, then
+  \[
+    \begin{cases}
+      \theta(t) \to \pi \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
+      \theta(t) = 0 \quad \text{for} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
+    \end{cases}
+  \]
+\end{lemma}
+
+\begin{proof}
+The second case is the easiest to check,
+
+\end{proof}

### 2013-09-28 path_theorems.tex
Remove jon-proofs.

@@
+\begin{lemma}
+If $a_t=0$ and $\norm{a_c} \le a_{c,max}$, then the minimum radius of curvature of a point trajectory is given by
+\begin{equation}
+R_{min} = \frac{v^2}{a_{c,max}}
+\end{equation}
+\end{lemma}
+
+\begin{theorem}
+For a particle, $p$, traveling along an optimal path, $\hat{\gamma}(t)$ between two points $X_1$ and $X_2$, 
+\end{theorem}
+
+\begin{lemma}
+Every optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$. Every point along an optimal trajectory where $a_t=0$ has $R = \infty$ or $R = R_{min}$.
+\end{lemma}
+
+\proof
+
+If we look at a position, p, on a trajectory. We can align a rectangular coordinate system with this point, such that $\hat{y} = \hat{v}$.
+
+\begin{align}
+a_c& = \ddot{r} - r \dot{\phi}^2\\
+%
+a_t& = \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}}\\
+%
+0& = \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}}\\
+%
+r^2 \dot{\phi}& = constant
+\end{align}
+
+\qed
+
 % -----------------------------------------------------------------------------
@@
 % -----------------------------------------------------------------------------
-
-\includefig{polar_param.eps}{Particle parameters in polar coordinates. B is center of coordinate system, and p is the particle.}{polar-param}
-
-\begin{lemma}
-  For a particle, $p$,
-  \begin{align*}
-    \frac{dr(t)}{dt} = -s(t) \, \cos\paren{\phi(t) + \theta(t)}\\
-    \frac{d\phi(t)}{dt} = -s(t) \, \sin\paren{\phi(t) + \theta(t)}
-  \end{align*}
-\end{lemma}
-
-\begin{lemma}\label{theta-deriv}
-  For a particle, $p$,
-  \[
-  \frac{d\theta(t)}{dt} = -\frac{a_c(t)}{s(t)}
-  \]
-\end{lemma}
-
-\begin{lemma}
-  For a particle, $p$, with bounded centripetal and tangential acceleration, than the functions $\phi(t)$ and $\theta(t)$ are continuous.
-Furthermore, for two times $t_1$ and $t_2$, s.t.
-$t_1 \le t_2$, $\phi(t_1) + \theta(t_1) > a$ and
-\end{lemma}
-
-\proof
-
-The proof follows directly from the fact that the derivatives of $\phi(t)$ and $\theta(t)$ exist: \ref{theta-deriv}).
-
-\begin{lemma}
-  For a particle, $p$, with nonzero speed, and no centripetal acceleration for $t \ge t_0$, then
-  \[
-    \begin{cases}
-      \phi(t) \to \theta(t_0) \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
-      \phi(t) = 0 \quad \text{for} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
-    \end{cases}
-  \]
-\end{lemma}

### 2013-09-28 path_theorems.tex

@@
 \begin{theorem}
-  Given points, $X_1, X_2 \in \R^2$ and a particle $p$ initially at $X_1$ with infinite centripetal acceleration bounded tangential acceleration, $\abs{a_t} \le \bar{a}$, then the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $X_1$ to $X_2$ is the line segment from $X_1$ to $X_2$.
+  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
+  \begin{eqnarray}
+    y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
+  \end{eqnarray}
 \end{theorem}
-
-\proof
-
-Let's transform the problem.
+\proof Let's transform the problem.
 We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis.
@@
 
-Recall that the acceleration of the particle $p$ is bounded by $\bar{a}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
+Recall that the acceleration of the point mass $p$ is bounded by $\bar{a}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
 \begin{eqnarray}
@@
 
-If the particle travels for time $t < \sqrt{\frac{2 x_2}{\bar{a}}}$, then it is impossible for the particle to reach $(x_2, 0)$ when starting at $(0,0)$.
+If the point mass travels for time $t < \sqrt{\frac{2 x_2}{\bar{a}}}$, then it is impossible for the point mass to reach $(x_2, 0)$ when starting at $(0,0)$.
 This is because $p$ cannot reach $(x_2, 0)$ in the $x$ direction when $t < \sqrt{\frac{2 x_2}{\bar{a}}}$ and any acceleration in the $y$ direction would not enable this either.
@@
 This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$.
-Let us examine the path taken by the particle $p$ on this fastest path.
+Let us examine the path taken by the point mass $p$ on this fastest path.
 Recall that $a_t(t) = \bar{a}$ for all $t$ along the fastest path.
 This means that there was no centripetal acceleration $|a_c| = 0$.
-In other words, the particle never turned on its way to reaching the destination point.
+In other words, the point mass never turned on its way to reaching the destination point.
 The only way this could have happened is if it travelled along the $x$ axis in a straight line.
@@
 
-% -----------------------------------------------------------------------------
+\begin{corollary}
+  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ is unique.
+\end{corollary}
+\proof We have already shown that any fastest path between $(x_1, y_1)$ and $(x_2, y_2)$ follows the straight line given by $y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1$.
+Moreover, we showed that when travelling along the fastest path, the particle must have acceleration along the straight line of $\bar{a}$.
+Since we have starting position $(x_1, y_1)$ and initial speed of $0$, the acceleration of the particle $a(t)$ uniquely defines a path for the particle.
 
-\begin{corollary}
-  The fastest path between two points $(x_1, y_1), (x_2, y_2) \in \R^2$ is unique.
-\end{corollary}
+There is only a single function $a(t) = \bar{a}$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
+\qed
 

### 2013-09-28 particle_definitions.tex
Add more proofs.

@@
+In this section, we will provide some basic definitions about particles and paths.
+These will lay the groundwork for thinking about optimal paths.
+We will begin by defining the description of a particle and then define various types of paths along which a particle can travel.
+
 \begin{definition}
@@
 \begin{definition}
-  For a given particle, $p$, a fastest path, $\hat{\gamma}(t)$, between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
+  For a given particle, $p$, a fastest path, $\hat{\gamma}(t)$, between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_{f,\hat{\gamma}} \leq T_{f,\gamma}$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
 \end{definition}
@@
 \begin{definition}
-  The centripetal acceleration, $\bvec{a_c}$, of a particle, $p$, is the component of the acceleration of $p$ perpendicular to its direction of motion, $\bhat{v}$.
-The sign of $a_c$ is difined as the sign of the projection of $\bhat{a_c}$ onto $\bhat{r}$.
+  A particle's velocity is defined as
+
+  \[\bvec{v} \coloneqq \frac{d\bvec{X}}{dt}\]
+
+  A particle's speed is $v$, and its direction of motion is $\bhat{v}$
+
 \end{definition}
@@
 \begin{definition}
-  The tangential acceleration, $\bvec{a_t}$, of a particle, $p$, is the component of the acceleration of $p$ in its direction of motion, $\bhat{v}$.
+  A particle's acceleration is defined as
+
+  \[\bvec{a} \coloneqq \frac{d\bvec{v}}{dt}\]
+\end{definition}
+
+\begin{definition}
+  The centripetal acceleration, $\bvec{a_c}$, of a particle, $p$, is the component of the acceleration of $p$ perpendicular to its direction of motion.
+
+  In rectangular coordinates, the sign of $a_c$ is the projection of $\bhat{a_c}$ onto $\bhat{x}$.
+
+  In polar coordinates, the sign of $a_c$ is difined as the sign of the projection of $\bhat{a_c}$ onto $\bhat{r}$.
+\end{definition}
+
+\begin{definition}
+  The tangential acceleration, $\bvec{a_t}$, of a particle, $p$, is the component of the acceleration of $p$ in its direction of motion, $\bhat{v}$. $a_t = \frac{ds}{dt}$.
 \end{definition}
@@
 
-The motion of the 2-dimensional particles in this paper will typically be described in the polar coordinate system, shown in figure \ref{fig:polar-param}.
+The motion of the 2-dimensional particles in this paper will be described in the polar coordinate system, shown in Figure \ref{fig:polar-param}.
 
@@
 
+If we look at a point, $p$, subject to only centripetal acceleration, $a_c$, the change in $\bvec{v}$ over an infinitesimal time, $dt$, is shown in Figure \ref{fig:theta-deriv} (the two vectors, $\bvec{v}$ and $\bvec{v}+\bvec{dv}$, are superimposed).
+
 \includefig{theta_deriv.eps}{Tangential acceleration}{theta-deriv}
 
-If we look at a point, $p$, subject to only a centripetal acceleration, $a_c$, the change in $\bvec{v}$ over an infinitesimal time, $dt$, is shown in the figure \ref{fig:theta-deriv} (the two vectors, $\bvec{v}$ and $\bvec{v}+\bvec{dv}$, are superimposed).
 From the definition of $a_c$
@@
 \[
-\frac{d\beta}{dt} = \frac{a_c}{s}
+\frac{d\beta}{dt} = \frac{a_c}{v}
 \]
@@
 
-Returning again to figure \ref{fig:polar-param}, the following equations can be derived
+Returning again to Figure \ref{fig:polar-param}, the following equations can be derived
 
 \begin{align}
-  \frac{dr(t)}{dt}& = -s(t) \, \cos\paren{\theta(t)}\\
-  \frac{d\phi(t)}{dt}& = s(t) \, \sin\paren{\theta(t)}\\
-  \frac{d\theta(t)}{dt}& = \frac{d\phi(t)}{dt} - \frac{a_c(t)}{s(t)}\label{eq:theta-deriv}\\
-  \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{ds(t)}{dt} \cos\paren{\theta(t)} + s(t) \sin\paren{\theta(t)} \frac{d\theta(t)}{dt}
+  \frac{dr(t)}{dt}& = -s(t) \, \cos\paren{\theta(t)}\label{eq:r-deriv}\\
+  \frac{d\phi(t)}{dt}& = s(t) \, \sin\paren{\theta(t)}\label{eq:phi-deriv}\\
+  \frac{d\theta(t)}{dt}& = \frac{d\phi(t)}{dt} - \frac{a_c(t)}{s(t)}\\
+  &= s(t) \, \sin\paren{\theta(t)} - \frac{a_c(t)}{s(t)}\label{eq:theta-deriv}\\
+  \intertext{Applying the chain rule to (\ref{eq:r-deriv})}
+  \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{ds(t)}{dt} \cos\paren{\theta(t)} + s(t) \sin\paren{\theta(t)} \frac{d\theta(t)}{dt}\\
+  &\begin{aligned}
+    = -\frac{ds(t)}{dt} \cos\paren{\theta(t)} &+ s(t)^2 \sin^2\paren{\theta(t)}\\
+    &\qquad - s(t) \sin\paren{\theta(t)} \frac{a_c(t)}{s(t)}\label{eq:r-deriv-2}
+  \end{aligned}
 \end{align}
@@
 
-  (1) The functions $\phi(t)$ and $\theta(t)$ are continuous.
+  1. The functions $\phi(t)$ and $\theta(t)$ are continuous.
 
-  (2) For two times $t_1$ and $t_2$, s.t. $t_1 < t_2$, $\theta(t_1) > a$ and $\theta(t_2) < a$, then $\theta(t_c) = a$ for some $t_c \in [t_1, t_2]$.
+  2. For two times $t_1$ and $t_2$, s.t. $t_1 < t_2$, $\theta(t_1) > a$ and $\theta(t_2) < a$, then $\theta(t_c) = a$ for some $t_c \in [t_1, t_2]$.
 \end{lemma}
@@
 \begin{proof}
-First off, it should be noted that a solution to \ref{eq:theta-deriv} exists because the rhs is Lipschitz continuous.
-The proof of (1) follows directly from the fact that the derivative of $\theta(t)$ exist and is bounded.
-(2) is just a restatement of the intermediate value theorem.
+First off, it should be noted that a solution to \ref{eq:theta-deriv} exists because the right hand side is Lipschitz continuous.
+The proof of 1.\ follows directly from the fact that the derivative of $\theta(t)$ exist and is bounded.
+2.\ is just a restatement of the intermediate value theorem.
 \end{proof}
@@
 \begin{proof}
-The second case is the easiest to check,
+
+For the first case
+
+The second case is the easiest to check. If we plug $\theta(t_0) = 0$ into \ref{eq:theta-deriv}, we get
+
+\begin{align*}
+\frac{d\theta(t)}{dt} = 0 \qquad \text{for} \;\; t \ge t_0\\
+\intertext{So...}
+\theta(t) = 0 \qquad \text{for} \;\; t \ge t_0
+\end{align*}
 

### 2013-09-28 path_theorems.tex
Add more proofs.

@@
 \begin{lemma}
-If $a_t=0$ and $\norm{a_c} \le a_{c,max}$, then the minimum radius of curvature of a point trajectory is given by
+If $a_t=0$ and $\norm{a_c} \le a_{c,max}$, then the minimum radius of curvature of a point's trajectory is given by
 \begin{equation}
@@
 \end{lemma}
+
+\begin{proof}
+This comes directly from the definition of radius of curvature as
+
+\[
+R = \frac{v^2}{a_c}
+\]
+\end{proof}
 

### 2013-09-29 cone_theorems.tex
Add cone proofs.

@@
+Now we are finally able to tackle the model problem of optimal paths around cones.
+The cone problem we will solve will involve only 3 cones, but first we will solve a simpler but related problem of minimizing the path length around a quadrilateral.
+
 \subsection{Quadrilateral}
 
-Before we attempt to tackle the problem of finding the optimal path around a cone at constant velocity, we may want to find some intuition for the problem with a simple, but related problem.
-In particular, if a particle is traveling around a cone, we would like to know what circle it traces as it goes around the cone.
+We would like to minimize the path length around the quadrilateral shown in Figure \ref{fig:quad}.
 
@@
 
-To make a simple model of this problem, we will use a quadrilateral to model a path around a cone.
-We will construct a quadrilateral with particular constaints that models the constraints of a path around a cone, and we will try to find the parameters that minimize the perimeter around the quadrilateral.
-Let us call the sides of the quadrilateral $s_1, s_2, s_3$ and $s_4$.
-Imagine that $s_1$ and $s_2$ are on opposite sides of the quadrilateral with fixed lengths $l_1$ and $l_2$ respectively.
-Now we will constrain the problem to be related to the problem of a particle traveling around a cone: imagine $s_1$ and $s_2$ are connected by a bar $s_b$ of length $d$.
-The bar will be perpendicular to $s_1$.
-The angle that $s_b$ forms with $s_2$ will be called $\theta$.
-We will try to find the optimal $\theta$ that minimizes the perimeter around the quadrilateral.
+We will constrain the problem such that it is similar to the problem of a particle traveling around a cone.
+Sides $\overline{BC}$, $\overline{DA}$, and $\overline{EF}$ have fixed lengths $l_1$, $l_2$, and $w$ respectively.
+Points E and F bisect $\overline{DA}$ and $\overline{BC}$ respectively.
+The goal is
 
-\subsection{Symmetric Quadrilateral}
+\[
+\argmin_{\theta} \bracket{l_{AB} + l_{BC} + l_{CD}}
+\]
 
-Let us begin by solving the simplest version of this problem.
-Let us imagine that $s_b$ is connected to the midpoints of $s_1$ and $s_2$.
-We know that the perimeter will be given by $l_1 + l_2 + l_3 + l_4$ where $l_3$ and $l_4$ are the lengths of the sides of $s_3$ and $s_4$, respectively.
-We are given $l_1$ and $l_2$, but we will need to compute $l_3$ and $l_4$ as functions of $l_1, l_2,d, $ and $\theta$.
+\begin{align}
+  x_c& = w - \frac{l2}{2 \cos{\theta}}\\
+  y_c& = \frac{l_2}{2} - \frac{l_2}{2 \sin{\theta}}\\
+  l_{AB}& = \sqrt{x_c^2 + y_c^2}\\
+  & = \sqrt{ \paren{\frac{l_1}{2} - \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }\\
+  l_{BC}& = l2\\
+  l_{CD}& = \sqrt{\paren{\frac{l_1}{2} + \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }
+\end{align}
 
-We can find $l_3$ by using the fact that it forms a right triangle.
-We know that $l_3^2 = m^2 + n^2$.
-Finding $l_4$ is similar.
-Therefore, we just need to find $m$ and $n$.
-This can be done by using the fact that $m = \frac{l_1}{2} - \frac{l_2}{2} \sin \theta$.
-This is just the upper half of $s_1$ minus the projection of $s_2$ onto $s_1$.
-We can find $n$ similarly: $n = d - \frac{l_2}{2} \cos \theta$.
-This is just the bar $s_b$ minus the projection of $s_2$ onto the bar.
-Thus by substituting, we have:
-\begin{eqnarray}
-  l_3 = \sqrt{ \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d - \frac{l_2}{2} \cos \theta \right)^2 }
-\end{eqnarray}
+Since we know that $l_{BC}$ is fixed the problem reduces to
 
-We can do a similar analysis on $l_4$, only remembering that $n$ for $l_4$ gets extended by the projection onto $s_4$ instead of shrunken. We therefore have:
-\begin{eqnarray}
-  l_4 = \sqrt{ \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2 }
-\end{eqnarray}
+\[
+\argmin_{\theta} \bracket{l_{AB} + l_{BC} + l_{CD}}
+\]
 
-Now, to minimize the perimeter with respect to $\theta$, we want to minimize $l_1 + l_2 + l_3 + l_4$.
-Since we know that $l_1$ and $l_2$ are fixed, we really want to minimize $l_3 + l_4$ with respect to $\theta$.
-The other thing to note is that we're minimizing positive distances.
-We will invoke the following lemma so that we can simplify our expression for $\min l_3 + l_4$:
+Because all distances are positive, we can use Lemma \ref{lemma:conv-argmin}, defined in the Appendix, to simplify our problem:
 
-\begin{lemma}
-  If $f(t), g(t) > 0$ and $k(t) > 0$ is a strictly monotonically increasing function for all $t$, then $\argmin_t k(f(t)) + k(g(t)) = \argmin_t f(t) + g(t)$.
-  \label{lemma:minsqrt}
-\end{lemma}
-\proof Let $t_1, t_2$ be such that $f(t_1) + g(t_1) < f(t_2) + g(t_2)$.
-In this proof, we will show that $k(f(t_1)) + k(g(t_1)) < \sqrt{f(t_2)} + \sqrt{g(t_2)}$.
-Since $k(t)$ is a strictly monotonically increasing function when $t > 0$, we know that $k(x) < k(y)$ if and only if $x < y$ (assuming we can confine $x, y$ to be non-negative).
+If we define $l_{AB} = \sqrt{z_{AB}}$ and $l_{CD} = \sqrt{z_{CD}}$, we can use \ref{lemma:conv-argmin} with $k(t) = \sqrt{t}$ to simplify our problem to
 
-Because this is the case, we see that $k(f(x)) < k(f(y))$ if and only if $f(x) < f(y)$ (the same goes for $g$).
-Thus, we see that if we have found the minimum $t_m$ to $\argmin_t k(f(t)) + k(g(t))$, then it is the case that $k(f(t_m)) + k(g(t_m)) < k(f(t)) + k(g(t))$ for all $t \neq t_m$ (again where $t > 0$).
-Following our train of logic, we see that $f(t_m) + g(t_m) < f(t) + g(t)$ for all $t \neq t_m$, which means that $t_m$ is a minimum of $f(t) + g(t)$.
-Thus by finding a minimum $t_m$ to $k(f(t)) + k(g(t))$, we also found a minimum to $f(t) + g(t)$.
-\qed
+\begin{multline}
+  \argmin_{\theta} \left[ 2\paren{\frac{l_1}{2} - \frac{l_2}{2 \sin\theta}}^2 \right.\\
+  \left. + \paren{w - \frac{l_2}{2 \cos\theta}}^2 + \paren{w + \frac{l_2}{2 \cos\theta}}^2 \right]
+\end{multline}
 
-Since we've proven this lemma, we can invoke it upon $\min l_3 + l_4$.
-Since $l_3 = \sqrt{z_3}$ and $l_4 = \sqrt{z_4}$, we can use $k(t) = \sqrt{t}$ and we can write $\min l_3 + l_4 = \min z_3 + z_4$ by using our lemma.
-Thus, we now want to solve the problem:
-\begin{eqnarray}
-  \argmin_{\theta} &2& \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 \\
-  &+& \left( d - \frac{l_2}{2} \cos \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2
-\end{eqnarray}
-
-Now, we can expand out our expression and use the fact that $\sin^2 \theta + \cos^2 \theta = 1$ to obtain a much simpler (but equivalent) minimization problem:
+Now, we can expand out our expression and use Lemma the fact that $\sin^2 \theta + \cos^2 \theta = 1$ to obtain a much simpler (but equivalent) minimization problem:
 \begin{eqnarray}
@@
 
-Thus, we see that $\theta = \frac{\pi}{2}$ minimizes the perimeter of the quadrilateral in the symmetric case.
-
 % -----------------------------------------------------------------------------
@@
 
-Given a cone setup consisting of 3 cones at locations $X_A$, $X_B$, and $X_C$.
+Given a particle with zero tangential acceleration and bounded centripetal acceleration, $a_c \le a_{c,max}$, and a cone setup consisting of 3 cones, A, B, and C, at locations $\bvec{X_A}$, $\bvec{X_B}$, and $\bvec{X_C}$ as is shown in Figure \ref{fig:3-cones}.
 
-\includefig{cones_fix_s.eps}{A}{cones-fix-s}
+\includefig{3_cones.eps}{3 Cone setup}{3-cones}
 
-\begin{align}
-dB& = \sqrt{x_B + y_B}\\
-\intertext{Applying the triangle inequality...}
-d_c& = \alpha_c - \tan^{-1}\paren{\frac{y_B}{x_B}}\\
-\end{align}
-
-\includefig{cones_fix_s_2.eps}{A}{cones-fix-s-2}
-
-\begin{align}
-l_1& = \sqrt{d_c - r}\\
-x_c = x_B - r \cos{\alpha_c}\\
-y_c = y_B - r \sin{\alpha_c}\\
-d_c& = \alpha_c - \tan^{-1}\paren{\frac{y_c}{x_c}}\\
-\end{align}
+The optimal path [TODO]
 
@@
 
-\proof
+\begin{proof}
+Since speed is constant, the optimal path will be the shortest path. The optimal path is of the form, tr. Thus, the problem reduces to a trigonometric problem.
+
+\includefig{cones_fix_s.eps}{Position of center of turn}{cones-fix-s}
+
+The turn must touch the cone B, otherwise the trajectory will either not go around the cone, or be longer than necessary. Therefor, the center of the turn must be a distance $r$ away from
+
+\includefig{cones_fix_s_2.eps}{Path length}{cones-fix-s-2}
+
+\begin{align*}
+x_c = x_B - r \cos{\alpha_c}\\
+y_c = y_B - r \sin{\alpha_c}\\
+l_1& = \sqrt{d_c - r}\\
+l_2& = r \paren{\alpha_c - \tan^{-1}\paren{\frac{y_c}{x_c}}}\\
+\end{align*}
+\end{proof}

### 2013-09-29 introduction.tex
Add cone proofs.

Our model problem is a particle moving in $\R^2$ with constrained acceleration. The particle must navigate around cones (points in $\R^2$) to reach a final position. The goal is to minimize the total time spend navigating to the final position.

In this paper, we first present a polar coordinate representation of a particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system. This allows us to devise some simple lemmas about the motion of the particle.

After developing an intuition for particles and particle paths, we then move on to the more complicated problem of deriving governing rules for optimal paths between points.

Finally, we are able to tackle the problem of finding an optimal path around cones.

### 2013-09-29 math_review.tex
Add more proofs.
Add cone proofs.

@@
-\subsection{Coordinate Systems\label{sec:notation}}
+\subsection{Analysis}
 
-\subsubsection{Time Derivatives}
+\begin{lemma}\label{lemma:conv-argmin}
+  If $f(t), g(t) > 0$ and $k(t) > 0$ is a strictly monotonically increasing function for all $t$, then $\argmin_t k(f(t)) + k(g(t)) = \argmin_t f(t) + g(t)$.
+  \label{lemma:minsqrt}
+\end{lemma}
+\begin{proof}
+Let $t_1, t_2$ be such that $f(t_1) + g(t_1) < f(t_2) + g(t_2)$.
+In this proof, we will show that $k(f(t_1)) + k(g(t_1)) < \sqrt{f(t_2)} + \sqrt{g(t_2)}$.
+Since $k(t)$ is a strictly monotonically increasing function when $t > 0$, we know that $k(x) < k(y)$ if and only if $x < y$ (assuming we can confine $x, y$ to be non-negative).
 
-\begin{align*}
-\dot{a}& = \frac{da}{dt}\\
-%
-\ddot{a}& = \frac{d^2a}{dt^2}
-\end{align*}
+Because this is the case, we see that $k(f(x)) < k(f(y))$ if and only if $f(x) < f(y)$ (the same goes for $g$).
+Thus, we see that if we have found the minimum $t_m$ to $\argmin_t k(f(t)) + k(g(t))$, then it is the case that $k(f(t_m)) + k(g(t_m)) < k(f(t)) + k(g(t))$ for all $t \neq t_m$ (again where $t > 0$).
+Following our train of logic, we see that $f(t_m) + g(t_m) < f(t) + g(t)$ for all $t \neq t_m$, which means that $t_m$ is a minimum of $f(t) + g(t)$.
+Thus by finding a minimum $t_m$ to $k(f(t)) + k(g(t))$, we also found a minimum to $f(t) + g(t)$.
+\end{proof}
+
+\subsection{Coordinate Systems}
 
@@
 
-\begin{align}
-R& = \abs{\frac{\paren{\dot{x}^2 + \dot{y}^2}^{3/2}}{\dot{x}\ddot{y} - \dot{y}{\ddot{x}}}}\\
-%
-&= \abs{\frac{s^2}{a_t}}\tag{for $a_c = $}
-\end{align}
+For $a_t = 0$
 
-\subsection{Scalar Calculus in Polar Coordinates}
-
-\begin{align}
-s& = \frac{dl}{dt}\\
-%
-a_t& = \frac{ds}{dt}\\
-\end{align}
+\[
+R= \abs{\frac{v^2}{a_c}}
+\]
 
@@
 
-\begin{align}
+\begin{align*}
 \boldsymbol{x}& = r \boldsymbol{\hat{r}}\\
-%
 \boldsymbol{\vec{v}}& = \dot{r} \boldsymbol{\hat{r}} + r \dot{\phi} \boldsymbol{\hat{\phi}}\\
-%
 \label{eq:a_vec_def}\boldsymbol{\vec{a}}& = \paren{\ddot{r} - r \dot{\phi}^2} \boldsymbol{\hat{r}} + \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}} \boldsymbol{\hat{\phi}}
-\end{align}
-
-\subsection{Relations}
-
-\begin{align}
-l& = \int_{t=0}^{T} \norm{\boldsymbol{\vec{v}} \, } \; dt\\
-%
-s& = \norm{\boldsymbol{\vec{v}}}\\
-%
-a_t& = \norm{\boldsymbol{\vec{a}}} \cdot \boldsymbol{\hat{v}} = \norm{\boldsymbol{\vec{a}}} \cdot \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}}}\\
-%
-a_c& = \norm{\boldsymbol{\vec{a}}} \times \boldsymbol{\hat{v}} = \norm{\boldsymbol{\vec{a}}} \times \frac{\boldsymbol{\vec{v}}}{\norm{\boldsymbol{\vec{v}}}}
-\end{align}
+\end{align*}

### 2013-09-29 paper.tex
Add more proofs.
Add cone proofs.

@@
 
-\title[The 18.821 report]{The 18.821 Mathematics Project Lab Report 
-[Proofs]} 
-% the first [...] gives a brief version of the title, which is long!
+\title[Optimal Paths in R2]{Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration}
 
@@
 \maketitle
+
+\subsection*{Abstract}
+
+Optimal particle paths in $\R^2$ between points and around points are investigated in this paper.
+A paramerization of a particle's motion around a point is defined.
+From this parameterization, we derive a general solution for an optimal path with constant speed between 2 points.
+The results of this paper can by applied towards calculating optimal object trajectories in physics when acceleration is constrained.
 
@@
 
+\section{Conclusion}
+\input{conclusion.tex}
+
 \section*{Appendix}
@@
 
-\bibliographystyle{plain}
-\begin{thebibliography}{9}
-\bibitem{wiki_pcoords}
-\url{http://en.wikipedia.org/wiki/Polar_coordinate_system}
-\end{thebibliography}
+\input{bibliography.tex}
 
 \end{document}
-
-From Spring 2011 or before; revised by Miller, Spring 2013.

### 2013-09-29 particle_definitions.tex
Add cone proofs.

@@
-In this section, we will provide some basic definitions about particles and paths.
-These will lay the groundwork for thinking about optimal paths.
-We will begin by defining the description of a particle and then define various types of paths along which a particle can travel.
+In this section, we will provide some basic definitions about particles and paths. These will lay the groundwork for thinking about optimal paths.
 
@@
 \begin{definition}
-  A n-dimensional particle, $p$, is an object with zero volume that travels along a n-dimensional path. The particle may have conditions on its position, velocity, and acceleration in $\R^n$.
+  A n-dimensional particle, $p$, is an object with zero volume that travels along a n-dimensional path.
+Traveling along a path means that the particle is at position $\lambda(t)$ at time $t$, for all $t \in [0, T_{f,\lambda}]$.
+The particle may have conditions on its position, velocity, and acceleration in $\R^n$.
 \end{definition}
@@
 \begin{definition}
-  A valid path $\gamma(t)$ for a particle $p$ is a path such that all conditions on the particle are satisfied at every point along the path.
+  A valid path $\gamma(t)$ for a particle $p$ is a path along which $p$ can travel, such that all its conditions are satisfied at every point along the path.
 \end{definition}
@@
 \begin{definition}
-  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$ where $\gamma(0) = \bvec{X_1}$ and $\gamma(T_{f, \gamma}) = \bvec{X_2}$.
+  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$, where $\gamma(0) = \bvec{X_1}$ and $\gamma(T_{f, \gamma}) = \bvec{X_2}$.
 \end{definition}
@@
 
-  A particle's speed is $v$, and its direction of motion is $\bhat{v}$
+  Furthermore, a particle's speed is $v$, and its direction of motion is $\bhat{v}$
 
@@
 \begin{definition}
-  The centripetal acceleration, $\bvec{a_c}$, of a particle, $p$, is the component of the acceleration of $p$ perpendicular to its direction of motion.
+  The centripetal acceleration, $\bvec{a_c}$, of a particle, $p$, is the component of its acceleration in the direction perpendicular to its direction of motion.
 
-  In rectangular coordinates, the sign of $a_c$ is the projection of $\bhat{a_c}$ onto $\bhat{x}$.
+  In rectangular coordinates, the sign of $a_c$ is defined to be the sign of the projection of $\bhat{a_c}$ onto $\bhat{x}$.
 
-  In polar coordinates, the sign of $a_c$ is difined as the sign of the projection of $\bhat{a_c}$ onto $\bhat{r}$.
+  In polar coordinates, the sign of $a_c$ is defined to be the sign of the projection of $\bhat{a_c}$ onto $\bhat{r}$.
 \end{definition}
@@
 \begin{definition}
-  The tangential acceleration, $\bvec{a_t}$, of a particle, $p$, is the component of the acceleration of $p$ in its direction of motion, $\bhat{v}$. $a_t = \frac{ds}{dt}$.
+  The tangential acceleration, $\bvec{a_t}$, of a particle, $p$, is the component of the acceleration of $p$ in its direction of motion, $\bhat{v}$.
+
+  \[
+  a_t = \frac{dv}{dt}
+  \]
 \end{definition}
@@
 
-The motion of the 2-dimensional particles in this paper will be described in the polar coordinate system, shown in Figure \ref{fig:polar-param}.
+Unless otherwise specified, the motion of 2-dimensional particles in this paper will be described in polar coordinates, along with an extra parameter $\theta$ as is shown in Figure \ref{fig:polar-param}.
 
 \includefig{polar_param.eps}{A particle moving in 2-dimensional polar coordinate system centered at B}{polar-param}
+
+$\theta(t), \phi(t) \in [-\pi, \pi]$. From now on, $\abs{\theta}$ and $\abs{\phi}$ will be used, since there is a symmetry in the system about $\bhat{r}$.
 
@@
 \[
-\frac{d\beta}{dt} = \frac{a_c}{s}
+\frac{d\abs{\theta(t)}}{dt} = \frac{a_c}{v}
 \]
@@
 
-So...
+Since $dv = d\abs{\theta} v$, then
 \[
-\frac{d\beta}{dt} = \frac{a_c}{v}
+\frac{d\abs{\theta}}{dt} = \frac{a_c}{v}
 \]
@@
 
-The proof of the lemma in the case where $a_t$ is also nonzero is very similar, since the component of $\bvec{dv}$ in the direction $\bhat{v}$ is negligeable compared to $v$.
+The proof of the lemma in the case where $a_t$ is also nonzero is very similar, since the component of $\bvec{dv}$ in the direction $\bhat{v}$ is negligible compared to $v$.
 
@@
 \begin{align}
-  \frac{dr(t)}{dt}& = -s(t) \, \cos\paren{\theta(t)}\label{eq:r-deriv}\\
-  \frac{d\phi(t)}{dt}& = s(t) \, \sin\paren{\theta(t)}\label{eq:phi-deriv}\\
-  \frac{d\theta(t)}{dt}& = \frac{d\phi(t)}{dt} - \frac{a_c(t)}{s(t)}\\
-  &= s(t) \, \sin\paren{\theta(t)} - \frac{a_c(t)}{s(t)}\label{eq:theta-deriv}\\
+  \frac{dr(t)}{dt}& = -v(t) \, \cos\paren{\abs{\theta(t)}}\label{eq:r-deriv}\\
+  \frac{d\abs{\phi(t)}}{dt}& = \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}}\label{eq:phi-deriv}\\
+  \frac{d\abs{\theta(t)}}{dt}& = \frac{d\abs{\phi(t)}}{dt} - \frac{a_c(t)}{v(t)}\\
+  &= \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}} - \frac{a_c(t)}{v(t)}\label{eq:theta-deriv}\\
   \intertext{Applying the chain rule to (\ref{eq:r-deriv})}
-  \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{ds(t)}{dt} \cos\paren{\theta(t)} + s(t) \sin\paren{\theta(t)} \frac{d\theta(t)}{dt}\\
+  \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{dv(t)}{dt} \cos\paren{\abs{\theta(t)}} + v(t) \sin\paren{\abs{\theta(t)}} \frac{d\abs{\theta(t)}}{dt}\\
   &\begin{aligned}
-    = -\frac{ds(t)}{dt} \cos\paren{\theta(t)} &+ s(t)^2 \sin^2\paren{\theta(t)}\\
-    &\qquad - s(t) \sin\paren{\theta(t)} \frac{a_c(t)}{s(t)}\label{eq:r-deriv-2}
+    = -\frac{dv(t)}{dt} \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
+    &\qquad - v(t) \sin\paren{\abs{\theta(t)}} \frac{a_c(t)}{v(t)}\label{eq:r-deriv-2}
   \end{aligned}
@@
 
-  1. The functions $\phi(t)$ and $\theta(t)$ are continuous.
+  1. The function $\abs{\theta(t)}$ is continuous.
 
-  2. For two times $t_1$ and $t_2$, s.t. $t_1 < t_2$, $\theta(t_1) > a$ and $\theta(t_2) < a$, then $\theta(t_c) = a$ for some $t_c \in [t_1, t_2]$.
+  2. Given $t_1, t_2 \in \R^2$, s.t. $t_1 < t_2$, $\theta(t_1) > a$ and $\theta(t_2) < a$, then $\theta(t_c) = a$ for some $t_c \in [t_1, t_2]$.
 \end{lemma}
@@
 \begin{proof}
-First off, it should be noted that a solution to \ref{eq:theta-deriv} exists because the right hand side is Lipschitz continuous.
-The proof of 1.\ follows directly from the fact that the derivative of $\theta(t)$ exist and is bounded.
+First off, it should be noted that a solution to (\ref{eq:theta-deriv}) exists because the right hand side is Lipschitz continuous.
+The proof of 1.\ follows directly from the fact that the derivative of $\abs{\theta(t)}$ exists and is bounded.
 2.\ is just a restatement of the intermediate value theorem.
@@
 
-\begin{lemma}
-  For a particle, $p$, with nonzero speed, and no centripetal acceleration for $t \ge t_0$, then
+\begin{lemma}\label{lemma:polar-assymptote}
+  For a particle, $p$, with nonzero speed, and zero centripetal acceleration for $t \ge t_0$, then
   \[
     \begin{cases}
-      \theta(t) \to \pi \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
-      \theta(t) = 0 \quad \text{for} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
+      \abs{\theta(t)} \to \pi \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
+      \abs{\theta(t)} = 0 \quad \text{for all} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
+    \end{cases}
+  \]
+
+    Furthermore,
+
+  \[
+    \begin{cases}
+      r(t) \to \infty \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
+      r(t) \to 0 \quad \text{as} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
     \end{cases}
@@
 
-For the first case
+For the first case, $\frac{d\abs{\theta(t)}}{dt} > 0$, except when $\abs{\theta(t)} = 0, \pi$, which means that $\theta(t)$ is monotonically increasing.
+Since $\phi(t)$ is bounded above py $\pi$, $\phi(t) \to \pi \;\; \text{as} \;\; \infty$.
 
@@
 \begin{align*}
-\frac{d\theta(t)}{dt} = 0 \qquad \text{for} \;\; t \ge t_0\\
-\intertext{So...}
-\theta(t) = 0 \qquad \text{for} \;\; t \ge t_0
+\frac{d\abs{\theta(t)}}{dt} = 0 \qquad \text{for} \;\; t \ge t_0\\
+\intertext{So}
+\abs{\theta(t)} = 0 \qquad \text{for} \;\; t \ge t_0
 \end{align*}
 
+[TODO]
+
 \end{proof}

### 2013-09-29 path_theorems.tex
Add cone proofs.

--- 2013-09-28 path_theorems.tex
@@
+The simplest problem to tackle first, is the optimal trajectory from a current position, $\bvec{X_0}$ to a final position, $\bvec{X_f}$.
+Working in a polar coordinate system centered on $X_f$, it is clear, that our goal is achieved when $r = 0$.
+Furthermore, $\theta(t)$ must be $0$ before reaching $X_f$, otherwise, it will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-deriv}).
+
 \begin{lemma}
-If $a_t=0$ and $\norm{a_c} \le a_{c,max}$, then the minimum radius of curvature of a point trajectory is given by
+If $a_t=0$ and $a_c \le a_{c,max}$, then the minimum radius of curvature of a particle's trajectory is given by
 \begin{equation}
@@
 
+\begin{proof}
+This comes directly from the definition of radius of curvature
+
+\[
+R = \frac{v^2}{a_c}
+\]
+
+and the fact that
+
+\[
+a_c \le a_{c,max} \to \frac{1}{a_c} \ge \frac{1}{a_{c,max}}
+\]
+\end{proof}
+
 \begin{theorem}
-For a particle, $p$, traveling along an optimal path, $\hat{\gamma}(t)$ between two points $X_1$ and $X_2$, 
+Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal path, $\hat{\gamma}(t)$ between two points $X_1$ and $X_2$, has a radius of curvature of $0$ or $a_{c,max}$ at every point along it.
 \end{theorem}
 
-\begin{lemma}
-Every optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$. Every point along an optimal trajectory where $a_t=0$ has $R = \infty$ or $R = R_{min}$.
-\end{lemma}
+\begin{proof}
+[TODO]
+\end{proof}
 
-\proof
+\begin{corollary}
+Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.
+\end{corollary}
 
-If we look at a position, p, on a trajectory. We can align a rectangular coordinate system with this point, such that $\hat{y} = \hat{v}$.
-
-\begin{align}
-a_c& = \ddot{r} - r \dot{\phi}^2\\
-%
-a_t& = \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}}\\
-%
-0& = \frac{1}{r} \frac{d}{dt} \paren{r^2 \dot{\phi}}\\
-%
-r^2 \dot{\phi}& = constant
-\end{align}
-
-\qed
+\begin{proof}
+[TODO]
+\end{proof}
 
@@
 \begin{theorem}
-  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
-  \begin{eqnarray}
-    y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
-  \end{eqnarray}
+  Given a 2-dimensional particle $p$ whose initial position is $\bvec{X_1}$ and moves with bounded tangential acceleration, $a_t \le a_{t,max}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ is the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
 \end{theorem}
-\proof Let's transform the problem.
-We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis.
-In this new coordinate system, we have transformed the following:
-\begin{eqnarray}
-  (x_1, y_1) &\to& (0,0) \\
-  (x_2, y_2) &\to& (x_2', 0)
-\end{eqnarray}
 
-For convenience of notation, we will now refer to $x_2'$ as $x_2$.
+\begin{proof}
 
-Now let us examine the particle's motion in the $x$ direction.
-Let $a_t(t)$ be the tangential acceleration at time $t$ in the $x$ direction.
-Then we can obtain the speed of the particle $s(t)$ at time $t$ in the $x$ direction like so:
-\begin{eqnarray}
-  s(t) = \int_0^t a_t(t_1) dt_1
-\end{eqnarray}
+Without loss of generality, we can define a cartesian coordinate system, where the origin is at $\bvec{X_1}$ and the positive x-axis passes through $\bvec{X_2}$.
 
-To find the distance $d(t)$ travelled up to time $t$ in the $x$ direction, we can use the relation:
-\begin{eqnarray}
-  d(t) &=& \int_0^t s(t_2) dt_2 \\
-       &=& \int_0^t \int_0^t a_t(t_1) dt_1 dt_2
-\end{eqnarray}
+Now let us examine the particle's motion in the $\bhat{x}$ direction. The speed of the particle is the following
+\begin{equation}
+  v_x(t) = \int_0^t a_x(t_1) dt_1
+\end{equation}
 
-Recall that the acceleration of the point mass $p$ is bounded by $\bar{a}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
-\begin{eqnarray}
-  d(t) &\leq& \int_0^t \int_0^t \bar{a} dt_1 dt_2 \\
-       &=& \frac{\bar{a} t^2}{2}
-\end{eqnarray}
+To find the distance $l_x(t)$ travelled in the $\bhat{x}$ direction, we can use the relation:
+\begin{align}
+  d(t) &= \int_0^t v_x(t_2) dt_2 \\
+  &= \int_0^t \int_0^t a_x(t_1) dt_1 dt_2
+\end{align}
+
+Recall that the tangential acceleration of the point mass $p$ is bounded by $a_{t,max}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
+\begin{align}
+  d(t) &\leq \int_0^t \int_0^t \bar{a} dt_1 dt_2\\
+  &= \frac{\bar{a} t^2}{2}
+\end{align}
 
@@
 Notice, however, that the $x$ axis in the transformed coordinates is given exactly by the following line:
-\begin{eqnarray}
+\begin{equation}
   y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
-\end{eqnarray}
+\end{equation}
 
 Thus, we see that the fastest path in the original coordinates follows the above equation, which is what we wanted to show.
-\qed
+\end{proof}
 

### 2013-09-29 cone_theorems.tex
Finish adding 3 cone proof.

@@
-Now we are finally able to tackle the model problem of optimal paths around cones.
-The cone problem we will solve will involve only 3 cones, but first we will solve a simpler but related problem of minimizing the path length around a quadrilateral.
+Now we are finally able to tackle the model problem of optimal paths around cones. First we will solve a simpler but related problem of minimizing the path length around a quadrilateral.
 
@@
 \begin{align}
-  x_c& = w - \frac{l2}{2 \cos{\theta}}\\
+  x_c& = w - \frac{l_2}{2 \cos{\theta}}\\
   y_c& = \frac{l_2}{2} - \frac{l_2}{2 \sin{\theta}}\\
@@
   & = \sqrt{ \paren{\frac{l_1}{2} - \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }\\
-  l_{BC}& = l2\\
+  l_{BC}& = l_2\\
   l_{CD}& = \sqrt{\paren{\frac{l_1}{2} + \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }
@@
 
-Given a particle with zero tangential acceleration and bounded centripetal acceleration, $a_c \le a_{c,max}$, and a cone setup consisting of 3 cones, A, B, and C, at locations $\bvec{X_A}$, $\bvec{X_B}$, and $\bvec{X_C}$ as is shown in Figure \ref{fig:3-cones}.
+Given a particle with zero tangential acceleration and bounded centripetal acceleration, $a_c \le a_{c,max}$, and a cone setup consisting of 3 cones, A, B, and C, at locations $\bvec{X_A}$, $\bvec{X_B}$, and $\bvec{X_C}$ as is shown in Figure \ref{fig:3-cones}
 
-\includefig{3_cones.eps}{3 Cone setup}{3-cones}
+\includefig{3_cones.eps}{3 cone setup}{3-cones}
 
-The optimal path [TODO]
+the optimal path around the cones is shown in Figure \ref{fig:3-cones-path}
+
+\includefig{3_cones_path.eps}{3 cone optimal path}{3-cones-path}
 
@@
 \begin{proof}
-Since speed is constant, the optimal path will be the shortest path. The optimal path is of the form, tr. Thus, the problem reduces to a trigonometric problem.
+[TODO: Finish proof]
+
+Since speed is constant, the optimal path will be the shortest path.
+By Corollary \ref{corr:optimal-path-fix-s}, the optimal path can only include line segments and circular sections.
+Thus, the problem reduces to a trigonometric problem.
+
+The turn must touch cone B, otherwise the trajectory will either not go around the cone, or be longer than necessary. Therefor, the center of the turn, c, must be a distance $r$ away from cone B.
 
@@
 
-The turn must touch the cone B, otherwise the trajectory will either not go around the cone, or be longer than necessary. Therefor, the center of the turn must be a distance $r$ away from
+Now that c is defined by $\alpha$, let us determine the total path length as a function of $\alpha$.
 
@@
 \begin{align*}
-x_c = x_B - r \cos{\alpha_c}\\
-y_c = y_B - r \sin{\alpha_c}\\
+x_c& = x_B - r \cos{\alpha_c}\\
+y_c& = y_B - r \sin{\alpha_c}\\
 l_1& = \sqrt{d_c - r}\\

### 2013-09-29 path_theorems.tex
Finish adding 3 cone proof.

@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:optimal-path-fix-s}
 Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.

### 2013-09-29 introduction.tex
Fixing trig in quadrilateral problem.

@@
+In this paper, we shall examine optimal paths for a particle.
+
 Our model problem is a particle moving in $\R^2$ with constrained acceleration.
@@
 
-In this paper, we first present a polar coordinate representation of a particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system.
+We first present a polar coordinate representation of a particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system.
 This allows us to devise some simple lemmas about the motion of the particle.
@@
 
-Finally, we are able to tackle the problem of finding an optimal path around cones.
+Finally, we tackle the problem of finding an optimal path around cones.
+
+\subsection{Motivation}
+
+The problem of finding an optimal trajectory is interesting because of its applications in physics.
+There are many instances where finding optimal paths is important.
+For instance, a race car driver wants to know the fastest way to get from one point to another so that he can win his race.
+For another example, imagine you are sending a spacecraft to a particular destination in space and would like the fastest means of getting there.
+
+The space example directly motivates our model problem.
+On a spacecraft, there is a limited amount of acceleration that is possible (provided by thrusters).
+One would potentially like to navigate to a planet while moving around obstacles.
+
+Understanding how to find optimal trajectories will provide greater insight into solving problems like these.

### 2013-09-29 path_theorems.tex

--- 2013-09-29 path_theorems.tex
@@
 \begin{theorem}
+A 2-dimensional particle, $p$, traveling along a valid path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} < 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
+\end{theorem}
+
+\begin{proof}
+Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ at some point along the path, then $\theta{T_{f,\gamma}} < \theta{t_0} < \theta{t_c}$, so [TODO]
+\end{proof}
+
+\begin{theorem}
+Given a 2-dimensional particle, $p$, it is always optimal to minimize $\frac{d\abs{\theta(t)}}{dt}$ at all $t \in [0, T_{\gamma}]$.
+\end{theorem}
+
+\begin{proof}
+[TODO]
+\end{proof}
+
+\begin{theorem}
 Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal path, $\hat{\gamma}(t)$ between two points $X_1$ and $X_2$, has a radius of curvature of $0$ or $a_{c,max}$ at every point along it.
@@
 
-\begin{corollary}
+\begin{corollary}\label{corr:optimal-path-fix-s}
 Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.

### 2013-09-29 path_theorems.tex
Add proof of minimizing theta.

@@
 \begin{proof}
-Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ at some point along the path, then $\theta{T_{f,\gamma}} < \theta{t_0} < \theta{t_c}$, so [TODO]
+Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma \ref{lemma:intermediate-theta} $\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$.
+Since all of the time derivatives in (\ref{eq:r-deriv}) - (\ref{eq:theta-deriv}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the optimal strategy should be the same, regardless of $r$.
+In other words, there can not be multiple cases for optimal strategies based on $r$.
 \end{proof}

### 2013-09-29 particle_definitions.tex
Add proof of minimizing theta.
Adding some particle definitions.

@@
 In this section, we will provide some basic definitions about particles and paths. These will lay the groundwork for thinking about optimal paths.
-
-\begin{definition}
-A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [0, T_{f, \gamma}]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
-\end{definition}
 
@@
 Traveling along a path means that the particle is at position $\lambda(t)$ at time $t$, for all $t \in [0, T_{f,\lambda}]$.
-The particle may have conditions on its position, velocity, and acceleration in $\R^n$.
+\end{definition}
+
+\begin{definition}
+A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^n$ and its derivatives at some time $t$.
+\end{definition}
+
+\begin{definition}
+A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$.
+We call a condition satisfied if the condition's output is $1$ at time $t$.
+\end{definition}
+
+\begin{definition}
+A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [0, T_{f, \gamma}]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
 \end{definition}

### 2013-09-29 conclusion.tex
Finishing up the paper.

In this paper, we have formalized many of the things that intuition would tell us. Namely, we have shown that a straight line is the fastest way to get between two points. This fact is unsurprising because of the fact that acceleration in a single direction (toward the finish point) is the least wasteful means of getting to the finish.

We developed a number of simple lemmas governing the motion of a volume-less particle with bounded acceleration. We also showed that symmetric paths tend to be better than non-symmetric paths (through our simple quadrilateral path minimization problem).

Finally, we found an optimal path for a particle to trace around three cones when the particle has constant velocity.

### 2013-09-29 cone_theorems.tex
Fixing trig in quadrilateral problem.
Reverted John's equations.
Finishing up the paper.

@@
 We would like to minimize the path length around the quadrilateral shown in Figure \ref{fig:quad}.
+Solving this problem will hopefully give us intuition for solving the problem of actual paths.
+We allow the quadrilateral's perimeter to vary based on an angle $\theta$ which has a physical representation of measuring how symmetric the system is.
 
@@
 
+Thus, we want to choose the angle which will minimize the path traveled by a particle along the perimeter of the quadrilateral.
+Intuitively, a symmetric quadrilateral should provide the fastest route, but we will formalize this intuition.
+We do this by deriving the following equations using basic trigonometry:
+
 \begin{align}
   x_c& = w - \frac{l_2}{2 \cos{\theta}}\\
-  y_c& = \frac{l_2}{2} - \frac{l_2}{2 \sin{\theta}}\\
+  y_c& = \frac{l_2}{2} - \frac{l_2}{2} \sin{\theta}\\
   l_{AB}& = \sqrt{x_c^2 + y_c^2}\\
-  & = \sqrt{ \paren{\frac{l_1}{2} - \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }\\
+  & = \sqrt{ \paren{\frac{l_1}{2} - \frac{l_2}{2} \cos\theta}^2 + \paren{w - \frac{l_2}{2} \sin\theta}^2 }\\
   l_{BC}& = l_2\\
-  l_{CD}& = \sqrt{\paren{\frac{l_1}{2} + \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }
+  l_{CD}& = \sqrt{\paren{\frac{l_1}{2} + \frac{l_2}{2} \cos\theta}^2 + \paren{w - \frac{l_2}{2} \sin\theta}^2 }
 \end{align}
 
-Since we know that $l_{BC}$ is fixed the problem reduces to
+Since we know that $l_{BC}$ is fixed, our minimization problem reduces to
 
@@
 \begin{multline}
-  \argmin_{\theta} \left[ 2\paren{\frac{l_1}{2} - \frac{l_2}{2 \sin\theta}}^2 \right.\\
-  \left. + \paren{w - \frac{l_2}{2 \cos\theta}}^2 + \paren{w + \frac{l_2}{2 \cos\theta}}^2 \right]
+  \argmin_{\theta} \left[ 2\paren{\frac{l_1}{2} - \frac{l_2}{2} \sin\theta}^2 \right.\\
+  \left. + \paren{w - \frac{l_2}{2} \cos\theta}^2 + \paren{w + \frac{l_2}{2} \cos\theta}^2 \right]
 \end{multline}
@@
 \end{eqnarray}
+
+Thus we see that the optimal angle for minimizing the path length is $\theta = \frac{\pi}{2}$.
+In other words, it is better to be have a symmetric path.
+This works well with our intuition, and so now we are ready to solve problems related to particles traveling around cones.
 

### 2013-09-29 path_theorems.tex
Finishing up the paper.

--- 2013-09-29 path_theorems.tex
@@
-The simplest problem to tackle first, is the optimal trajectory from a current position, $\bvec{X_0}$ to a final position, $\bvec{X_f}$.
+Now that we have defined our notation, we are ready to think about the problem of optimal trajectories.
+
+The simplest problem to tackle first, is the optimal trajectory from a starting position, $\bvec{X_0}$ to a final position, $\bvec{X_f}$.
 Working in a polar coordinate system centered on $X_f$, it is clear, that our goal is achieved when $r = 0$.
@@
 
+Now we will show that the fastest path between two points goes in a straight line.
+This will formalize the natural intuition that straight lines are the fastest path when there are no obstacles between the start and finish position.
+
 \begin{theorem}
-  Given a 2-dimensional particle $p$ whose initial position is $\bvec{X_1}$ and moves with bounded tangential acceleration, $a_t \le a_{t,max}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ is the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
+  Given a 2-dimensional particle $p$ whose initial position is $\bvec{X_1}$ and moves with bounded tangential acceleration, $a_t \le a_{t,max}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
 \end{theorem}

### 2013-10-07 path_theorems.tex
Writing main path theorem definitions

@@
 % -----------------------------------------------------------------------------
+
+\section{Constant Speed Conditions}
+
+\begin{definition}
+  The minimum radius of curvature of a particle under constant speed conditions is given by $r_{min} = \frac{\bar{v}^2}{\bar{a}_c}$.
+This is the radius of the circle that the particle would trace out if the particle were turning with maximum centripetal acceleration $\bar{a}_c$.
+\end{definition}
+
+\begin{conjecture}
+  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1 = \bvec{x}_2$ respectively.
+Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_1) = d(\bvec{x}_f, \bvec{x}_2) > r_{min}$.
+If $d(\bvec{x}_1, \bvec{x}_f) \leq d(\bvec{x}_2, \bvec{x}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
+\end{conjecture}
+
+\begin{theorem}
+  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{x}_0$.
+Let $p$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_0) > r_{min}$.
+The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{x}_f$ minimizes $\theta(t)$ for all $t \in [T_0, T_f(\bhat{\gamma_p})]$.
+  \label{theorem:restricted-theta}
+\end{theorem}
+
+\begin{corollary}
+  The fastest path $\bhat{\gamma_p}$, given the conditions set forth in theorem \ref{theorem:restricted-theta}, will trace out a path which contains an arc of a circle with radius $\bar{v}^2 / \bar{a}^2$ connected to a straight line tangent to the arc.
+\end{corollary}
+
+\begin{corollary}
+  Given conditions set forth in theorem \ref{theorem:restricted-theta}, we have:
+  \begin{eqnarray}
+    T_f(\bhat{\gamma_p}}) = v_0 \left( \left( \pi - \arccos \frac{r_{min}}{d - r_{min}} \right) 2 \pi r_{min}  + \sqrt{d^2 - 2 r_{min} d}  \right)
+  \end{eqnarray}
+\end{corollary}

### 2013-10-07 particle_definitions.tex

@@
 
-$\theta(t), \phi(t) \in [-\pi, \pi]$. From now on, $\abs{\theta}$ and $\abs{\phi}$ will be used, since there is a symmetry in the system about $\bhat{r}$.
+$\theta(t), \phi(t) \in [-\pi, \pi]$. From now on, $\abs{\theta(t)}$ and $\abs{\phi(t)}$ will be used, since there is a symmetry in the system about $\bhat{r}$.
 
@@
   &\begin{aligned}
-    = -\frac{dv(t)}{dt} \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
+    = -a_t \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
     &\qquad - v(t) \sin\paren{\abs{\theta(t)}} \frac{a_c(t)}{v(t)}\label{eq:r-deriv-2}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:intermediate-theta}
   For a particle, $p$, with bounded centripetal and tangential acceleration, then:

### 2013-10-07 particle_definitions.tex
Change particle definitions.

@@
 \begin{definition}
-  A n-dimensional particle, $p$, is an object with zero volume that travels along a n-dimensional path.
-Traveling along a path means that the particle is at position $\lambda(t)$ at time $t$, for all $t \in [0, T_{f,\lambda}]$.
+  A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [T_0(\gamma), T_f(\gamma)]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
 \end{definition}
@@
 \begin{definition}
-A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^n$ and its derivatives at some time $t$.
+  A particle, $p$, is an object with zero volume that, given a time $t$, can only be located at a position in space.
+A particle travels along a path, $\gamma(t)$ if the particle is at position $\gamma(t)$ at time $t$, for all $t \in [T_0 (\gamma), T_f(\gamma)]$.
+If a particle is traveling along a path $\gamma(t)$ ,then we define a position, $\bvec{X} = \gamma(t)$, a velocity, $\bvec{X} = \frac{d\gamma(t)}{dt}$, and an acceleration, $\bvec{X} = \frac{d^2\gamma(t)}{dt^2}$, of the particle, for all $t \in [T_0 (\gamma), T_f(\gamma)]$.
+
+  A particle is restricted, if there are conditions on its position, $\bvec{X}$ and the time derivatives of its position for some $t$.
+The set of all valid paths for a particle consists of all paths that the particle can travel along.
 \end{definition}
@@
 \begin{definition}
-A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$.
-We call a condition satisfied if the condition's output is $1$ at time $t$.
+  A planar path is a 2-dimensional path.
 \end{definition}
@@
 \begin{definition}
-A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [0, T_{f, \gamma}]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
-\end{definition}
-
-\begin{definition}
-  A valid path $\gamma(t)$ for a particle $p$ is a path along which $p$ can travel, such that all its conditions are satisfied at every point along the path.
-\end{definition}
-
-\begin{definition}
-  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$, where $\gamma(0) = \bvec{X_1}$ and $\gamma(T_{f, \gamma}) = \bvec{X_2}$.
+  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$, where $\gamma(T_0(\gamma)) = \bvec{X_1}$ and $\gamma(T_f(\gamma)) = \bvec{X_2}$.
 \end{definition}
@@
   \]
+\end{definition}
+
+\begin{definition}
+  Constant speed conditions is a set of restrictions on a particle's motion, $\bvec{X}$ in $R^2$, , and its centripetal 
 \end{definition}

### 2013-10-07 path_theorems.tex
Making the straight line theorem bulletproof.

@@
 \begin{theorem}
-A 2-dimensional particle, $p$, traveling along a valid path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} < 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
+A 2-dimensional particle, $p$, traveling along a fastest path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} \leq 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
 \end{theorem}
@@
 
-\begin{theorem}
-Given a 2-dimensional particle, $p$, it is always optimal to minimize $\frac{d\abs{\theta(t)}}{dt}$ at all $t \in [0, T_{\gamma}]$.
-\end{theorem}
-
-\begin{proof}
-[TODO]
-\end{proof}
-
-\begin{theorem}
-Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal path, $\hat{\gamma}(t)$ between two points $X_1$ and $X_2$, has a radius of curvature of $0$ or $a_{c,max}$ at every point along it.
-\end{theorem}
-
-\begin{proof}
-[TODO]
-\end{proof}
-
-\begin{corollary}\label{corr:optimal-path-fix-s}
-Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.
-\end{corollary}
-
-\begin{proof}
-[TODO]
-\end{proof}
-
 % -----------------------------------------------------------------------------
 
-Now we will show that the fastest path between two points goes in a straight line.
+Now we will show that the fastest path between two points goes in a straight line if there is no initial speed.
 This will formalize the natural intuition that straight lines are the fastest path when there are no obstacles between the start and finish position.
@@
 \begin{theorem}
-  Given a 2-dimensional particle $p$ whose initial position is $\bvec{X_1}$ and moves with bounded tangential acceleration, $a_t \le a_{t,max}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
+  Given a particle $p \in \mathrm{R}^2$ whose initial position is $\bvec{X_1}$ and moves with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
 \end{theorem}
@@
 Without loss of generality, we can define a cartesian coordinate system, where the origin is at $\bvec{X_1}$ and the positive x-axis passes through $\bvec{X_2}$.
+Let us say that the two points in our cartesian coordinate system become $(0,0)$ and $(x_2, 0)$ respectively.
 
@@
 \begin{align}
-  d(t) &= \int_0^t v_x(t_2) dt_2 \\
+  l_x(t) &= \int_0^t v_x(t_2) dt_2 \\
   &= \int_0^t \int_0^t a_x(t_1) dt_1 dt_2
@@
 
-Recall that the tangential acceleration of the point mass $p$ is bounded by $a_{t,max}$. This means that $a_t(t) \leq \bar{a}$ for all $t$. Therefore, we see:
+Recall that the tangential acceleration of the point mass $p$ is bounded by $\bar{a}_{t}$. This means that $a_t(t) \leq \bar{a}_t$ for all $t$. Therefore, we see:
 \begin{align}
-  d(t) &\leq \int_0^t \int_0^t \bar{a} dt_1 dt_2\\
-  &= \frac{\bar{a} t^2}{2}
+  d(t) &\leq \int_0^t \int_0^t \bar{a}_t dt_1 dt_2\\
+  &= \frac{\bar{a}_t t^2}{2}
 \end{align}
 
-Thus, in order to travel a distance of $d(T_f) = x_2$, it needs to be the case that $T_f \geq \sqrt{\frac{2 x_2}{\bar{a}}}$.
-Moreover, equality holds if and only if $a_t(t) = \bar{a}$ for all $t \in [0, T_f(\gamma)]$.
+Thus, in order to travel a distance of $l_x(T_f(\hat{\gamma})) = d' = d(\bvec{X_2}, \bvec{X_1})$, it needs to be the case that $T_f(\hat{\gamma}) \geq \sqrt{\frac{2 d'}{\bar{a}_t}}$.
+It is possible to travel from $\vec{X_2}$ to $\vec{X_1}$ in time $T_{min} = \sqrt{\frac{2 d'}{\bar{a}_t}}$ if and only if $a_t(t) = \bar{a}_t$ and $\theta(t) = 0$ for all $t \in [T_0(\gamma), T_{min}]$.
+In other words, the particle must be accelerating at the maximum possible tangential acceleration of $\bar{a}_t$ and it must be accelerating in the straight line direction to $\vec{X_2}$ at all times.
 
-If the point mass travels for time $t < \sqrt{\frac{2 x_2}{\bar{a}}}$, then it is impossible for the point mass to reach $(x_2, 0)$ when starting at $(0,0)$.
-This is because $p$ cannot reach $(x_2, 0)$ in the $x$ direction when $t < \sqrt{\frac{2 x_2}{\bar{a}}}$ and any acceleration in the $y$ direction would not enable this either.
+If the particle travels for time $t < T_{min}$, then it is impossible for the point mass to reach $\vec{X_2}$ when starting at $\vec{X_1}$.
+This is because $p$ cannot reach $\vec{X}_2$ in the $x$ direction when $t < \sqrt{\frac{2 d'}{\bar{a}}}$ because it is impossible for $p$ to reach any point whose $x$-coordinate is $x_2$, so it is obviously impossible to reach $(x_2, 0) = \vec{X_2}$.
+
+Moreover, if there exists some time $t < T_{min}$ when $\theta(t) \neq 0$, then it is also impossible for the point mass to reach $\vec{X_2}$.
+Suppose that there are two particles $p_1$ and $p_2$ both accelerating at $a_t(t) = \bar{a}_t$.
+Imagine $p_1$ satisfies $\theta_{p_1}(t) = 0$ for all $t$ and that $p_2$ satisfies $\theta_{p_2}(t) = 0$ except for times in some interval $[t_0, t_1]$, the particle $p_2$ sets a constant non-zero angle $\zeta_{p_2}(t) \neq 0$ with the $x$-axis for $t \in [t_0, t_1]$.
+Denote $d_{p}$ as the distance that is left to be travelled by particle $p$ between times $t_1$ and $T_{min}$.
+We can find $d_{p_2}$ in terms of $d_{p_1}$ by using trigonometry:
+
+\begin{eqnarray}
+d_{p_2}^2 = d_{p_1}^2 + \left(\frac{\bar{a}_t (t_1 - t_0)^2}{2} \sin \zeta_{p_2} \right)^2
+\end{eqnarray}
+
+Since $d_{p_2} \geq 0$ by being a distance, $\sin \zeta_{p_2} \neq 0$ by setting $\zeta_{p_2} > 0$, and $t_1 - t_0 > 0$, we know that $d_{p_2} > d_{p_1}$.
+This means that at time $T_{min}$ when $p_1$ has reached its destination at $\Vec{X_2}$, particle $p_2$ still has $d_{p_2} - d_{p_1}$ distance left to travel.
+This means that it is impossible for $\theta(t) > 0$ on the fastest path.
 
@@
 
-Now, we have seen that the fastest path in the transformed coordinates travels exactly on the $x$ axis so that $y = 0$ anywhere along the fastest path.
-Notice, however, that the $x$ axis in the transformed coordinates is given exactly by the following line:
-\begin{equation}
-  y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
-\end{equation}
-
-Thus, we see that the fastest path in the original coordinates follows the above equation, which is what we wanted to show.
+Thus, we see that the fastest path is the straight line between $\vec{X_1}$ and $\vec{X_2}$.
 \end{proof}

### 2013-10-07 path_theorems.tex
Changed r_min to R_min

@@
 
-\begin{definition}
-  The minimum radius of curvature of a particle under constant speed conditions is given by $r_{min} = \frac{\bar{v}^2}{\bar{a}_c}$.
-This is the radius of the circle that the particle would trace out if the particle were turning with maximum centripetal acceleration $\bar{a}_c$.
-\end{definition}
-
 \begin{conjecture}
   Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1 = \bvec{x}_2$ respectively.
-Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_1) = d(\bvec{x}_f, \bvec{x}_2) > r_{min}$.
+Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_1) = d(\bvec{x}_f, \bvec{x}_2) > R_{min}$.
 If $d(\bvec{x}_1, \bvec{x}_f) \leq d(\bvec{x}_2, \bvec{x}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
@@
   Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{x}_0$.
-Let $p$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_0) > r_{min}$.
+Let $p$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_0) > R_{min}$.
 The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{x}_f$ minimizes $\theta(t)$ for all $t \in [T_0, T_f(\bhat{\gamma_p})]$.
@@
   \begin{eqnarray}
-    T_f(\bhat{\gamma_p}}) = v_0 \left( \left( \pi - \arccos \frac{r_{min}}{d - r_{min}} \right) 2 \pi r_{min}  + \sqrt{d^2 - 2 r_{min} d}  \right)
+    T_f(\bhat{\gamma_p}}) = v_0 \left( \left( \pi - \arccos \frac{R_{min}}{d - R_{min}} \right) 2 \pi R_{min}  + \sqrt{d^2 - 2 R_{min} d}  \right)
   \end{eqnarray}

### 2013-10-07 particle_definitions.tex
Finish modifying particle and path defs.

@@
 \begin{definition}
-  A particle, $p$, is an object with zero volume that, given a time $t$, can only be located at a position in space.
-A particle travels along a path, $\gamma(t)$ if the particle is at position $\gamma(t)$ at time $t$, for all $t \in [T_0 (\gamma), T_f(\gamma)]$.
-If a particle is traveling along a path $\gamma(t)$ ,then we define a position, $\bvec{X} = \gamma(t)$, a velocity, $\bvec{X} = \frac{d\gamma(t)}{dt}$, and an acceleration, $\bvec{X} = \frac{d^2\gamma(t)}{dt^2}$, of the particle, for all $t \in [T_0 (\gamma), T_f(\gamma)]$.
-
-  A particle is restricted, if there are conditions on its position, $\bvec{X}$ and the time derivatives of its position for some $t$.
-The set of all valid paths for a particle consists of all paths that the particle can travel along.
-\end{definition}
-
-\begin{definition}
-  A planar path is a 2-dimensional path.
+  A planar path is a path in $\R^2$.
 \end{definition}
@@
 \begin{definition}
-  For a given particle, $p$, a fastest path, $\hat{\gamma}(t)$, between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_{f,\hat{\gamma}} \leq T_{f,\gamma}$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
+  A particle, $p$, is an object in space with zero volume.
+A particle travels along a path, $\gamma(t)$ if the particle is at position $\gamma(t)$ at time $t$, for all $t \in [T_0(\gamma), T_f(\gamma)]$.
+If a particle is traveling along a path, $\gamma(t)$, then we define a position, $\bvec{X}(t) \coloneqq \gamma(t)$, a velocity, $\bvec{v}(t) \coloneqq \frac{d\gamma(t)}{dt}$, and an acceleration, $\bvec{a}(t) \coloneqq \frac{d^2\gamma(t)}{dt^2}$, for the particle, for all $t \in [T_0(\gamma), T_f(\gamma)]$.
+
+  A particle is restricted if there are conditions on its position and the time derivatives of its position. Given a particle, a valid path is a path that the particle can travel along.
 \end{definition}
@@
 \begin{definition}
-  A particle's velocity is defined as
-
-  \[\bvec{v} \coloneqq \frac{d\bvec{X}}{dt}\]
-
-  Furthermore, a particle's speed is $v$, and its direction of motion is $\bhat{v}$
-
+  Given a particle, a fastest path, $\hat{\gamma}(t)$, between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
 \end{definition}
@@
 \begin{definition}
-  A particle's acceleration is defined as
-
-  \[\bvec{a} \coloneqq \frac{d\bvec{v}}{dt}\]
+  A particle's speed is $v(t)$, and its direction of motion is $\bhat{v}$.
 \end{definition}
@@
 \begin{definition}
-  The tangential acceleration, $\bvec{a_t}$, of a particle, $p$, is the component of the acceleration of $p$ in its direction of motion, $\bhat{v}$.
+  The tangential acceleration, $a_t$, of a particle, is the component of the acceleration of the particle in its direction of motion.
 
-  \[
-  a_t = \frac{dv}{dt}
-  \]
-\end{definition}
-
-\begin{definition}
-  Constant speed conditions is a set of restrictions on a particle's motion, $\bvec{X}$ in $R^2$, , and its centripetal 
+  \[a_t \coloneqq \frac{dv}{dt}\]
 \end{definition}
@@
 
-Unless otherwise specified, the motion of 2-dimensional particles in this paper will be described in polar coordinates, along with an extra parameter $\theta$ as is shown in Figure \ref{fig:polar-param}.
+Unless otherwise specified, the motion of particle moving along planar paths  will be described in polar coordinates, along with an extra parameter $\theta$, as is shown in Figure \ref{fig:polar-param}.
 
@@
 
-\begin{lemma}\label{lemma:intermediate-theta}
-  For a particle, $p$, with bounded centripetal and tangential acceleration, then:
-
-  1. The function $\abs{\theta(t)}$ is continuous.
-
-  2. Given $t_1, t_2 \in \R^2$, s.t. $t_1 < t_2$, $\theta(t_1) > a$ and $\theta(t_2) < a$, then $\theta(t_c) = a$ for some $t_c \in [t_1, t_2]$.
-\end{lemma}
-
-\begin{proof}
-First off, it should be noted that a solution to (\ref{eq:theta-deriv}) exists because the right hand side is Lipschitz continuous.
-The proof of 1.\ follows directly from the fact that the derivative of $\abs{\theta(t)}$ exists and is bounded.
-2.\ is just a restatement of the intermediate value theorem.
-\end{proof}
-
 \begin{lemma}\label{lemma:polar-assymptote}
-  For a particle, $p$, with nonzero speed, and zero centripetal acceleration for $t \ge t_0$, then
+  Given a particle with the following restrictions: $a = 0$, $v(t) = \bar{v}$, for all $t \ge T_0$then the following equations hold
   \[
     \begin{cases}
-      \abs{\theta(t)} \to \pi \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
-      \abs{\theta(t)} = 0 \quad \text{for all} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
+      \abs{\theta(t)} \to \pi \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(T_0) > 0\\
+      \abs{\theta(t)} = 0 \quad \text{for all} \quad t \ge T_0 \qquad &\text{if} \;\; \theta(T_0) = 0
     \end{cases}
@@
     \begin{cases}
-      r(t) \to \infty \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(t_0) > 0\\
-      r(t) \to 0 \quad \text{as} \quad t \ge t_0 \qquad &\text{if} \;\; \theta(t_0) = 0
+      r(t) \to \infty \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(T_0) > 0\\
+      r(t) \to 0 \quad \text{as} \quad t \ge T_0 \qquad &\text{if} \;\; \theta(T_0) = 0
     \end{cases}
@@
 
-For the first case, $\frac{d\abs{\theta(t)}}{dt} > 0$, except when $\abs{\theta(t)} = 0, \pi$, which means that $\theta(t)$ is monotonically increasing.
-Since $\phi(t)$ is bounded above py $\pi$, $\phi(t) \to \pi \;\; \text{as} \;\; \infty$.
+The first part of the lemma is proven by referring to (\ref{eq:theta-deriv}), and noting that $\frac{d\abs{\theta(t)}}{dt} = 0$ when $\abs{\theta(t)} = 0, \pi$, and $\frac{d\abs{\theta(t)}}{dt} > 0$ otherwise.
+If $\theta(T_0) \ne 0$, then $\theta(t)$ is bounded above by $\pi$ and strictly increasing, because its derivative is strictly positive, so $\abs{\theta(t)} \to \pi \quad \text{as} \quad t \to \infty$.
+If $\theta(T_0) = 0$, then $\abs{\theta(t)} = 0 \quad \text{for all} \quad t \ge T_0$.
 
-The second case is the easiest to check. If we plug $\theta(t_0) = 0$ into \ref{eq:theta-deriv}, we get
+For the first case of the second part of the lemma,
 

### 2013-10-07 path_theorems.tex
Finish modifying particle and path defs.

@@
 Now that we have defined our notation, we are ready to think about the problem of optimal trajectories.
+
+\begin{definition}
+  A fixed speed particle is a particle with the following conditions: $\bvec{X} \in \R^2$, $a_t = 0$, $v(t) = \bar{v}$.
+\end{definition}
+
+\begin{definition}
+  A particle with bounded centripetal acceleration is a particle with the following condition: $\norm{a_c} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
+\end{definition}
 

### 2013-10-07 path_theorems.tex
Compiled paper (no more conflicts).
Changing path theorems.

@@
 \begin{theorem}
-  Given a particle $p \in \mathrm{R}^2$ whose initial position is $\bvec{X_1}$ and moves with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
+  \label{theorem:line-proof}
+  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$, no initial speed, and moves with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
 \end{theorem}
@@
 \begin{corollary}
-  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ is unique.
+  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in \ref{theorem:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
 \end{corollary}
-\proof We have already shown that any fastest path between $(x_1, y_1)$ and $(x_2, y_2)$ follows the straight line given by $y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1$.
-Moreover, we showed that when travelling along the fastest path, the particle must have acceleration along the straight line of $\bar{a}$.
-Since we have starting position $(x_1, y_1)$ and initial speed of $0$, the acceleration of the particle $a(t)$ uniquely defines a path for the particle.
+\proof We have already shown that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them.
+Moreover, we showed that when travelling along the fastest path, the particle must have tangential acceleration of $\bar{a}_t$.
+Since we have starting position $\vec{X_1}$ and initial speed of $0$, the acceleration of the particle uniquely defines a path for the particle.
 
-There is only a single function $a(t) = \bar{a}$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
+There is only a single function $a(t) = \bar{a}_t$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
 \qed
@@
 \begin{conjecture}
-  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1 = \bvec{x}_2$ respectively.
+  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1, \bvec{x}_2$ respectively.
 Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_1) = d(\bvec{x}_f, \bvec{x}_2) > R_{min}$.
@@
   \begin{eqnarray}
-    T_f(\bhat{\gamma_p}}) = v_0 \left( \left( \pi - \arccos \frac{R_{min}}{d - R_{min}} \right) 2 \pi R_{min}  + \sqrt{d^2 - 2 R_{min} d}  \right)
+    T_f(\bhat{\gamma_p}) = v_0 \left( \left( \pi - \arccos \frac{R_{min}}{d - R_{min}} \right) 2 \pi R_{min}  + \sqrt{d^2 - 2 R_{min} d}  \right)
   \end{eqnarray}

### 2013-10-07 path_theorems.tex
Small changes to corollary of unique fastest path.

@@
 \begin{corollary}
-  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in \ref{theorem:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
+  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in Theorem \ref{theorem:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
 \end{corollary}
-\proof We have already shown that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them.
+\proof We have already shown in Theorem \ref{theorem:line-proof} that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them.
 Moreover, we showed that when travelling along the fastest path, the particle must have tangential acceleration of $\bar{a}_t$.
@@
 
-There is only a single function $a(t) = \bar{a}_t$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
+There is only a single function of the acceleration $a(t) = \bar{a}_t$ which can be satisfied when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
 \qed

### 2013-10-07 path_theorems.tex
Writing filler for path theorems.

@@
 Now that we have defined our notation, we are ready to think about the problem of optimal trajectories.
-
-\begin{definition}
-  A fixed speed particle is a particle with the following conditions: $\bvec{X} \in \R^2$, $a_t = 0$, $v(t) = \bar{v}$.
-\end{definition}
-
-\begin{definition}
-  A particle with bounded centripetal acceleration is a particle with the following condition: $\norm{a_c} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
-\end{definition}
 
@@
 
+In the previous section, we made statements about fastest paths between two points when the initial velocity was set to zero.
+We saw that our physical intuition was confirmed and that a straight line was the fastest way to travel between two points.
+
+This is a simple case of the more general problem.
+We shall now examine optimal trajectories when the initial velocity is non-zero but when the centripetal acceleration is bounded.
+These conditions are much closer to physical reality, because it is often the case that you want to find a fastest path after you have already started moving.
+Moreover, Theorem \ref{theorem:line-proof} assumed that centripetal acceleration was unbounded so that the particle could turn on a dime in any direction.
+This is not realistic because most physical objects have momentum when they are travelling at high speeds, making it much more difficult to turn.
+
+Assuming bounded acceleration makes the problem more interesting, and also much more difficult if we allow for tangential acceleration.
+In this section, we will eliminate tangential acceleration so that the particle will travel at constant speed.
+
+To begin proving things about the fastest path, we first formalize the conditions we will be using:
+
+\begin{definition}
+  A fixed speed particle is a particle such that: $\bvec{X} \in \R^2$, $a_t = 0$, $v(t) = \bar{v}$.
+\end{definition}
+
+\begin{definition}
+  A particle with bounded centripetal acceleration is a particle with the following condition: $\norm{a_c} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
+\end{definition}
+
+Now we shall use the following shorthand throughout this section to talk about the conditions on a particle:
+
+\begin{definition}
+  A particle with constant speed conditions is a fixed speed particle with bounded centripetal acceleration.
+\end{definition}
+
+To prove things about the fastest path of a particle under constant speed conditions, we shall make Conjecture \ref{conjecture:fastest-paths} about how fastest paths behave.
+
 \begin{conjecture}
+  \label{conjecture:fastest-paths}
   Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1, \bvec{x}_2$ respectively.
@@
 \end{conjecture}
+
+This conjecture comes from physical intuition.
+If two particles $p_1$ and $p_2$ are attempting to arrive at a particular ending point $\bvec{X}_f$, and $p_2$ is farther away than $p_1$ and also has an initial angle $\theta$ to $\bvec{X}_f$ that is larger than $p_1$'s initial angle, then $p_2$ must take a longer time to turn towards $\bvec{X}_f$ and must travel a longer distance than $p_1$.
+Because of this, it seems to be the case that $p_1$'s fastest path is faster than $p_2$'s fastest path.
+
+If this conjecture is true, then we can provide the strategy for obtaining the fastest path between two points $\bvec{X}_0$ and $\bvec{X}_f$.
 

### 2013-10-08 path_theorems.tex
Changing wording and adding filler.

@@
 The simplest problem to tackle first, is the optimal trajectory from a starting position, $\bvec{X_0}$ to a final position, $\bvec{X_f}$.
-Working in a polar coordinate system centered on $X_f$, it is clear, that our goal is achieved when $r = 0$.
-Furthermore, $\theta(t)$ must be $0$ before reaching $X_f$, otherwise, it will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-deriv}).
+Working in a polar coordinate system centered on $\bvec{X_f}$, it is clear, that our goal is achieved when $r = 0$.
+Furthermore, $\theta(t)$ must be $0$ before reaching $\bvec{X_f}$, otherwise, it will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-deriv}).
 
 \begin{lemma}
-If $a_t=0$ and $a_c \le a_{c,max}$, then the minimum radius of curvature of a particle's trajectory is given by
+  If $a_t=0$ and $a_c \le \bar{a}_{c}$, then the minimum radius of curvature of a particle's trajectory is given by
 \begin{equation}
-R_{min} = \frac{v^2}{a_{c,max}}
+  R_{min} = \frac{v^2}{\bar{a}_{c}}
 \end{equation}
@@
 \begin{proof}
-This comes directly from the definition of radius of curvature
+This comes directly from the definition of radius of curvature for a particle without any tangential acceleration:
 
@@
 \[
-a_c \le a_{c,max} \to \frac{1}{a_c} \ge \frac{1}{a_{c,max}}
+  a_c \le \bar{a}_{c} \to \frac{1}{\bar{a}_c} \ge \frac{1}{\bar{a}_{c}}
 \]
 \end{proof}
+
+We cann also investigate how the particle moves along a fastest path.
+In particle, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
 

### 2013-10-08 path_theorems.tex
Remove unneeded sections of appendix.

@@
 
-We cann also investigate how the particle moves along a fastest path.
-In particle, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
+We can also investigate how the particle moves along a fastest path.
+In particular, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
 
@@
 Assuming bounded acceleration makes the problem more interesting, and also much more difficult if we allow for tangential acceleration.
-In this section, we will eliminate tangential acceleration so that the particle will travel at constant speed.
+In this section, we will eliminate tangential acceleration so that the particle will travel at constant speed with bounded acceleration.
 
@@
   \label{conjecture:fastest-paths}
-  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1, \bvec{x}_2$ respectively.
-Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_1) = d(\bvec{x}_f, \bvec{x}_2) > R_{min}$.
-If $d(\bvec{x}_1, \bvec{x}_f) \leq d(\bvec{x}_2, \bvec{x}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
+  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{X}_1, \bvec{X}_2$ respectively.
+Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_1) = d(\bvec{X}_f, \bvec{X}_2) > R_{min}$.
+If $d(\bvec{X}_1, \bvec{X}_f) \leq d(\bvec{X}_2, \bvec{X}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
 \end{conjecture}
@@
 \begin{theorem}
-  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{x}_0$.
-Let $p$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_0) > R_{min}$.
-The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{x}_f$ minimizes $\theta(t)$ for all $t \in [T_0, T_f(\bhat{\gamma_p})]$.
+  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$.
+Let $p$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_0) > R_{min}$.
+The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
   \label{theorem:restricted-theta}
 \end{theorem}
+\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta(t)|$ for all times $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
+We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.
+
+\qed
 

### 2013-10-08 path_theorems.tex
Adding more filler words.

@@
 
+We can also prove that this fastest path is unique without very much extra work.
+
 \begin{corollary}
@@
 \end{theorem}
-\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta(t)|$ for all times $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
+\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta(t)|$ for all times $t \in [T_0(\gamma_{p_1}), T_f(\gamma_{p_1})]$.
 We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.

### 2013-10-08 path_theorems.tex
Completing main theorem.

@@
 \end{theorem}
-\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta(t)|$ for all times $t \in [T_0(\gamma_{p_1}), T_f(\gamma_{p_1})]$.
+\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta_{p_1}(t)|$ for all times $t \in [T_0(\gamma_{p_1}), T_f(\gamma_{p_1})]$.
 We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.
 
+To do this, we will invoke a lemma which is closely related to Theorem \ref{theorem:line-proof}:
+
+\begin{lemma}
+  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$ with constant speed conditions.
+If the end position is $\bvec{X}_f$ and $\theta(T_0(\gamma)) = 0$, then the fastest path $\bhat{\gamma_p}$ for particle $p$ follows the straight line between $\bvec{X}_0$ and $\bvec{X}_f$.
+\end{lemma}
+
+The lemma says that if a particle starts with initial velocity pointing directly towards $\bvec{X}_f$, then it is optimal to continue moving towards $\bvec{X}_f$ in a straight line.
+The proof of this lemma is very similar to the proof for Theorem \ref{theorem:line-proof}, so we will omit it.
+
+This lemma does allow us to determine something crucial about the fastest path of $\bhat{\gamma_{p}}$.
+In particular, if the particle $p$ ever obtains $\theta_p(t_s) = 0$ at some time $t_s$, then it will be the case that $\theta_p(t') = 0$ for all $t'$ such that $t_s < t' < T_f(\bhat{\gamma_p})$.
+In words, if $\theta_p(t_s) = 0$ for any $t_s < T_f(\bhat{\gamma_p})$, then the particle will follow a straight line to $\bvec{X}_f$ after time $t_s$.
+Moreover that it must be the case that the particle reaches $\theta_p = 0$ at some time (or else the particle would never reach $\bvec{X}_f$).
+Thus, there must exist time $t_s$ where $\theta_p(t') = 0$ for all $t' > t_s$ in the fastest path $\bhat{\gamma_p}$.
+Note that $\gamma_{p_1}$ will contain this point.
+This is a necessary, but not sufficient condition for being a fastest path.
+
+To show that $\gamma_{p_1}$ truly is a fastest path, we must examine what happens before $t_s$, i.e.
+for all times $t'$ such that $T_0(\gamma_{p_1}) < t' < t_s$.
+This becomes the important period because we know that after $t_s$ (which necessarily occurs in a fastest path), the motion of the particle is in a straight line.
+
+For particle $p_1$, we know that $|a_c(t')| = \bar{a}_c$ for all $t' < t_s$ because $p_1$ is minimizing $|\theta_{p_1}(t)|$.
+Thus, we see that $p_1$ traces out an arc of a circle with radius $R_{min} = \frac{\bar{v}}{\bar{a}_c}$ because we know that $|a_c(t')| = \bar{a}_c$ for all $t' < t_s$.
+
+Now let us introduce a particle $p_2$ with the same conditions as $p_1$.
+However, at some time $t_b < t_s$, $p_2$ will choose $a^{p_2}_c$ such that $|a^{p_2}_c| \neq \bar{a}_c$ so that $p_2$'s centripetal acceleration diverges from $p_1$'s centripetal acceleration.
+We shall show that $p_2$'s fastest path after this divergence is worse than $p_1$'s fastest path, which will allow us to conclude that deviations from $p_1$ are suboptimal.
+
+We can examine the difference in radius $r$ and angle $theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof.
+Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section.
+We can use \ref{eq:r-deriv-2} to obtain the following:
+
+\begin{eqnarray}
+  \frac{d^2 r_{p_1}(t)}{d t^2} - \frac{d^2 r_{p_2}(t)}{d t^2} = \\
+  - sin(| \theta(t_b) |) \left( \bar{a}_c - a^{p_2}_c(t_b) \right) < 0
+\end{eqnarray}
+
+The inequality was obtained because $\bar{a}_c - a^{p_2}_c(t_b) > 0$.
+This directly implies that $r_1(t_b + \epsilon) < r_2(t_b + \epsilon)$ for some small $\epsilon > 0$.
+Therefore the distance left to travel for $p_1$ is less than the distance left for $p_2$ at $t_b + \epsilon$ time, i.e.
+$d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$.
+
+We can also use \ref{eq:theta-deriv} to obtain the following for the difference in angles:
+\begin{eqnarray}
+  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_1} (t_b) |}{dt} = \\
+  - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
+\end{eqnarray}
+
+Again, we used the fact that $\bar{a}_c - a^{p_2}_c(t_b) > 0$ to show the inequality. This implies that $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
+
+Now, we have satisfied the conditions of Conjecture \ref{conjecture:fastest-paths} since $d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$ and $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
+This implies that $T_f(\gamma_{p_1}) < T_f(\gamma_{p_2})$.
+Thus, the fastest path before $t_s$ must be to travel along $\gamma_{p_1}$.
+However, we know that the fastest path after $t_s$ is to travel along the straight line (which $\gamma_{p_1}$ does).
+Therefore, we see that $\gamma_{p_1} = \bhat{\gamma}_p$ is the fastest path.
 \qed

### 2013-10-08 particle_definitions.tex

@@
     = -a_t \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
-    &\qquad - v(t) \sin\paren{\abs{\theta(t)}} \frac{a_c(t)}{v(t)}\label{eq:r-deriv-2}
+    &\qquad - \sin\paren{\abs{\theta(t)}} a_c(t) \label{eq:r-deriv-2}
   \end{aligned}

### 2013-10-08 particle_definitions.tex
Cutting out unneeded parts of the paper.

@@
 \end{align}
-
-\begin{lemma}\label{lemma:polar-assymptote}
-  Given a particle with the following restrictions: $a = 0$, $v(t) = \bar{v}$, for all $t \ge T_0$then the following equations hold
-  \[
-    \begin{cases}
-      \abs{\theta(t)} \to \pi \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(T_0) > 0\\
-      \abs{\theta(t)} = 0 \quad \text{for all} \quad t \ge T_0 \qquad &\text{if} \;\; \theta(T_0) = 0
-    \end{cases}
-  \]
-
-    Furthermore,
-
-  \[
-    \begin{cases}
-      r(t) \to \infty \quad \text{as} \quad t \to \infty \qquad &\text{if} \;\; \theta(T_0) > 0\\
-      r(t) \to 0 \quad \text{as} \quad t \ge T_0 \qquad &\text{if} \;\; \theta(T_0) = 0
-    \end{cases}
-  \]
-\end{lemma}
-
-\begin{proof}
-
-The first part of the lemma is proven by referring to (\ref{eq:theta-deriv}), and noting that $\frac{d\abs{\theta(t)}}{dt} = 0$ when $\abs{\theta(t)} = 0, \pi$, and $\frac{d\abs{\theta(t)}}{dt} > 0$ otherwise.
-If $\theta(T_0) \ne 0$, then $\theta(t)$ is bounded above by $\pi$ and strictly increasing, because its derivative is strictly positive, so $\abs{\theta(t)} \to \pi \quad \text{as} \quad t \to \infty$.
-If $\theta(T_0) = 0$, then $\abs{\theta(t)} = 0 \quad \text{for all} \quad t \ge T_0$.
-
-For the first case of the second part of the lemma,
-
-\begin{align*}
-\frac{d\abs{\theta(t)}}{dt} = 0 \qquad \text{for} \;\; t \ge t_0\\
-\intertext{So}
-\abs{\theta(t)} = 0 \qquad \text{for} \;\; t \ge t_0
-\end{align*}
-
-[TODO]
-
-\end{proof}

### 2013-10-08 path_theorems.tex
Cutting out unneeded parts of the paper.

@@
 
-We can examine the difference in radius $r$ and angle $theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof.
+We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof.
 Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section.
@@
 \qed
-
-\begin{corollary}
-  The fastest path $\bhat{\gamma_p}$, given the conditions set forth in theorem \ref{theorem:restricted-theta}, will trace out a path which contains an arc of a circle with radius $\bar{v}^2 / \bar{a}^2$ connected to a straight line tangent to the arc.
-\end{corollary}
-
-\begin{corollary}
-  Given conditions set forth in theorem \ref{theorem:restricted-theta}, we have:
-  \begin{eqnarray}
-    T_f(\bhat{\gamma_p}) = v_0 \left( \left( \pi - \arccos \frac{R_{min}}{d - R_{min}} \right) 2 \pi R_{min}  + \sqrt{d^2 - 2 R_{min} d}  \right)
-  \end{eqnarray}
-\end{corollary}

### 2013-10-08 path_theorems.tex
Small typo corrections.

@@
 Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section.
-We can use \ref{eq:r-deriv-2} to obtain the following:
+We can use equation \ref{eq:r-deriv-2} to obtain the following:
 
 \begin{eqnarray}
-  \frac{d^2 r_{p_1}(t)}{d t^2} - \frac{d^2 r_{p_2}(t)}{d t^2} = \\
-  - sin(| \theta(t_b) |) \left( \bar{a}_c - a^{p_2}_c(t_b) \right) < 0
+  \frac{d^2 r_{p_1}(t)}{d t^2} - \frac{d^2 r_{p_2}(t)}{d t^2} = - \sin(| \theta(t_b) |) \left( \bar{a}_c - a^{p_2}_c(t_b) \right) < 0
 \end{eqnarray}
@@
 
-We can also use \ref{eq:theta-deriv} to obtain the following for the difference in angles:
+We can also use equation \ref{eq:theta-deriv} to obtain the following for the difference in angles:
 \begin{eqnarray}
-  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_1} (t_b) |}{dt} = \\
-  - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
+  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_1} (t_b) |}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
 \end{eqnarray}

### 2013-10-09 conclusion.tex
Fixing typos

@@
 We developed a number of simple lemmas governing the motion of a volume-less particle with bounded acceleration.
-We also showed that symmetric paths tend to be better than non-symmetric paths (through our simple quadrilateral path minimization problem).
-
-Finally, we found an optimal path for a particle to trace around three cones when the particle has constant velocity.
+We also showed that when a particle has bounded accleration, the optimal strategy for getting to another point as fast as possible is to minimize the angle that the particle's velocity vector makes with the ending point.

### 2013-10-09 particle_definitions.tex
Fixing typos

@@
 \begin{definition}
-  A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [T_0(\gamma), T_f(\gamma)]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
+  A n-dimensional path $\gamma(t): [T_0(\gamma), T_f(\gamma)] \to \mathrm{R}^n$ is a function which maps a time $t \in [T_0(\gamma), T_f(\gamma)]$ to a position $\bvec{X} \in \mathrm{R}^n$.
+The path $\gamma$ begins at time $T_0(\gamma)$ and ends at time $T_f(\gamma)$.
 \end{definition}
@@
 \begin{definition}
-  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$, where $\gamma(T_0(\gamma)) = \bvec{X_1}$ and $\gamma(T_f(\gamma)) = \bvec{X_2}$.
+  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path $\gamma(t)$ where $\gamma(T_0(\gamma)) = \bvec{X_1}$ and $\gamma(T_f(\gamma)) = \bvec{X_2}$.
 \end{definition}

### 2013-10-09 path_theorems.tex
Fixing typos

@@
 
-The simplest problem to tackle first, is the optimal trajectory from a starting position, $\bvec{X_0}$ to a final position, $\bvec{X_f}$.
+The simplest problem to tackle first is to find the optimal trajectory from a starting position, $\bvec{X_0}$, to a final position, $\bvec{X_f}$.
 Working in a polar coordinate system centered on $\bvec{X_f}$, it is clear, that our goal is achieved when $r = 0$.
@@
   \label{theorem:line-proof}
-  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$, no initial speed, and moves with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
+  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$ and no initial speed moving with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
 \end{theorem}
@@
   l_x(t) &= \int_0^t v_x(t_2) dt_2 \\
-  &= \int_0^t \int_0^t a_x(t_1) dt_1 dt_2
+         &= \int_0^t \int_0^{t_1} a_x(t_1) dt_1 dt_2
 \end{align}
 
-Recall that the tangential acceleration of the point mass $p$ is bounded by $\bar{a}_{t}$. This means that $a_t(t) \leq \bar{a}_t$ for all $t$. Therefore, we see:
+Recall that the tangential acceleration of the particle $p$ is bounded by $\bar{a}_{t}$. This means that $a_t(t) \leq \bar{a}_t$ for all $t$. Therefore, we see:
 \begin{align}
-  d(t) &\leq \int_0^t \int_0^t \bar{a}_t dt_1 dt_2\\
+d(t) &\leq \int_0^t \int_0^{t_2} \bar{a}_t dt_1 dt_2\\
   &= \frac{\bar{a}_t t^2}{2}
@@
 
-If the particle travels for time $t < T_{min}$, then it is impossible for the point mass to reach $\vec{X_2}$ when starting at $\vec{X_1}$.
+If the particle travels for time $t < T_{min}$, then it is impossible for the particle to reach $\vec{X_2}$ when starting at $\vec{X_1}$.
 This is because $p$ cannot reach $\vec{X}_2$ in the $x$ direction when $t < \sqrt{\frac{2 d'}{\bar{a}}}$ because it is impossible for $p$ to reach any point whose $x$-coordinate is $x_2$, so it is obviously impossible to reach $(x_2, 0) = \vec{X_2}$.
 
-Moreover, if there exists some time $t < T_{min}$ when $\theta(t) \neq 0$, then it is also impossible for the point mass to reach $\vec{X_2}$.
+Moreover, if there exists some time $t < T_{min}$ when $\theta(t) \neq 0$, then it is also impossible for the particle to reach $\vec{X_2}$ by time $T_{min}$.
 Suppose that there are two particles $p_1$ and $p_2$ both accelerating at $a_t(t) = \bar{a}_t$.
@@
 Thus, there must exist time $t_s$ where $\theta_p(t') = 0$ for all $t' > t_s$ in the fastest path $\bhat{\gamma_p}$.
-Note that $\gamma_{p_1}$ will contain this point.
 This is a necessary, but not sufficient condition for being a fastest path.
@@
 For particle $p_1$, we know that $|a_c(t')| = \bar{a}_c$ for all $t' < t_s$ because $p_1$ is minimizing $|\theta_{p_1}(t)|$.
-Thus, we see that $p_1$ traces out an arc of a circle with radius $R_{min} = \frac{\bar{v}}{\bar{a}_c}$ because we know that $|a_c(t')| = \bar{a}_c$ for all $t' < t_s$.
+Thus, we see that $p_1$ traces out an arc of a circle with radius $R_{min} = \frac{\bar{v}}{\bar{a}_c}$.
 
-Now let us introduce a particle $p_2$ with the same conditions as $p_1$.
-However, at some time $t_b < t_s$, $p_2$ will choose $a^{p_2}_c$ such that $|a^{p_2}_c| \neq \bar{a}_c$ so that $p_2$'s centripetal acceleration diverges from $p_1$'s centripetal acceleration.
-We shall show that $p_2$'s fastest path after this divergence is worse than $p_1$'s fastest path, which will allow us to conclude that deviations from $p_1$ are suboptimal.
+Now let us introduce a particle $p_2$ with the same conditions as $p_1$ except that at some time $t_b < t_s$, $p_2$ will choose $a^{p_2}_c$ such that $|a^{p_2}_c| \neq \bar{a}_c$ so that $p_2$'s centripetal acceleration diverges from $p_1$'s centripetal acceleration.
+We shall show that $p_2$'s fastest path after this divergence is worse than $p_1$'s fastest path, which will allow us to conclude that deviations from $\gamma_{p_1}$ are suboptimal.
 
@@
 The inequality was obtained because $\bar{a}_c - a^{p_2}_c(t_b) > 0$.
-This directly implies that $r_1(t_b + \epsilon) < r_2(t_b + \epsilon)$ for some small $\epsilon > 0$.
+This directly implies that $r_{p_1}(t_b + \epsilon) < r_{p_2}(t_b + \epsilon)$ for some small $\epsilon > 0$.
 Therefore the distance left to travel for $p_1$ is less than the distance left for $p_2$ at $t_b + \epsilon$ time, i.e.
@@
 \begin{eqnarray}
-  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_1} (t_b) |}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
+  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_2} (t_b) |}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
 \end{eqnarray}

### 2013-10-10 introduction.tex
Fixing typos
Added more to intro.

@@
-In this paper, we shall examine optimal paths for a particle.
-
-Our model problem is a particle moving in $\R^2$ with constrained acceleration.
-The particle must navigate around cones (points in $\R^2$) to reach a final position.
-The goal is to minimize the total time spend navigating to the final position.
-
-We first present a polar coordinate representation of a particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system.
-This allows us to devise some simple lemmas about the motion of the particle.
-
-After developing an intuition for particles and particle paths, we then move on to the more complicated problem of deriving governing rules for optimal paths between points.
-
-Finally, we tackle the problem of finding an optimal path around cones.
+The problem of finding optimal paths between points for a particle with fixed speed is interesting because many attributes of an optimal path are intuitively obvious, but rigorously proving them is much more difficult.
+One's first assumption would be that the optimal path between points A and B, would be to travel in a straight line from point A to B.
+This would be true in the simple case where the turning rate is not constrained, but it is not true in the general case when a particle has a constrained turning rate and starts with some nonzero velocity not directed towards B.
 
@@
 
-The problem of finding an optimal trajectory is interesting because of its applications in physics.
+In physics and computational geometry the problem of finding the shortest path given constraints on the radius of curvature.
+
 There are many instances where finding optimal paths is important.
-For instance, a race car driver wants to know the fastest way to get from one point to another so that he can win his race.
-For another example, imagine you are sending a spacecraft to a particular destination in space and would like the fastest means of getting there.
+For instance, a race car driver wants to know the optimal way to get from one point to another so that he can win his race.
+For another example, imagine you are sending a spacecraft to a particular destination in space and would like the optimal means of getting there.
 
@@
 Understanding how to find optimal trajectories will provide greater insight into solving problems like these.
+
+\subsection{Problem Description}
+
+Given a particle, $p$, moving in $\R^2$, we set constraints on its position, velocity .
+The particle has a starting position and velocity, and must navigate in $\R^2$ to reach a final position.
+The goal is to minimize the total time spent navigating to the final position.
+
+\subsection{Outline}
+
+We first present a modified polar coordinate representation of the particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system.
+This allows us to devise some simple lemmas about the motion of the particle.

### 2013-10-10 paper.tex
eps for pdflatex
Change particle definitions.
Finish modifying particle and path defs.
Changing wording and adding filler.
Fixing typos
Added more to intro.

--- 2013-09-28 paper.tex
@@
 \usepackage{subcaption}
+\usepackage{epstopdf}
 \usepackage{hyperref} % Enable embedded hyperlinks.
@@
 
-\title[The 18.821 report]{The 18.821 Mathematics Project Lab Report 
-[Proofs]} 
-% the first [...] gives a brief version of the title, which is long!
+\title[Fastest Paths in R2]{Fastest Paths Between Points in $\R^2$ for a Particle Moving with Constant Speed and Bounded Centripetal Acceleration}
 
@@
 \maketitle
+
+\subsection*{Abstract}
+
+This paper investigates fastest paths for a particle moving between two points in $\R^2$.
+A modified polar coordinate system is defined, which we use to derive differential equations to model the particle's motion.
+These equations allow us to describe theorems about fastest paths between points.
+The results of this paper can by applied to modeling a particle's motion in $\R^2$ and to calculating shortest paths in $\R^2$.
 
@@
 
-\section{Turning Around Cones}
-\input{cone_theorems.tex}
+\section{Conclusion}
+\input{conclusion.tex}
 

### 2013-10-10 particle_definitions.tex
Added more to intro.

@@
-In this section, we will provide some basic definitions about particles and paths. These will lay the groundwork for thinking about optimal paths.
+Now we will provide some basic definitions about particles and paths, which will lay the groundwork for thinking about fastest paths.
 
 \begin{definition}
-  A n-dimensional path $\gamma(t): [T_0(\gamma), T_f(\gamma)] \to \mathrm{R}^n$ is a function which maps a time $t \in [T_0(\gamma), T_f(\gamma)]$ to a position $\bvec{X} \in \mathrm{R}^n$.
+  A path $\gamma(t): [T_0(\gamma), T_f(\gamma)] \to \mathrm{R}^2$ is a function which maps a time $t \in [T_0(\gamma), T_f(\gamma)]$ to a position $\bvec{X} \in \mathrm{R}^2$.
 The path $\gamma$ begins at time $T_0(\gamma)$ and ends at time $T_f(\gamma)$.
-\end{definition}
-
-\begin{definition}
-  A planar path is a path in $\R^2$.
 \end{definition}
@@
 
-  A particle is restricted if there are conditions on its position and the time derivatives of its position. Given a particle, a valid path is a path that the particle can travel along.
+  A particle is restricted if there are conditions on its position and the time derivatives of its position.
+Given a particle, a valid path is a path that the particle can travel along without violating its restrictions.
 \end{definition}
@@
   A particle's speed is $v(t)$, and its direction of motion is $\bhat{v}$.
+
+  A particle with constant speed, is a particle with zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
 \end{definition}
@@
 \begin{definition}
-  The centripetal acceleration, $\bvec{a_c}$, of a particle, $p$, is the component of its acceleration in the direction perpendicular to its direction of motion.
+  The centripetal acceleration, $\bvec{a_c}(t)$, of a particle, $p$, is the component of its acceleration in the direction perpendicular to its direction of motion.
 
-  In rectangular coordinates, the sign of $a_c$ is defined to be the sign of the projection of $\bhat{a_c}$ onto $\bhat{x}$.
+  In rectangular coordinates, the sign of $a_c(t)$ is defined to be the sign of the projection of $\bhat{a_c}(t)$ onto $\bhat{x}(t)$.
 
-  In polar coordinates, the sign of $a_c$ is defined to be the sign of the projection of $\bhat{a_c}$ onto $\bhat{r}$.
+  In polar coordinates, the sign of $a_c(t)$ is defined to be the sign of the projection of $\bhat{a_c}(t)$ onto $\bhat{r}(t)$.
 \end{definition}
@@
 \begin{definition}
-  The tangential acceleration, $a_t$, of a particle, is the component of the acceleration of the particle in its direction of motion.
+  The tangential acceleration, $a_t(t)$, of a particle, is the component of the acceleration of the particle in its direction of motion.
 
-  \[a_t \coloneqq \frac{dv}{dt}\]
+  \[a_t(t) \coloneqq \frac{dv(t)}{dt}\]
 \end{definition}
@@
 
-Unless otherwise specified, the motion of particle moving along planar paths  will be described in polar coordinates, along with an extra parameter $\theta$, as is shown in Figure \ref{fig:polar-param}.
+Before we introduce the equations governing a particle's motion in $\R^2$, we must first define a coordinate system to describe its motion.
+Unless otherwise specified, the motion of particles in this paper will be described in polar coordinates that contain an extra parameter $\theta$, that is shown in Figure \ref{fig:polar-param}.
 
@@
 
-$\theta(t), \phi(t) \in [-\pi, \pi]$. From now on, $\abs{\theta(t)}$ and $\abs{\phi(t)}$ will be used, since there is a symmetry in the system about $\bhat{r}$.
+Note that $\theta(t), \phi(t)$ are directional angles, so $\theta(t), \phi(t) \in [-\pi, \pi]$.
+From now on, we will only use $\abs{\theta(t)}$ and $\abs{\phi(t)}$, since there is a symmetry in the system about $\bhat{r}$.
 
 \begin{lemma}
-The time derivative of $\theta$ is given by
-\[
-\frac{d\abs{\theta(t)}}{dt} = \frac{a_c}{v}
-\]
+The time derivative of $\theta(t)$ is given by
+
+\begin{equation}\label{eq:theta-deriv}
+\frac{d\abs{\theta(t)}}{dt} = \frac{d\abs{\phi(t)}}{dt} + \frac{a_c(t)}{v(t)}
+\end{equation}
+
 \end{lemma}
@@
 
-If we look at a point, $p$, subject to only centripetal acceleration, $a_c$, the change in $\bvec{v}$ over an infinitesimal time, $dt$, is shown in Figure \ref{fig:theta-deriv} (the two vectors, $\bvec{v}$ and $\bvec{v}+\bvec{dv}$, are superimposed).
+$\theta(t)$ is composed of $\phi(t)$ plus the angle between $\bhat{v}(t)$ and the horizontal, which we can temporarily call $\beta(t)$.
+$\phi(t)$ is the component of $\theta(t)$ in the polar coordinate system, and changes as the point moves with respect to the point B.
+$\beta(t)$ can be thought of as the component of $\theta(t)$ in the Cartesian coordinate system, and it only changes when $a_c(t)$ is nonzero.
+
+So differentiating, we get
+
+\[
+\frac{d\abs{\theta(t)}}{dt} = \frac{d\abs{\phi(t)}}{dt} + \frac{d\beta(t)}{dt}
+\]
+
+To find $\frac{d\beta(t)}{dt}$, we can look at a point, $p$, subject to nonzero centripetal acceleration, $a_c(t)$, and zero tangential acceleration.
+The change in $\bvec{v(t)}$ over an infinitesimal time, $dt$, is shown in Figure \ref{fig:theta-deriv} (the two vectors, $\bvec{v(t)}$ and $\paren{\bvec{v(t)}+\bvec{dv(t)}}$, are superimposed).
 
@@
 
-From the definition of $a_c$
+$a_c(t)$ is defined to be the component of acceleration perpendicular to the direction of motion, so
 
 \[
-\frac{dv}{dt} = a_c
+\frac{dv(t)}{dt} = a_c(t)
 \]
 
-Since $dv = d\abs{\theta} v$, then
+Since $dv(t) = -d\beta(t) v(t)$, then
+
 \[
-\frac{d\abs{\theta}}{dt} = \frac{a_c}{v}
+\frac{d\beta(t)}{dt} = -\frac{a_c(t)}{v(t)}
 \]
+
+So
+
+\[
+\frac{d\abs{\theta(t)}}{dt} = \frac{d\abs{\phi(t)}}{dt} - \frac{a_c(t)}{v}
+\]
+
+The proof of the lemma in the case where $a_t(t)$ is nonzero is very similar, since the component of $\bvec{dv(t)}$ in the direction $\bhat{v(t)}$ is negligible compared to $v(t)$.
+
 \end{proof}
-
-The proof of the lemma in the case where $a_t$ is also nonzero is very similar, since the component of $\bvec{dv}$ in the direction $\bhat{v}$ is negligible compared to $v$.
 
@@
 \begin{align}
-  \frac{dr(t)}{dt}& = -v(t) \, \cos\paren{\abs{\theta(t)}}\label{eq:r-deriv}\\
-  \frac{d\abs{\phi(t)}}{dt}& = \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}}\label{eq:phi-deriv}\\
+  \frac{dr(t)}{dt}& = -v(t) \, \cos\paren{\abs{\theta(t)}}\label{eq:r-diff}\\
+  \frac{d\abs{\phi(t)}}{dt}& = \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}}\label{eq:phi-diff}\\
   \frac{d\abs{\theta(t)}}{dt}& = \frac{d\abs{\phi(t)}}{dt} - \frac{a_c(t)}{v(t)}\\
-  &= \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}} - \frac{a_c(t)}{v(t)}\label{eq:theta-deriv}\\
-  \intertext{Applying the chain rule to (\ref{eq:r-deriv})}
+  &= \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}} - \frac{a_c(t)}{v(t)}\label{eq:theta-diff}\\
+  \intertext{Applying the chain rule to (\ref{eq:r-diff})}
   \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{dv(t)}{dt} \cos\paren{\abs{\theta(t)}} + v(t) \sin\paren{\abs{\theta(t)}} \frac{d\abs{\theta(t)}}{dt}\\
   &\begin{aligned}
-    = -a_t \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
-    &\qquad - \sin\paren{\abs{\theta(t)}} a_c(t) \label{eq:r-deriv-2}
+    = -a_t(t) \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
+    &\qquad - \sin\paren{\abs{\theta(t)}} a_c(t) \label{eq:r-diff-2}
   \end{aligned}

### 2013-10-10 path_theorems.tex
Added more to intro.

@@
-Now that we have defined our notation, we are ready to think about the problem of optimal trajectories.
-
-The simplest problem to tackle first is to find the optimal trajectory from a starting position, $\bvec{X_0}$, to a final position, $\bvec{X_f}$.
-Working in a polar coordinate system centered on $\bvec{X_f}$, it is clear, that our goal is achieved when $r = 0$.
-Furthermore, $\theta(t)$ must be $0$ before reaching $\bvec{X_f}$, otherwise, it will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-deriv}).
+Now that we have defined a coordinate system, we are ready to think about particle paths.
 
 \begin{lemma}
-  If $a_t=0$ and $a_c \le \bar{a}_{c}$, then the minimum radius of curvature of a particle's trajectory is given by
+  Given a particle, $p$, with constant speed and bounded centripetal acceleration, $\abs{a_c(t)} \le \bar{a_c}$, the minimum radius of curvature of the particle's trajectory is given by
+
   \begin{equation}
-  R_{min} = \frac{v^2}{\bar{a}_{c}}
+    R_{min} = \frac{\bar{v}^2}{\bar{a}_c}
   \end{equation}
@@
 \[
-  R = \frac{v^2}{a_c}
+  R(t) = \frac{v(t)^2}{a_c(t)}
 \]
@@
 \[
-  a_c \le \bar{a}_{c} \to \frac{1}{\bar{a}_c} \ge \frac{1}{\bar{a}_{c}}
+  a_c(t) \le \bar{a}_c \to \frac{1}{a_c} \ge \frac{1}{\bar{a}_c}
 \]
 \end{proof}
+
+Knowing this fact, the simplest problem to tackle first is one with infinite centripetal acceleration, which means that a particle can change its direction of motion to an arbitrary direction infinitely fast, $\frac{d\abs{\theta}}{dt}$ is unbounded.
+We now tackle the problem of finding a fastest path from $\bvec{X_1}$ to $\bvec{X_2}$.
+Working in our modified polar coordinate system centered on $\bvec{X_2}$, it is clear, that our goal is achieved when $r(t) = 0$.
+Furthermore, it is important that $\theta(t)$ approach $0$ as $r(t) \to 0$, otherwise, the particle will pass by $\bvec{X_2}$.
+Equation will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-diff}).
 
@@
 \begin{proof}
-Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma \ref{lemma:intermediate-theta} $\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$.
-Since all of the time derivatives in (\ref{eq:r-deriv}) - (\ref{eq:theta-deriv}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the optimal strategy should be the same, regardless of $r$.
-In other words, there can not be multiple cases for optimal strategies based on $r$.
+Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma ????
+$\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$.
+Since all of the time derivatives in (\ref{eq:r-diff}) - (\ref{eq:theta-diff}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the fastest strategy should be the same, regardless of $r$.
+In other words, there can not be multiple cases for fastest strategies based on $r$.
 \end{proof}
@@
 \begin{theorem}
-  \label{theorem:line-proof}
+  \label{thm:line-proof}
   Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$ and no initial speed moving with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
@@
 \begin{corollary}
-  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in Theorem \ref{theorem:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
+  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in Theorem \ref{thm:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
 \end{corollary}
-\proof We have already shown in Theorem \ref{theorem:line-proof} that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them.
+\proof We have already shown in Theorem \ref{thm:line-proof} that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them.
 Moreover, we showed that when travelling along the fastest path, the particle must have tangential acceleration of $\bar{a}_t$.
@@
 This is a simple case of the more general problem.
-We shall now examine optimal trajectories when the initial velocity is non-zero but when the centripetal acceleration is bounded.
+We shall now examine fastest trajectories when the initial velocity is non-zero but when the centripetal acceleration is bounded.
 These conditions are much closer to physical reality, because it is often the case that you want to find a fastest path after you have already started moving.
-Moreover, Theorem \ref{theorem:line-proof} assumed that centripetal acceleration was unbounded so that the particle could turn on a dime in any direction.
+Moreover, Theorem \ref{thm:line-proof} assumed that centripetal acceleration was unbounded so that the particle could turn on a dime in any direction.
 This is not realistic because most physical objects have momentum when they are travelling at high speeds, making it much more difficult to turn.
@@
 The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
-  \label{theorem:restricted-theta}
+  \label{thm:restricted-theta}
 \end{theorem}
@@
 
-To do this, we will invoke a lemma which is closely related to Theorem \ref{theorem:line-proof}:
+To do this, we will invoke a lemma which is closely related to Theorem \ref{thm:line-proof}:
 
@@
 
-The lemma says that if a particle starts with initial velocity pointing directly towards $\bvec{X}_f$, then it is optimal to continue moving towards $\bvec{X}_f$ in a straight line.
-The proof of this lemma is very similar to the proof for Theorem \ref{theorem:line-proof}, so we will omit it.
+The lemma says that if a particle starts with initial velocity pointing directly towards $\bvec{X}_f$, then it is fastest to continue moving towards $\bvec{X}_f$ in a straight line.
+The proof of this lemma is very similar to the proof for Theorem \ref{thm:line-proof}, so we will omit it.
 
@@
 Now let us introduce a particle $p_2$ with the same conditions as $p_1$ except that at some time $t_b < t_s$, $p_2$ will choose $a^{p_2}_c$ such that $|a^{p_2}_c| \neq \bar{a}_c$ so that $p_2$'s centripetal acceleration diverges from $p_1$'s centripetal acceleration.
-We shall show that $p_2$'s fastest path after this divergence is worse than $p_1$'s fastest path, which will allow us to conclude that deviations from $\gamma_{p_1}$ are suboptimal.
+We shall show that $p_2$'s fastest path after this divergence is worse than $p_1$'s fastest path, which will allow us to conclude that deviations from $\gamma_{p_1}$ are subfastest.
 
 We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof.
-Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section.
-We can use equation \ref{eq:r-deriv-2} to obtain the following:
+Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section.
+We can use equation \ref{eq:r-diff-2} to obtain the following:
 
@@
 
-We can also use equation \ref{eq:theta-deriv} to obtain the following for the difference in angles:
+We can also use equation \ref{eq:theta-diff} to obtain the following for the difference in angles:
 \begin{eqnarray}

### 2013-10-10 conclusion.tex
Added more to intro.
Small changes to conclusion.

@@
 We also showed that when a particle has bounded accleration, the optimal strategy for getting to another point as fast as possible is to minimize the angle that the particle's velocity vector makes with the ending point.
+
+\subsection{Future Work}
+
+Future work should first involve a rigorous proof of .
+Furthermore, the special case of optimal paths for when the particle is \"too close\" to the final point, should be researched.
+This special case is very interesting, because it involves moving away from the final point for a period of time, and the shape of the optimal path does not appear to be intuitive.
+
+To make the problem more general, one could extend the problem to include particles moving with varying speed.
+Equations \ref{eq:r-diff} - \ref{eq:r-diff-2} still apply in this case, but the analysis is more complex in this case.

### 2013-10-10 introduction.tex
Small changes to conclusion.

@@
 
+\subsection{The Problem}
+
+Given a particle that starts at a position in $\R^2$, has initial velocity, and has constrained acceleration, what is the path in $\R^2$ for the particle to take to reach a final position in $\R^2$, such that the time spent traveling from the starting position to the ending position is minimized.
+The particle can have restrictions on its position, velocity, and acceleration.
+
 \subsection{Motivation}
 
-In physics and computational geometry the problem of finding the shortest path given constraints on the radius of curvature.
+The problem of finding a fastest path for a particle with constant speed is usefull because it is identical to the problem of finding a shortest path in $\R^2$ given constraints on the radius of curvature of the path, which appears in fields such as physics and computational geometry.
+One could imagine a race car driver navigating a racetrack with constant speed, as a physical example of the problem.
 
-There are many instances where finding optimal paths is important.
-For instance, a race car driver wants to know the optimal way to get from one point to another so that he can win his race.
-For another example, imagine you are sending a spacecraft to a particular destination in space and would like the optimal means of getting there.
+This example directly motivates our problem, because a racecar driver has a turning rate limited by friction.
 
-The space example directly motivates our model problem.
-On a spacecraft, there is a limited amount of acceleration that is possible (provided by thrusters).
-One would potentially like to navigate to a planet while moving around obstacles.
-
-Understanding how to find optimal trajectories will provide greater insight into solving problems like these.
-
-\subsection{Problem Description}
-
-Given a particle, $p$, moving in $\R^2$, we set constraints on its position, velocity .
-The particle has a starting position and velocity, and must navigate in $\R^2$ to reach a final position.
-The goal is to minimize the total time spent navigating to the final position.
+Understanding how to find optimal paths for a particle with constant speed moving in $\R^2$ will provide insight into solving even more complicated problems with varying speed and more dimensions such as spacecraft trajectories.
 

### 2013-10-10 path_theorems.tex
Small changes to conclusion.

@@
 Now that we have defined a coordinate system, we are ready to think about particle paths.
+Working in our modified polar coordinate system centered on $\bvec{X_2}$, it is clear, that our goal is achieved when $r(t) = 0$.
+Furthermore, it is important that $\theta(t)$ approach $0$ as $r(t) \to 0$, otherwise, the particle will pass by $\bvec{X_2}$.
 
-\begin{lemma}
+\begin{lemma} \label{lem:r-curve}
   Given a particle, $p$, with constant speed and bounded centripetal acceleration, $\abs{a_c(t)} \le \bar{a_c}$, the minimum radius of curvature of the particle's trajectory is given by
@@
 \begin{proof}
+
 This comes directly from the definition of radius of curvature for a particle without any tangential acceleration:
@@
 
-and the fact that
+and
 
@@
 
-Knowing this fact, the simplest problem to tackle first is one with infinite centripetal acceleration, which means that a particle can change its direction of motion to an arbitrary direction infinitely fast, $\frac{d\abs{\theta}}{dt}$ is unbounded.
-We now tackle the problem of finding a fastest path from $\bvec{X_1}$ to $\bvec{X_2}$.
-Working in our modified polar coordinate system centered on $\bvec{X_2}$, it is clear, that our goal is achieved when $r(t) = 0$.
-Furthermore, it is important that $\theta(t)$ approach $0$ as $r(t) \to 0$, otherwise, the particle will pass by $\bvec{X_2}$.
-Equation will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-diff}).
-
-We can also investigate how the particle moves along a fastest path.
-In particular, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
-
-\begin{theorem}
-A 2-dimensional particle, $p$, traveling along a fastest path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} \leq 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
-\end{theorem}
-
-\begin{proof}
-Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma ????
-$\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$.
-Since all of the time derivatives in (\ref{eq:r-diff}) - (\ref{eq:theta-diff}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the fastest strategy should be the same, regardless of $r$.
-In other words, there can not be multiple cases for fastest strategies based on $r$.
-\end{proof}
-
-% -----------------------------------------------------------------------------
+With Lemma \ref{lem:r-curve} in mind, the simplest problem to tackle first is the fastest path from $\bvec{X_1}$ to $\bvec{X_2}$ where centripetal acceleration is unbounded, which means that a particle can change its direction of motion to an arbitrary direction infinitely fast, $\frac{d\abs{\theta}}{dt}$ is unbounded.
+The following Theorem
 
@@
 
-Without loss of generality, we can define a cartesian coordinate system, where the origin is at $\bvec{X_1}$ and the positive x-axis passes through $\bvec{X_2}$.
-Let us say that the two points in our cartesian coordinate system become $(0,0)$ and $(x_2, 0)$ respectively.
+Without loss of generality, we can define a Cartesian coordinate system, where the origin is at $\bvec{X_1}$ and the positive x-axis passes through $\bvec{X_2}$.
+Let us say that the two points in our Cartesian coordinate system become $(0,0)$ and $(x_2, 0)$ respectively.
 
@@
 
-To find the distance $l_x(t)$ travelled in the $\bhat{x}$ direction, we can use the relation:
+To find the distance $l_x(t)$ traveled in the $\bhat{x}$ direction, we can use the relation:
 \begin{align}
@@
 \qed
+
+We can also investigate how the particle moves along a fastest path.
+In particular, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
+
+\begin{theorem}
+A 2-dimensional particle, $p$, traveling along a fastest path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} \leq 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
+\end{theorem}
+
+\begin{proof}
+Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma ????
+$\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$.
+Since all of the time derivatives in (\ref{eq:r-diff}) - (\ref{eq:theta-diff}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the fastest strategy should be the same, regardless of $r$.
+In other words, there can not be multiple cases for fastest strategies based on $r$.
+\end{proof}
+
+% -----------------------------------------------------------------------------
 

### 2013-10-10 particle_definitions.tex
Add back figure pdfs.

@@
   A particle's speed is $v(t)$, and its direction of motion is $\bhat{v}$.
-
-  A particle with constant speed, is a particle with zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
 \end{definition}
@@
 Before we introduce the equations governing a particle's motion in $\R^2$, we must first define a coordinate system to describe its motion.
-Unless otherwise specified, the motion of particles in this paper will be described in polar coordinates that contain an extra parameter $\theta$, that is shown in Figure \ref{fig:polar-param}.
+Unless otherwise specified, the motion of particles in this paper will be described in a modified polar coordinate system that contain an extra parameter $\theta$, that is shown in Figure \ref{fig:polar-param}.
+We will refer to this system as the B centered particle coordinate system.
 
-\includefig{polar_param.eps}{A particle moving in 2-dimensional polar coordinate system centered at B}{polar-param}
+\includefig{polar_param.eps}{A particle moving in a B centered particle coordinate system}{polar-param}
 

### 2013-10-10 path_theorems.tex
Add back figure pdfs.

@@
 
-% -----------------------------------------------------------------------------
-
 \section{Constant Speed Conditions}
@@
 
-To begin proving things about the fastest path, we first formalize the conditions we will be using:
-
 \begin{definition}
-  A fixed speed particle is a particle such that: $\bvec{X} \in \R^2$, $a_t = 0$, $v(t) = \bar{v}$.
+  A particle with constant speed, is a particle with zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
 \end{definition}
@@
 \begin{definition}
-  A particle with bounded centripetal acceleration is a particle with the following condition: $\norm{a_c} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
+  A particle with bounded centripetal acceleration is a particle with $\norm{a_c(t)} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
 \end{definition}
 
-Now we shall use the following shorthand throughout this section to talk about the conditions on a particle:
-
-\begin{definition}
-  A particle with constant speed conditions is a fixed speed particle with bounded centripetal acceleration.
-\end{definition}
+Throughout the rest of this paper, all the particles we will deal with will have constant speed and bounded centripetal acceleration.
 
@@
   \label{conjecture:fastest-paths}
-  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{X}_1, \bvec{X}_2$ respectively.
-Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_1) = d(\bvec{X}_f, \bvec{X}_2) > R_{min}$.
-If $d(\bvec{X}_1, \bvec{X}_f) \leq d(\bvec{X}_2, \bvec{X}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
+  Let particles $p_1, p_2$ have centripetal acceleration bounded by $\bar{a_c}$, constant speed $\bar{v}$, starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and final position $\bvec{X}_f$.
+Both particles move in a $X_f$ centered particle coordinate system.
+If $r_1(T_0) \leq r_2(T_0)$ and $\theta_1(T_0) < \theta_1(T_0)$, then $T_f(\hat{\gamma_1}) < T_f(\hat{\gamma_2})$.
 \end{conjecture}
 
-This conjecture comes from physical intuition.
-If two particles $p_1$ and $p_2$ are attempting to arrive at a particular ending point $\bvec{X}_f$, and $p_2$ is farther away than $p_1$ and also has an initial angle $\theta$ to $\bvec{X}_f$ that is larger than $p_1$'s initial angle, then $p_2$ must take a longer time to turn towards $\bvec{X}_f$ and must travel a longer distance than $p_1$.
-Because of this, it seems to be the case that $p_1$'s fastest path is faster than $p_2$'s fastest path.
+In words, this conjecture states that if a particle, $p_1$, is closer to the final position than another, $p_2$, and has a smaller $\theta(t)$, then its optimal path to the final position is shorter.
+The intuition behind this is that $p_2$ must travel a longer distance than $p_1$ to reach the final position, because it is further away.
+Furthermore, one could also imagine, that
 

### 2013-10-10 path_theorems.tex
In process of adding second two point proof.

@@
 
-\begin{theorem}
-  \label{thm:line-proof}
+Note: we provide two nearly identical theorems with different proofs, to provide the reader with different ways to think about the problem.
+
+\begin{theorem}\label{thm:line-proof}
+  (John Wang's version)
+
   Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$ and no initial speed moving with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
@@
 In particular, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
+
+\begin{theorem}\label{thm:theta-zero}
+  Given a particle $p$, if $\abs{\theta(t_1)} = 0$ at some time $t_$, then an optimal path, $\hat{\gamma}(t)$ has $\abs{\theta(t)} \ge 0$ for all $t \ge t_1$.
+Furthermore, given two valid paths, $\gamma_1(t)$ and $\gamma_2(t)$, then $T_f(\gamma_1) \le T_f(\gamma_2)$ if $\abs{\theta_1(t_1)} = 0$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem}
+  (Jonathan Allen's version)
+
+  Given a particle $p$ with initial position $\bvec{X_1}$, initial velocity $\bvec{v}(t)$, bounded tangential acceleration $a_t \le \bar{a}_t$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ is the line segment from $\bvec{X_1}$ to $\bvec{X_2}$.
+\end{theorem}
+
+\begin{proof}
+
+  Define two particles, $p_1$ and $p_2$, that have the same initial conditions as particle $p$ in the Theorem statement.
+
+  For some arbitrary $\epsilon > 0$.
+Define the centripetal acceleration of $p_1$ to be $a_{c, 1}$, and let $\bar{a_{c,\epsilon}}$ be the maximum value of $a_{c, 1}$ for $t \in [T_0, \epsilon]$.
+Now define the centripetal acceleration of $p_2$ to be
+
+  \[
+    a_c(t) = \begin{cases}
+      \theta(T_0) / \epsilon \quad &\text{for} \quad t \in [T_0, T_0 + \epsilon]\\
+      0 \quad &\text{for} \quad otherwise
+    \end{cases}
+  \]
+
+  If we take the limit as $\epsilon \to \infty$, we get
+
+  \[
+
+  \]
+
+  \begin{align}
+    \theta_1(T_0(\gamma_1))& = \int_{t=T_0(\gamma_1)}^{T_0(\gamma_1)^+} \frac{d\abs{\phi(t')}}{dt} - \frac{\theta(T_0)}{\epsilon \v(t)} dt'\\
+    & = 0 \quad \text{for} \quad \epsilon \to T_0
+  \end{align}
+
+  Furthermore,
+
+  \begin{align}
+    \theta_2(T_0)& = \int_{t=T_0(\gamma_1)}^{T_0(\gamma_1)^+} \frac{d\abs{\phi(t')}}{dt} - \frac{\theta(T_0)}{\epsilon \v(t)} dt'\\
+    & = \theta(T_0)
+  \end{align}
+
+  From Theorem \ref{thm:theta-zero} we know that $\theta(t)$ must now be $0$, for all $t \ge T_0$, thus the particle is traveling in the $-\bhat{r}$ direction for $t \in [T_0, T_f]$, which is the line segment from $X_1$ to $X_2$.
+
+\end{proof}
 

### 2013-10-11 conclusion.tex
Finish checking intro and definitions. Made paper smaller. Added new line proof.

@@
-In this paper, we have formalized many of the things that intuition would tell us.
-Namely, we have shown that a straight line is the fastest way to get between two points.
-This fact is unsurprising because of the fact that acceleration in a single direction (toward the finish point) is the least wasteful means of getting to the finish.
+In this paper, we developed a number of simple lemmas governing the motion of a particle with bounded acceleration.
+We also formalized many of the things that intuition tells us are true.
+Namely, we have shown that a straight line is the fastest path for a particle to take to get to a point, if centripetal acceleration is unbounded.
+This fact is unsurprising, since the particle should be accelerating towards the point as much as possible, which occurs when it is moving directly towards the point.
 
-We developed a number of simple lemmas governing the motion of a volume-less particle with bounded acceleration.
-We also showed that when a particle has bounded accleration, the optimal strategy for getting to another point as fast as possible is to minimize the angle that the particle's velocity vector makes with the ending point.
+We also provided a conjecture that it is also optimal for a particle to orient itself towards the point as quickly as possible, in the case when centripetal acceleration is bounded.
+Assuming this conjecture to be true, we were able to draw more conclusions about optimal paths that can be directly used to calculate optimal paths.
 
@@
 
-Future work should first involve a rigorous proof of .
+Future work should first involve a rigorous proof of \ref{conj:optimal-position}.
 Furthermore, the special case of optimal paths for when the particle is \"too close\" to the final point, should be researched.
@@
 To make the problem more general, one could extend the problem to include particles moving with varying speed.
-Equations \ref{eq:r-diff} - \ref{eq:r-diff-2} still apply in this case, but the analysis is more complex in this case.
+Equations \ref{eq:r-diff} - \ref{eq:r-diff-2} still apply in this case, but the analysis is more complex.

### 2013-10-11 fixed_speed_theorems.tex
Finish checking intro and definitions. Made paper smaller. Added new line proof.

--- 2013-10-10 path_theorems.tex
@@
-Now that we have defined a coordinate system, we are ready to think about particle paths.
-Working in our modified polar coordinate system centered on $\bvec{X_2}$, it is clear, that our goal is achieved when $r(t) = 0$.
-Furthermore, it is important that $\theta(t)$ approach $0$ as $r(t) \to 0$, otherwise, the particle will pass by $\bvec{X_2}$.
+We will now examine the more general case of particles with bounded centripetal acceleration, $\abs{a_c(t)} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
+This case is much more relevant to physical problems, because objects typically have momentum which limits their ability to turn quickly.
+To keep the problem manageable, all particle in this section have zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
 
 \begin{lemma} \label{lem:r-curve}
-  Given a particle, $p$, with constant speed and bounded centripetal acceleration, $\abs{a_c(t)} \le \bar{a_c}$, the minimum radius of curvature of the particle's trajectory is given by
+  Given a particle with constant speed and bounded acceleration, the minimum radius of curvature of the particle's trajectory is given by
 
@@
 
-This comes directly from the definition of radius of curvature for a particle without any tangential acceleration:
+This comes directly from the definition of radius of curvature for a particle with zero tangential acceleration:
 
 \[
-  R(t) = \frac{v(t)^2}{a_c(t)}
+  R(t) = \frac{\bar{v}^2}{a_c(t)}
 \]
@@
 
-With Lemma \ref{lem:r-curve} in mind, the simplest problem to tackle first is the fastest path from $\bvec{X_1}$ to $\bvec{X_2}$ where centripetal acceleration is unbounded, which means that a particle can change its direction of motion to an arbitrary direction infinitely fast, $\frac{d\abs{\theta}}{dt}$ is unbounded.
-The following Theorem
+We must first make a conjecture about how fastest paths behave. Unfortunately, our research has not yet yielded a rigorous proof of the conjecture, but we will provide some intuition behind it.
 
-Now we will show that the fastest path between two points goes in a straight line if there is no initial speed.
-This will formalize the natural intuition that straight lines are the fastest path when there are no obstacles between the start and finish position.
+\begin{conjecture}\label{conj:optimal-position}
+  Given particles $p_1, p_2$ with starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and a final position $\bvec{X}_f$.
+If $r_1(T_0) \leq r_2(T_0)$ and $\abs{\theta_1(T_0)} < \abs{\theta_1(T_0)}$, then $T_f(\hat{\gamma_1}) < T_f(\hat{\gamma_2})$.
+\end{conjecture}
+
+In words, this conjecture states that a particle, $p_2$, further away from $X_f$ cannot overtake another point, $p_1$, that is closer to $X_f$, if $\theta_1(t) \le \theta_2(t)$.
+The intuition behind this is that $p_2$ must travel further than $p_1$ to reach $X_f$, because it is further away.
+Furthermore, one could also imagine, that if this conjecture were not true, then it would be fastest to move away from $X_f$, which seems intuitively wrong.
+
+Assuming that Conjecture \ref{conj:optimal-position} is true, we will move on to prove some theorems about fastest paths.
 
 \begin{theorem}
-  \label{thm:line-proof}
-  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$ and no initial speed moving with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
-\end{theorem}
-
-\begin{proof}
-
-Without loss of generality, we can define a Cartesian coordinate system, where the origin is at $\bvec{X_1}$ and the positive x-axis passes through $\bvec{X_2}$.
-Let us say that the two points in our Cartesian coordinate system become $(0,0)$ and $(x_2, 0)$ respectively.
-
-Now let us examine the particle's motion in the $\bhat{x}$ direction. The speed of the particle is the following
-\begin{equation}
-  v_x(t) = \int_0^t a_x(t_1) dt_1
-\end{equation}
-
-To find the distance $l_x(t)$ traveled in the $\bhat{x}$ direction, we can use the relation:
-\begin{align}
-  l_x(t) &= \int_0^t v_x(t_2) dt_2 \\
-         &= \int_0^t \int_0^{t_1} a_x(t_1) dt_1 dt_2
-\end{align}
-
-Recall that the tangential acceleration of the particle $p$ is bounded by $\bar{a}_{t}$. This means that $a_t(t) \leq \bar{a}_t$ for all $t$. Therefore, we see:
-\begin{align}
-d(t) &\leq \int_0^t \int_0^{t_2} \bar{a}_t dt_1 dt_2\\
-  &= \frac{\bar{a}_t t^2}{2}
-\end{align}
-
-Thus, in order to travel a distance of $l_x(T_f(\hat{\gamma})) = d' = d(\bvec{X_2}, \bvec{X_1})$, it needs to be the case that $T_f(\hat{\gamma}) \geq \sqrt{\frac{2 d'}{\bar{a}_t}}$.
-It is possible to travel from $\vec{X_2}$ to $\vec{X_1}$ in time $T_{min} = \sqrt{\frac{2 d'}{\bar{a}_t}}$ if and only if $a_t(t) = \bar{a}_t$ and $\theta(t) = 0$ for all $t \in [T_0(\gamma), T_{min}]$.
-In other words, the particle must be accelerating at the maximum possible tangential acceleration of $\bar{a}_t$ and it must be accelerating in the straight line direction to $\vec{X_2}$ at all times.
-
-If the particle travels for time $t < T_{min}$, then it is impossible for the particle to reach $\vec{X_2}$ when starting at $\vec{X_1}$.
-This is because $p$ cannot reach $\vec{X}_2$ in the $x$ direction when $t < \sqrt{\frac{2 d'}{\bar{a}}}$ because it is impossible for $p$ to reach any point whose $x$-coordinate is $x_2$, so it is obviously impossible to reach $(x_2, 0) = \vec{X_2}$.
-
-Moreover, if there exists some time $t < T_{min}$ when $\theta(t) \neq 0$, then it is also impossible for the particle to reach $\vec{X_2}$ by time $T_{min}$.
-Suppose that there are two particles $p_1$ and $p_2$ both accelerating at $a_t(t) = \bar{a}_t$.
-Imagine $p_1$ satisfies $\theta_{p_1}(t) = 0$ for all $t$ and that $p_2$ satisfies $\theta_{p_2}(t) = 0$ except for times in some interval $[t_0, t_1]$, the particle $p_2$ sets a constant non-zero angle $\zeta_{p_2}(t) \neq 0$ with the $x$-axis for $t \in [t_0, t_1]$.
-Denote $d_{p}$ as the distance that is left to be travelled by particle $p$ between times $t_1$ and $T_{min}$.
-We can find $d_{p_2}$ in terms of $d_{p_1}$ by using trigonometry:
-
-\begin{eqnarray}
-d_{p_2}^2 = d_{p_1}^2 + \left(\frac{\bar{a}_t (t_1 - t_0)^2}{2} \sin \zeta_{p_2} \right)^2
-\end{eqnarray}
-
-Since $d_{p_2} \geq 0$ by being a distance, $\sin \zeta_{p_2} \neq 0$ by setting $\zeta_{p_2} > 0$, and $t_1 - t_0 > 0$, we know that $d_{p_2} > d_{p_1}$.
-This means that at time $T_{min}$ when $p_1$ has reached its destination at $\Vec{X_2}$, particle $p_2$ still has $d_{p_2} - d_{p_1}$ distance left to travel.
-This means that it is impossible for $\theta(t) > 0$ on the fastest path.
-
-This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$.
-Let us examine the path taken by the point mass $p$ on this fastest path.
-Recall that $a_t(t) = \bar{a}$ for all $t$ along the fastest path.
-This means that there was no centripetal acceleration $|a_c| = 0$.
-In other words, the point mass never turned on its way to reaching the destination point.
-The only way this could have happened is if it travelled along the $x$ axis in a straight line.
-
-Thus, we see that the fastest path is the straight line between $\vec{X_1}$ and $\vec{X_2}$.
-\end{proof}
-
-We can also prove that this fastest path is unique without very much extra work.
-
-\begin{corollary}
-  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in Theorem \ref{thm:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
-\end{corollary}
-\proof We have already shown in Theorem \ref{thm:line-proof} that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them.
-Moreover, we showed that when travelling along the fastest path, the particle must have tangential acceleration of $\bar{a}_t$.
-Since we have starting position $\vec{X_1}$ and initial speed of $0$, the acceleration of the particle uniquely defines a path for the particle.
-
-There is only a single function of the acceleration $a(t) = \bar{a}_t$ which can be satisfied when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
-\qed
-
-We can also investigate how the particle moves along a fastest path.
-In particular, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
-
-\begin{theorem}
-A 2-dimensional particle, $p$, traveling along a fastest path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} \leq 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
-\end{theorem}
-
-\begin{proof}
-Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma ????
-$\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$.
-Since all of the time derivatives in (\ref{eq:r-diff}) - (\ref{eq:theta-diff}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the fastest strategy should be the same, regardless of $r$.
-In other words, there can not be multiple cases for fastest strategies based on $r$.
-\end{proof}
-
-% -----------------------------------------------------------------------------
-
-\section{Constant Speed Conditions}
-
-In the previous section, we made statements about fastest paths between two points when the initial velocity was set to zero.
-We saw that our physical intuition was confirmed and that a straight line was the fastest way to travel between two points.
-
-This is a simple case of the more general problem.
-We shall now examine fastest trajectories when the initial velocity is non-zero but when the centripetal acceleration is bounded.
-These conditions are much closer to physical reality, because it is often the case that you want to find a fastest path after you have already started moving.
-Moreover, Theorem \ref{thm:line-proof} assumed that centripetal acceleration was unbounded so that the particle could turn on a dime in any direction.
-This is not realistic because most physical objects have momentum when they are travelling at high speeds, making it much more difficult to turn.
-
-Assuming bounded acceleration makes the problem more interesting, and also much more difficult if we allow for tangential acceleration.
-In this section, we will eliminate tangential acceleration so that the particle will travel at constant speed with bounded acceleration.
-
-\begin{definition}
-  A particle with constant speed, is a particle with zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
-\end{definition}
-
-\begin{definition}
-  A particle with bounded centripetal acceleration is a particle with $\norm{a_c(t)} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
-\end{definition}
-
-Throughout the rest of this paper, all the particles we will deal with will have constant speed and bounded centripetal acceleration.
-
-To prove things about the fastest path of a particle under constant speed conditions, we shall make Conjecture \ref{conjecture:fastest-paths} about how fastest paths behave.
-
-\begin{conjecture}
-  \label{conjecture:fastest-paths}
-  Let particles $p_1, p_2$ have centripetal acceleration bounded by $\bar{a_c}$, constant speed $\bar{v}$, starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and final position $\bvec{X}_f$.
-Both particles move in a $X_f$ centered particle coordinate system.
-If $r_1(T_0) \leq r_2(T_0)$ and $\theta_1(T_0) < \theta_1(T_0)$, then $T_f(\hat{\gamma_1}) < T_f(\hat{\gamma_2})$.
-\end{conjecture}
-
-In words, this conjecture states that if a particle, $p_1$, is closer to the final position than another, $p_2$, and has a smaller $\theta(t)$, then its optimal path to the final position is shorter.
-The intuition behind this is that $p_2$ must travel a longer distance than $p_1$ to reach the final position, because it is further away.
-Furthermore, one could also imagine, that
-
-If this conjecture is true, then we can provide the strategy for obtaining the fastest path between two points $\bvec{X}_0$ and $\bvec{X}_f$.
-
-\begin{theorem}
-  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$.
-Let $p$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_0) > R_{min}$.
+  Let particle $p$ have initial velocity $\bvec{v_0}$, starting position $\bvec{X}_0$, and ending position $\bvec{X}_f$, such that $d(\bvec{X}_0, \bvec{X}_f) > R_{min}$.
 The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
@@
 We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.
-
-To do this, we will invoke a lemma which is closely related to Theorem \ref{thm:line-proof}:
-
-\begin{lemma}
-  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$ with constant speed conditions.
-If the end position is $\bvec{X}_f$ and $\theta(T_0(\gamma)) = 0$, then the fastest path $\bhat{\gamma_p}$ for particle $p$ follows the straight line between $\bvec{X}_0$ and $\bvec{X}_f$.
-\end{lemma}
-
-The lemma says that if a particle starts with initial velocity pointing directly towards $\bvec{X}_f$, then it is fastest to continue moving towards $\bvec{X}_f$ in a straight line.
-The proof of this lemma is very similar to the proof for Theorem \ref{thm:line-proof}, so we will omit it.
 
@@
 
-We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof.
+We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conj:optimal-position} to finish our proof.
 Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section.
@@
 
-Now, we have satisfied the conditions of Conjecture \ref{conjecture:fastest-paths} since $d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$ and $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
+Now, we have satisfied the conditions of Conjecture \ref{conj:optimal-position} since $d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$ and $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
 This implies that $T_f(\gamma_{p_1}) < T_f(\gamma_{p_2})$.

### 2013-10-11 introduction.tex
Finish checking intro and definitions. Made paper smaller. Added new line proof.

@@
-The problem of finding optimal paths between points for a particle with fixed speed is interesting because many attributes of an optimal path are intuitively obvious, but rigorously proving them is much more difficult.
-One's first assumption would be that the optimal path between points A and B, would be to travel in a straight line from point A to B.
+The problem of finding fastest paths between two points (let's call them A and B) is interesting because many attributes of a fastest path are intuitively obvious, but rigorously proving them is much more difficult.
+One's first assumption would be that the fastest path between A and B, would be to travel in a straight line from A to B.
 This would be true in the simple case where the turning rate is not constrained, but it is not true in the general case when a particle has a constrained turning rate and starts with some nonzero velocity not directed towards B.
+In the general case, it is easier to turn towards B, the further one is away from it, so there is the possibility that it would be fastest for the particle to turn away from B for a short period of time, so that it can then turn towards it more quickly.
+In fact, if the particle is too close to B, it won't have time to turn towards it, and will pass by B.
 
-\subsection{The Problem}
+\subsection{The Problem (more precise terms will be defined later)}
 
-Given a particle that starts at a position in $\R^2$, has initial velocity, and has constrained acceleration, what is the path in $\R^2$ for the particle to take to reach a final position in $\R^2$, such that the time spent traveling from the starting position to the ending position is minimized.
+Given a particle in $\R^2$ starts at a position A in with an initial velocity, what is the path in for the particle to take to reach a final position B, such that the time spent traveling from A to B is minimized.
 The particle can have restrictions on its position, velocity, and acceleration.
+Our model problem has fixed speed and a bounded turning rate.
 
@@
 
-The problem of finding a fastest path for a particle with constant speed is usefull because it is identical to the problem of finding a shortest path in $\R^2$ given constraints on the radius of curvature of the path, which appears in fields such as physics and computational geometry.
-One could imagine a race car driver navigating a racetrack with constant speed, as a physical example of the problem.
+The problem of finding a fastest path for a particle with constant speed is useful because it is identical to the problem of finding a shortest path given constraints on the radius of curvature of the path, which appears in fields such as physics and computational geometry.
 
-This example directly motivates our problem, because a racecar driver has a turning rate limited by friction.
+Intuitively, one could imagine a race car driver navigating a racetrack with constant speed, as a physical example of the problem.
+In fact, this example directly motivates our problem, because a race car driver has a limited turning rate which is created by friction between the wheels and the ground.
 
-Understanding how to find optimal paths for a particle with constant speed moving in $\R^2$ will provide insight into solving even more complicated problems with varying speed and more dimensions such as spacecraft trajectories.
+Understanding how to find fastest paths for a particle with constant speed will also provide insight into solving even more complicated problems which may have varying speed and more dimensions such as spacecraft trajectories.
 
@@
 
-We first present a modified polar coordinate representation of the particle's position around a point and derive a set of differential equations governing the motion of the particle in this coordinate system.
-This allows us to devise some simple lemmas about the motion of the particle.
+We first present a modified polar coordinate system to represent the particle's motion around a point and then derive a set of differential equations governing the motion of the particle in this coordinate system.
+This allows us to devise some simple lemmas about the motion of the particle, and draw some conclusions about fastest paths.

### 2013-10-11 particle_definitions.tex
Finish checking intro and definitions. Made paper smaller. Added new line proof.

@@
-Now we will provide some basic definitions about particles and paths, which will lay the groundwork for thinking about fastest paths.
+We will first provide some basic definitions about particles and paths, which will lay the groundwork for thinking about fastest paths. First we will define what we mean by a particle and a path.
 
@@
   A path $\gamma(t): [T_0(\gamma), T_f(\gamma)] \to \mathrm{R}^2$ is a function which maps a time $t \in [T_0(\gamma), T_f(\gamma)]$ to a position $\bvec{X} \in \mathrm{R}^2$.
-The path $\gamma$ begins at time $T_0(\gamma)$ and ends at time $T_f(\gamma)$.
 \end{definition}
@@
 \begin{definition}
-  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path $\gamma(t)$ where $\gamma(T_0(\gamma)) = \bvec{X_1}$ and $\gamma(T_f(\gamma)) = \bvec{X_2}$.
-\end{definition}
-
-\begin{definition}
-  A particle, $p$, is an object in space with zero volume.
-A particle travels along a path, $\gamma(t)$ if the particle is at position $\gamma(t)$ at time $t$, for all $t \in [T_0(\gamma), T_f(\gamma)]$.
+  A particle $p$ is an object in space with zero volume.
 If a particle is traveling along a path, $\gamma(t)$, then we define a position, $\bvec{X}(t) \coloneqq \gamma(t)$, a velocity, $\bvec{v}(t) \coloneqq \frac{d\gamma(t)}{dt}$, and an acceleration, $\bvec{a}(t) \coloneqq \frac{d^2\gamma(t)}{dt^2}$, for the particle, for all $t \in [T_0(\gamma), T_f(\gamma)]$.
@@
 
+Now we will make our problem statement more rigorous, by defining what a fastest path is.
+
 \begin{definition}
-  Given a particle, a fastest path, $\hat{\gamma}(t)$, between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
+  Given a particle, a fastest path $\hat{\gamma}(t)$ between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
+\end{definition}
+
+Finally, we need to define some terms for a particle's motion which will be needed later on to describe restrictions on a particle's motion.
+
+\begin{definition}
+  The centripetal acceleration $\bvec{a_c}(t)$ of a particle, $p$, is the component of its acceleration in the direction perpendicular to its direction of motion.
 \end{definition}
@@
 \begin{definition}
-  A particle's speed is $v(t)$, and its direction of motion is $\bhat{v}$.
-\end{definition}
-
-\begin{definition}
-  The centripetal acceleration, $\bvec{a_c}(t)$, of a particle, $p$, is the component of its acceleration in the direction perpendicular to its direction of motion.
-
-  In rectangular coordinates, the sign of $a_c(t)$ is defined to be the sign of the projection of $\bhat{a_c}(t)$ onto $\bhat{x}(t)$.
-
-  In polar coordinates, the sign of $a_c(t)$ is defined to be the sign of the projection of $\bhat{a_c}(t)$ onto $\bhat{r}(t)$.
-\end{definition}
-
-\begin{definition}
-  The tangential acceleration, $a_t(t)$, of a particle, is the component of the acceleration of the particle in its direction of motion.
+  The tangential acceleration $a_t(t)$ of a particle is the component of the acceleration of the particle in its direction of motion.
 
@@
 \end{definition}
-
 % -----------------------------------------------------------------------------
@@
 Unless otherwise specified, the motion of particles in this paper will be described in a modified polar coordinate system that contain an extra parameter $\theta$, that is shown in Figure \ref{fig:polar-param}.
-We will refer to this system as the B centered particle coordinate system.
+We will refer to this system as the \textit{B centered particle coordinate system}.
 
@@
 
-Note that $\theta(t), \phi(t)$ are directional angles, so $\theta(t), \phi(t) \in [-\pi, \pi]$.
-From now on, we will only use $\abs{\theta(t)}$ and $\abs{\phi(t)}$, since there is a symmetry in the system about $\bhat{r}$.
+The sign of $a_c(t)$ is defined to be the sign of the projection of $\bhat{a_c}(t)$ onto $-\bhat{r}(t)$; in other words, it is positive when pointing towards B.
+$\theta(t), \phi(t) \in [-\pi, \pi]$, and from now on, we will only use $\abs{\theta(t)}$ and $\abs{\phi(t)}$, since there is a symmetry in the system about $\bhat{r}$.
 
 \begin{lemma}
-The time derivative of $\theta(t)$ is given by
+The time derivative of $\abs{\theta(t)}$ is given by
 
@@
 
-So differentiating, we get
+Differentiating, we get
 
@@
 
-To find $\frac{d\beta(t)}{dt}$, we can look at a point, $p$, subject to nonzero centripetal acceleration, $a_c(t)$, and zero tangential acceleration.
+To find $\frac{d\beta(t)}{dt}$, we can look at a point, $p$, subject to nonzero centripetal acceleration, and zero tangential acceleration.
 The change in $\bvec{v(t)}$ over an infinitesimal time, $dt$, is shown in Figure \ref{fig:theta-deriv} (the two vectors, $\bvec{v(t)}$ and $\paren{\bvec{v(t)}+\bvec{dv(t)}}$, are superimposed).
@@
 
-So
-
-\[
-\frac{d\abs{\theta(t)}}{dt} = \frac{d\abs{\phi(t)}}{dt} - \frac{a_c(t)}{v}
-\]
-
-The proof of the lemma in the case where $a_t(t)$ is nonzero is very similar, since the component of $\bvec{dv(t)}$ in the direction $\bhat{v(t)}$ is negligible compared to $v(t)$.
+The proof of the lemma in the case where $a_t(t)$ is nonzero is nearly identical, since the component of $\bvec{dv(t)}$ in the direction $\bhat{v}(t)$ is negligible compared to $v(t)$.
 

### 2013-10-11 path_theorems.tex
Finish checking intro and definitions. Made paper smaller. Added new line proof.

--- 2013-10-10 path_theorems.tex
@@
 Now that we have defined a coordinate system, we are ready to think about particle paths.
-Working in our modified polar coordinate system centered on $\bvec{X_2}$, it is clear, that our goal is achieved when $r(t) = 0$.
-Furthermore, it is important that $\theta(t)$ approach $0$ as $r(t) \to 0$, otherwise, the particle will pass by $\bvec{X_2}$.
+All particles in this section have bounded tangential acceleration, $\abs{a_t(t)} \le \bar{a_t}$, for some $\bar{a_t} \ge 0$.
 
-\begin{lemma} \label{lem:r-curve}
-  Given a particle, $p$, with constant speed and bounded centripetal acceleration, $\abs{a_c(t)} \le \bar{a_c}$, the minimum radius of curvature of the particle's trajectory is given by
+The simplest problem to tackle first is the fastest path from $\bvec{X_1}$ to $\bvec{X_2}$ when centripetal acceleration is unbounded, which means that a particle can change its direction of motion instantaneously.
+The following theorem makes this notion more precise.
 
-  \begin{equation}
-    R_{min} = \frac{\bar{v}^2}{\bar{a}_c}
-  \end{equation}
-  \end{lemma}
+\begin{theorem}
+  Let a particle $p$ have bounded tangential acceleration and $\theta(T_0) = \theta_0$.
+For all $\theta_f \in [0, \pi]$ and $\epsilon > 0$, there exists a valid path $\gamma(t)$, such that $\abs{\theta(T_0(\gamma) + \epsilon)} \to \theta_f$ as $\epsilon \to 0$.
+\end{theorem}
 
 \begin{proof}
-
-This comes directly from the definition of radius of curvature for a particle without any tangential acceleration:
+  Define a a particle's centripetal acceleration to be the following
 
   \[
-  R(t) = \frac{v(t)^2}{a_c(t)}
+      a_c(t) = v(t) \frac{\theta(T_0(\gamma)) - \theta(T_f(\gamma))}{\epsilon}
   \]
 
-and
+  Now, using Equation \ref{eq:theta-diff}
 
   \[
-  a_c(t) \le \bar{a}_c \to \frac{1}{a_c} \ge \frac{1}{\bar{a}_c}
+    \abs{\theta(T_0(\gamma) + \epsilon)} = \theta(T_0(\gamma)) + \int_{t'=T_0(\gamma)}^{T_0(\gamma)+\epsilon} \paren{\frac{d\abs{\phi(t')}}{dt} - \frac{\theta(T_0(\gamma)) - \theta_f}{\epsilon}} dt'
+  \]
+
+  Taking the limit as $\epsilon \to 0$
+
+  \[
+    \abs{\theta(T_0(\gamma) + \epsilon)} \to \theta_f \quad \text{as} \quad \epsilon \to 0
   \]
@@
 
-With Lemma \ref{lem:r-curve} in mind, the simplest problem to tackle first is the fastest path from $\bvec{X_1}$ to $\bvec{X_2}$ where centripetal acceleration is unbounded, which means that a particle can change its direction of motion to an arbitrary direction infinitely fast, $\frac{d\abs{\theta}}{dt}$ is unbounded.
-The following Theorem
+\begin{theorem}\label{thm:theta-zero}
+  Given a particle $p$, a path $\gamma_1$ from $\bvec{X_1}$ to $\bvec{X_2}$ is a fastest path if, for every other valid path $\gamma_2$ from $\bvec{X_1}$ to $\bvec{X_2}$, $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$.
 
-Now we will show that the fastest path between two points goes in a straight line if there is no initial speed.
-This will formalize the natural intuition that straight lines are the fastest path when there are no obstacles between the start and finish position.
-
-\begin{theorem}
-  \label{thm:line-proof}
-  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$ and no initial speed moving with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
+  Furthermore, if, at some time $t_s \ge T_0(\hat{\gamma})$ along a fastest path $\hat{\gamma}$, $\abs{\theta(t_s)} = 0$, then $\abs{\theta(t)} = 0$ for all $t \ge t_s$. 
 \end{theorem}
@@
 \begin{proof}
+  Referring back to Equation \ref{eq:r-diff}
 
-Without loss of generality, we can define a Cartesian coordinate system, where the origin is at $\bvec{X_1}$ and the positive x-axis passes through $\bvec{X_2}$.
+  \[r(t) = r(T_0) + \int_{t' = T_0}^{t} - v(t) \cos(\abs{\theta(t)})\]
+
+  Thus, if $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$, then $r_1(t) \le r_2(t)$, and $T_f(\gamma_1) \le T_f(\gamma_2)$, so $\gamma_1$ is a fastest path.
+
+  The second part of the theorem follows directly from the first part.
+\end{proof}
+
+Now we will formalize the natural intuition that straight lines are the fastest paths between points when centripetal acceleration is unbounded.
+
+\begin{theorem}\label{thm:line-proof}
+  Given a particle $p$ with initial position $\bvec{X_1}$, initial velocity $\bvec{v}(t)$, the fastest path $\hat{\gamma}(t)$ from $\bvec{X_1}$ to $\bvec{X_2}$ is the line segment from $\bvec{X_1}$ to $\bvec{X_2}$.
+\end{theorem}
+
+\begin{proof}
+  Because of Theorem \ref{thm:theta-zero}, there is a path, $\gamma_1(t)$, such that $\theta_1(t) = 0$ for $t \in (T_0(\gamma_1), T_f(\gamma_1)]$ \ref{thm:theta-zero}
+
+\end{proof}
+
+% \begin{theorem}\label{thm:line-proof}
+%   Given a particle with initial position $\bvec{X_1}$, initial velocity $\bvec{v}(t)$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ from $\bvec{X_1}$ to $\bvec{X_2}$ is the line segment from $\bvec{X_1}$ to $\bvec{X_2}$.
+% \end{theorem}
+
+% \begin{proof}
+
+% Without loss of generality, we can define a Cartesian coordinate system, where the origin is at $\bvec{X_1}$ and the positive x-axis passes through $\bvec{X_2}$.
 Let us say that the two points in our Cartesian coordinate system become $(0,0)$ and $(x_2, 0)$ respectively.
 
-Now let us examine the particle's motion in the $\bhat{x}$ direction. The speed of the particle is the following
-\begin{equation}
-  v_x(t) = \int_0^t a_x(t_1) dt_1
-\end{equation}
+% Now let us examine the particle's motion in the $\bhat{x}$ direction. The speed of the particle is the following
+% \begin{equation}
+%   v_x(t) = \int_0^t a_x(t_1) dt_1
+% \end{equation}
 
-To find the distance $l_x(t)$ traveled in the $\bhat{x}$ direction, we can use the relation:
-\begin{align}
-  l_x(t) &= \int_0^t v_x(t_2) dt_2 \\
-         &= \int_0^t \int_0^{t_1} a_x(t_1) dt_1 dt_2
-\end{align}
+% To find the distance $l_x(t)$ traveled in the $\bhat{x}$ direction, we can use the relation:
+% \begin{align}
+%   l_x(t) &= \int_0^t v_x(t_2) dt_2 \\
+%          &= \int_0^t \int_0^{t_1} a_x(t_1) dt_1 dt_2
+% \end{align}
 
-Recall that the tangential acceleration of the particle $p$ is bounded by $\bar{a}_{t}$. This means that $a_t(t) \leq \bar{a}_t$ for all $t$. Therefore, we see:
-\begin{align}
-d(t) &\leq \int_0^t \int_0^{t_2} \bar{a}_t dt_1 dt_2\\
-  &= \frac{\bar{a}_t t^2}{2}
-\end{align}
+% Recall that the tangential acceleration of the particle is bounded by $\bar{a}_{t}$. This means that $a_t(t) \leq \bar{a}_t$ for all $t$. Therefore, we see:
+% \begin{align}
+% d(t) &\leq \int_0^t \int_0^{t_2} \bar{a}_t dt_1 dt_2\\
+%   &= \frac{\bar{a}_t t^2}{2}
+% \end{align}
 
-Thus, in order to travel a distance of $l_x(T_f(\hat{\gamma})) = d' = d(\bvec{X_2}, \bvec{X_1})$, it needs to be the case that $T_f(\hat{\gamma}) \geq \sqrt{\frac{2 d'}{\bar{a}_t}}$.
+% Thus, in order to travel a distance of $l_x(T_f(\hat{\gamma})) = d' = d(\bvec{X_2}, \bvec{X_1})$, it needs to be the case that $T_f(\hat{\gamma}) \geq \sqrt{\frac{2 d'}{\bar{a}_t}}$.
 It is possible to travel from $\vec{X_2}$ to $\vec{X_1}$ in time $T_{min} = \sqrt{\frac{2 d'}{\bar{a}_t}}$ if and only if $a_t(t) = \bar{a}_t$ and $\theta(t) = 0$ for all $t \in [T_0(\gamma), T_{min}]$.
@@
 
-If the particle travels for time $t < T_{min}$, then it is impossible for the particle to reach $\vec{X_2}$ when starting at $\vec{X_1}$.
+% If the particle travels for time $t < T_{min}$, then it is impossible for the particle to reach $\vec{X_2}$ when starting at $\vec{X_1}$.
 This is because $p$ cannot reach $\vec{X}_2$ in the $x$ direction when $t < \sqrt{\frac{2 d'}{\bar{a}}}$ because it is impossible for $p$ to reach any point whose $x$-coordinate is $x_2$, so it is obviously impossible to reach $(x_2, 0) = \vec{X_2}$.
 
-Moreover, if there exists some time $t < T_{min}$ when $\theta(t) \neq 0$, then it is also impossible for the particle to reach $\vec{X_2}$ by time $T_{min}$.
+% Moreover, if there exists some time $t < T_{min}$ when $\theta(t) \neq 0$, then it is also impossible for the particle to reach $\vec{X_2}$ by time $T_{min}$.
 Suppose that there are two particles $p_1$ and $p_2$ both accelerating at $a_t(t) = \bar{a}_t$.
 Imagine $p_1$ satisfies $\theta_{p_1}(t) = 0$ for all $t$ and that $p_2$ satisfies $\theta_{p_2}(t) = 0$ except for times in some interval $[t_0, t_1]$, the particle $p_2$ sets a constant non-zero angle $\zeta_{p_2}(t) \neq 0$ with the $x$-axis for $t \in [t_0, t_1]$.
-Denote $d_{p}$ as the distance that is left to be travelled by particle $p$ between times $t_1$ and $T_{min}$.
+Denote $d_{p}$ as the distance that is left to be traveled by $p$ between times $t_1$ and $T_{min}$.
 We can find $d_{p_2}$ in terms of $d_{p_1}$ by using trigonometry:
 
-\begin{eqnarray}
-d_{p_2}^2 = d_{p_1}^2 + \left(\frac{\bar{a}_t (t_1 - t_0)^2}{2} \sin \zeta_{p_2} \right)^2
-\end{eqnarray}
+% \begin{eqnarray}
+% d_{p_2}^2 = d_{p_1}^2 + \left(\frac{\bar{a}_t (t_1 - t_0)^2}{2} \sin \zeta_{p_2} \right)^2
+% \end{eqnarray}
 
-Since $d_{p_2} \geq 0$ by being a distance, $\sin \zeta_{p_2} \neq 0$ by setting $\zeta_{p_2} > 0$, and $t_1 - t_0 > 0$, we know that $d_{p_2} > d_{p_1}$.
+% Since $d_{p_2} \geq 0$ by being a distance, $\sin \zeta_{p_2} \neq 0$ by setting $\zeta_{p_2} > 0$, and $t_1 - t_0 > 0$, we know that $d_{p_2} > d_{p_1}$.
 This means that at time $T_{min}$ when $p_1$ has reached its destination at $\Vec{X_2}$, particle $p_2$ still has $d_{p_2} - d_{p_1}$ distance left to travel.
@@
 
-This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$.
+% This means that the fastest path is completed in time $T_f(\hat{\gamma}) = \sqrt{\frac{2 x_2}{\bar{a}}}$.
 Let us examine the path taken by the point mass $p$ on this fastest path.
@@
 In other words, the point mass never turned on its way to reaching the destination point.
-The only way this could have happened is if it travelled along the $x$ axis in a straight line.
+The only way this could have happened is if it traveled along the $x$ axis in a straight line.
 
-Thus, we see that the fastest path is the straight line between $\vec{X_1}$ and $\vec{X_2}$.
-\end{proof}
+% Thus, we see that the fastest path is the straight line between $\vec{X_1}$ and $\vec{X_2}$.
+% \end{proof}
 
-We can also prove that this fastest path is unique without very much extra work.
+% We can also prove that this fastest path is unique without very much extra work.
 
@@
 \end{proof}
-
-% -----------------------------------------------------------------------------
-
-\section{Constant Speed Conditions}
-
-In the previous section, we made statements about fastest paths between two points when the initial velocity was set to zero.
-We saw that our physical intuition was confirmed and that a straight line was the fastest way to travel between two points.
-
-This is a simple case of the more general problem.
-We shall now examine fastest trajectories when the initial velocity is non-zero but when the centripetal acceleration is bounded.
-These conditions are much closer to physical reality, because it is often the case that you want to find a fastest path after you have already started moving.
-Moreover, Theorem \ref{thm:line-proof} assumed that centripetal acceleration was unbounded so that the particle could turn on a dime in any direction.
-This is not realistic because most physical objects have momentum when they are travelling at high speeds, making it much more difficult to turn.
-
-Assuming bounded acceleration makes the problem more interesting, and also much more difficult if we allow for tangential acceleration.
-In this section, we will eliminate tangential acceleration so that the particle will travel at constant speed with bounded acceleration.
-
-\begin{definition}
-  A particle with constant speed, is a particle with zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
-\end{definition}
-
-\begin{definition}
-  A particle with bounded centripetal acceleration is a particle with $\norm{a_c(t)} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
-\end{definition}
-
-Throughout the rest of this paper, all the particles we will deal with will have constant speed and bounded centripetal acceleration.
-
-To prove things about the fastest path of a particle under constant speed conditions, we shall make Conjecture \ref{conjecture:fastest-paths} about how fastest paths behave.
-
-\begin{conjecture}
-  \label{conjecture:fastest-paths}
-  Let particles $p_1, p_2$ have centripetal acceleration bounded by $\bar{a_c}$, constant speed $\bar{v}$, starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and final position $\bvec{X}_f$.
-Both particles move in a $X_f$ centered particle coordinate system.
-If $r_1(T_0) \leq r_2(T_0)$ and $\theta_1(T_0) < \theta_1(T_0)$, then $T_f(\hat{\gamma_1}) < T_f(\hat{\gamma_2})$.
-\end{conjecture}
-
-In words, this conjecture states that if a particle, $p_1$, is closer to the final position than another, $p_2$, and has a smaller $\theta(t)$, then its optimal path to the final position is shorter.
-The intuition behind this is that $p_2$ must travel a longer distance than $p_1$ to reach the final position, because it is further away.
-Furthermore, one could also imagine, that
-
-If this conjecture is true, then we can provide the strategy for obtaining the fastest path between two points $\bvec{X}_0$ and $\bvec{X}_f$.
-
-\begin{theorem}
-  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$.
-Let $p$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_0) > R_{min}$.
-The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
-  \label{thm:restricted-theta}
-\end{theorem}
-\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta_{p_1}(t)|$ for all times $t \in [T_0(\gamma_{p_1}), T_f(\gamma_{p_1})]$.
-We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.
-
-To do this, we will invoke a lemma which is closely related to Theorem \ref{thm:line-proof}:
-
-\begin{lemma}
-  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$ with constant speed conditions.
-If the end position is $\bvec{X}_f$ and $\theta(T_0(\gamma)) = 0$, then the fastest path $\bhat{\gamma_p}$ for particle $p$ follows the straight line between $\bvec{X}_0$ and $\bvec{X}_f$.
-\end{lemma}
-
-The lemma says that if a particle starts with initial velocity pointing directly towards $\bvec{X}_f$, then it is fastest to continue moving towards $\bvec{X}_f$ in a straight line.
-The proof of this lemma is very similar to the proof for Theorem \ref{thm:line-proof}, so we will omit it.
-
-This lemma does allow us to determine something crucial about the fastest path of $\bhat{\gamma_{p}}$.
-In particular, if the particle $p$ ever obtains $\theta_p(t_s) = 0$ at some time $t_s$, then it will be the case that $\theta_p(t') = 0$ for all $t'$ such that $t_s < t' < T_f(\bhat{\gamma_p})$.
-In words, if $\theta_p(t_s) = 0$ for any $t_s < T_f(\bhat{\gamma_p})$, then the particle will follow a straight line to $\bvec{X}_f$ after time $t_s$.
-Moreover that it must be the case that the particle reaches $\theta_p = 0$ at some time (or else the particle would never reach $\bvec{X}_f$).
-Thus, there must exist time $t_s$ where $\theta_p(t') = 0$ for all $t' > t_s$ in the fastest path $\bhat{\gamma_p}$.
-This is a necessary, but not sufficient condition for being a fastest path.
-
-To show that $\gamma_{p_1}$ truly is a fastest path, we must examine what happens before $t_s$, i.e.
-for all times $t'$ such that $T_0(\gamma_{p_1}) < t' < t_s$.
-This becomes the important period because we know that after $t_s$ (which necessarily occurs in a fastest path), the motion of the particle is in a straight line.
-
-For particle $p_1$, we know that $|a_c(t')| = \bar{a}_c$ for all $t' < t_s$ because $p_1$ is minimizing $|\theta_{p_1}(t)|$.
-Thus, we see that $p_1$ traces out an arc of a circle with radius $R_{min} = \frac{\bar{v}}{\bar{a}_c}$.
-
-Now let us introduce a particle $p_2$ with the same conditions as $p_1$ except that at some time $t_b < t_s$, $p_2$ will choose $a^{p_2}_c$ such that $|a^{p_2}_c| \neq \bar{a}_c$ so that $p_2$'s centripetal acceleration diverges from $p_1$'s centripetal acceleration.
-We shall show that $p_2$'s fastest path after this divergence is worse than $p_1$'s fastest path, which will allow us to conclude that deviations from $\gamma_{p_1}$ are subfastest.
-
-We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof.
-Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section.
-We can use equation \ref{eq:r-diff-2} to obtain the following:
-
-\begin{eqnarray}
-  \frac{d^2 r_{p_1}(t)}{d t^2} - \frac{d^2 r_{p_2}(t)}{d t^2} = - \sin(| \theta(t_b) |) \left( \bar{a}_c - a^{p_2}_c(t_b) \right) < 0
-\end{eqnarray}
-
-The inequality was obtained because $\bar{a}_c - a^{p_2}_c(t_b) > 0$.
-This directly implies that $r_{p_1}(t_b + \epsilon) < r_{p_2}(t_b + \epsilon)$ for some small $\epsilon > 0$.
-Therefore the distance left to travel for $p_1$ is less than the distance left for $p_2$ at $t_b + \epsilon$ time, i.e.
-$d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$.
-
-We can also use equation \ref{eq:theta-diff} to obtain the following for the difference in angles:
-\begin{eqnarray}
-  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_2} (t_b) |}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
-\end{eqnarray}
-
-Again, we used the fact that $\bar{a}_c - a^{p_2}_c(t_b) > 0$ to show the inequality. This implies that $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
-
-Now, we have satisfied the conditions of Conjecture \ref{conjecture:fastest-paths} since $d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$ and $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
-This implies that $T_f(\gamma_{p_1}) < T_f(\gamma_{p_2})$.
-Thus, the fastest path before $t_s$ must be to travel along $\gamma_{p_1}$.
-However, we know that the fastest path after $t_s$ is to travel along the straight line (which $\gamma_{p_1}$ does).
-Therefore, we see that $\gamma_{p_1} = \bhat{\gamma}_p$ is the fastest path.
-\qed

### 2013-10-11 particle_definitions.tex
Finish path theorems.

@@
 \begin{definition}
-  Given a particle, a fastest path $\hat{\gamma}(t)$ between two points, $\bvec{X_1}$ and $\bvec{X_2}$, is a valid path such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid paths, $\gamma(t)$, between $\bvec{X_1}$ and $\bvec{X_2}$.
+  Let $p$ be a particle with initial position $X_0$, a fastest path $\hat{\gamma}(t)$ to $\bvec{X_f}$, is a valid path such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid paths $\gamma(t)$ to $\bvec{X_f}$.
 \end{definition}

### 2013-10-11 path_theorems.tex
Finish path theorems.

@@
 
-The simplest problem to tackle first is the fastest path from $\bvec{X_1}$ to $\bvec{X_2}$ when centripetal acceleration is unbounded, which means that a particle can change its direction of motion instantaneously.
+The simplest problem to tackle first is the fastest path from $\bvec{X_0}$ to $\bvec{X_f}$ when centripetal acceleration is unbounded, which means that a particle can change its direction of motion instantaneously.
 The following theorem makes this notion more precise.
 
-\begin{theorem}
-  Let a particle $p$ have bounded tangential acceleration and $\theta(T_0) = \theta_0$.
+\begin{theorem}\label{thm:theta-choose}
+  Let $p$ be a particle with bounded tangential acceleration and $\theta(T_0) = \theta_0$.
 For all $\theta_f \in [0, \pi]$ and $\epsilon > 0$, there exists a valid path $\gamma(t)$, such that $\abs{\theta(T_0(\gamma) + \epsilon)} \to \theta_f$ as $\epsilon \to 0$.
@@
 
-\begin{theorem}\label{thm:theta-zero}
-  Given a particle $p$, a path $\gamma_1$ from $\bvec{X_1}$ to $\bvec{X_2}$ is a fastest path if, for every other valid path $\gamma_2$ from $\bvec{X_1}$ to $\bvec{X_2}$, $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$.
+\begin{theorem}\label{thm:theta-min}
+  Let $p$ be a particle with bounded tangential acceleration and initial position $X_0$.
+A path $\gamma_1$ to $\bvec{X_f}$ is a fastest path if, for every other valid path $\gamma_2$ to $\bvec{X_f}$, $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$.
+The fastest path is unique if all the inequalities are strict.
 
@@
   Thus, if $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$, then $r_1(t) \le r_2(t)$, and $T_f(\gamma_1) \le T_f(\gamma_2)$, so $\gamma_1$ is a fastest path.
+If all the inequalities are strict, then $T_f(\gamma_1) < T_f(\gamma_2)$, so every other path is longer, and thus $\gamma_1$ is the unique fastest path.
 
@@
 \begin{theorem}\label{thm:line-proof}
-  Given a particle $p$ with initial position $\bvec{X_1}$, initial velocity $\bvec{v}(t)$, the fastest path $\hat{\gamma}(t)$ from $\bvec{X_1}$ to $\bvec{X_2}$ is the line segment from $\bvec{X_1}$ to $\bvec{X_2}$.
+  Let $p$ be a particle with bounded tangential acceleration, initial position $\bvec{X_0}$, and initial velocity $\bvec{v}(t)$.
+The line segment from $\bvec{X_0}$ to $\bvec{X_f}$ with $a_c(t) = \bar{a_c}$ for all $t \in [T_0(\gamma_1), T_f(\gamma_1)]$ is a fastest path $\hat{\gamma}(t)$ to $\bvec{X_f}$.
+Furthermore, the fastest path for this system is unique.
 \end{theorem}
@@
 \begin{proof}
-  Because of Theorem \ref{thm:theta-zero}, there is a path, $\gamma_1(t)$, such that $\theta_1(t) = 0$ for $t \in (T_0(\gamma_1), T_f(\gamma_1)]$ \ref{thm:theta-zero}
+  Because of Theorem \ref{thm:theta-choose}, there is a valid path $\gamma_1(t)$, which has $\theta_1(t) = 0$ for $t \in (T_0(\gamma_1), T_f(\gamma_1)]$.
 
+  If we let $a_{t, 1}(t) = \bar{a_t}$ for all $t \in [T_0(\gamma_1), T_f(\gamma_1)]$, then $v_1(t) = \bar{a_t} t$, so for every other valid path $\gamma_2$
+
+  \begin{align*}
+    v_2(t)& = \int_{t'=T_0(\gamma_2(t))}^{t} a_{t, 2} dt\\
+    & \le \bar{a_t} t\\
+    &  \le v_1(t)
+  \end{align*}
+
+  Thus, all the conditions are satisfied for Theorem \ref{thm:theta-min}, so $\gamma_1(t)$ is a fastest path.
+The $\theta$ inequality is strict, so the fastest path is unique.
+Geometrically, since $\theta(t) = 0$, the path is the line segment from $\bvec{X_0}$ to $\bvec{X_f}$.
 \end{proof}
@@
 
-\begin{corollary}
-  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in Theorem \ref{thm:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
-\end{corollary}
-\proof We have already shown in Theorem \ref{thm:line-proof} that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them.
-Moreover, we showed that when travelling along the fastest path, the particle must have tangential acceleration of $\bar{a}_t$.
-Since we have starting position $\vec{X_1}$ and initial speed of $0$, the acceleration of the particle uniquely defines a path for the particle.
+% \begin{corollary}
+%   The fastest path given by  is unique.
+% \end{corollary}
+% \begin{proof}
+% Since we have starting position $\vec{X_0}$ and initial speed of $0$, the acceleration of the particle uniquely defines a path for the particle.
 
-There is only a single function of the acceleration $a(t) = \bar{a}_t$ which can be satisfied when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
-\qed
+% There is only a single function of the acceleration $a(t) = \bar{a}_t$ which can be satisfied when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
+% \end{proof}
 
-We can also investigate how the particle moves along a fastest path.
+% We can also investigate how the particle moves along a fastest path.
 In particular, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
-
-\begin{theorem}
-A 2-dimensional particle, $p$, traveling along a fastest path, $\hat{\gamma(t)}$, from $X_1$ to $X_2$ has $\frac{d\abs{\theta(t)}}{dt} \leq 0$ for all $t \in [0, T_{f, \gamma}]$, unless $\norm{X_1 - X_2} < 2 R_{min}$.
-\end{theorem}
-
-\begin{proof}
-Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma ????
-$\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$.
-Since all of the time derivatives in (\ref{eq:r-diff}) - (\ref{eq:theta-diff}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the fastest strategy should be the same, regardless of $r$.
-In other words, there can not be multiple cases for fastest strategies based on $r$.
-\end{proof}

### 2013-10-11 conclusion.tex
Almost done editing paper.

@@
 
-We also provided a conjecture that it is also optimal for a particle to orient itself towards the point as quickly as possible, in the case when centripetal acceleration is bounded.
-Assuming this conjecture to be true, we were able to draw more conclusions about optimal paths that can be directly used to calculate optimal paths.
+We posed the conjecture that it is also optimal for a particle to orient itself towards the point as quickly as possible, in the case when centripetal acceleration is bounded.
+Assuming this conjecture to be true, we were able to draw more conclusions about optimal paths under the new constraint of bounded centripetal acceleration.
 
@@
 
+Much of this paper was spend defining the terminology, coordinate system, and basic equation governing a particle.
+The intention was to build a strong framework for future research.
 Future work should first involve a rigorous proof of \ref{conj:optimal-position}.
@@
 
-To make the problem more general, one could extend the problem to include particles moving with varying speed.
+To make the problem more general, one could extend it to include particles moving with varying speed.
 Equations \ref{eq:r-diff} - \ref{eq:r-diff-2} still apply in this case, but the analysis is more complex.

### 2013-10-11 fixed_speed_theorems.tex
Almost done editing paper.

@@
 \begin{lemma} \label{lem:r-curve}
-  Given a particle with constant speed and bounded acceleration, the minimum radius of curvature of the particle's trajectory is given by
+  Given a particle with constant speed and bounded centripetal acceleration, the minimum radius of curvature of the particle's trajectory is given by
 
@@
 
-We must first make a conjecture about how fastest paths behave. Unfortunately, our research has not yet yielded a rigorous proof of the conjecture, but we will provide some intuition behind it.
+At the beginning of our paper we mentioned that there is a case when a particle is too close to the ending position and can't turn fast enought, so it ends up passing by it.
+We formalize this notion in the following lemma.
+
+\begin{lemma}\label{lem:too-close}
+  Let particle $p$ have constant speed, bounded centripetal acceleration, an initial angle $\theta_0$, starting position $\bvec{X_0}$, and ending position $\bvec{X_f}$.
+Every valid path where $\theta(t)$ is minimized for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$ has $d(\bvec{X}_0, \bvec{X}_f) \ge 2 R_{min} \cos\paren{\theta_0}$.
+\end{lemma}
+
+\begin{proof}
+
+  The following figure will help illustrate the theorem.
+
+  \includefig{valid_trajs.eps}{Valid and invalid final positions for a particle starting at position $X_0 = A$}{valid-traj}
+
+  Looking at Figure \ref{fig:valid-traj}, one should notice that if $X_f$ is any position inside the circle of radius $R_{min}$, such as point B, then the path is invalid.
+It is not possible to turn inside the circle, because the centripetal acceleration is bounded.
+Thus, C is the closest valid ending position.
+C is a distance $2 R_{min} \cos\paren{\theta_0}$ away from A.
+
+\end{proof}
+
+In order to continue, we must first make a conjecture about how fastest paths behave.
+Unfortunately, our research has not yet yielded a rigorous proof of this conjecture, so we will provide some intuition behind it.
 
 \begin{conjecture}\label{conj:optimal-position}
-  Given particles $p_1, p_2$ with starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and a final position $\bvec{X}_f$.
+  Let $p_1, p_2$ be particles with constant speed, bounded centripetal acceleration, starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and a final position $\bvec{X}_f$, such that $d(\bvec{X}_1, \bvec{X}_f), d(\bvec{X}_2, \bvec{X}_f) \ge 2 R_{min} \cos\paren{\theta_0}$.
 If $r_1(T_0) \leq r_2(T_0)$ and $\abs{\theta_1(T_0)} < \abs{\theta_1(T_0)}$, then $T_f(\hat{\gamma_1}) < T_f(\hat{\gamma_2})$.
@@
 
-In words, this conjecture states that a particle, $p_2$, further away from $X_f$ cannot overtake another point, $p_1$, that is closer to $X_f$, if $\theta_1(t) \le \theta_2(t)$.
+In words, this conjecture states that a particle $p_2$ that is further away from $X_f$ cannot overtake another particle $p_1$ that is closer to $X_f$, if $\theta_1(t) \le \theta_2(t)$.
 The intuition behind this is that $p_2$ must travel further than $p_1$ to reach $X_f$, because it is further away.
-Furthermore, one could also imagine, that if this conjecture were not true, then it would be fastest to move away from $X_f$, which seems intuitively wrong.
+Furthermore, one could also imagine, that if this conjecture were not true, then it would be fastest to move away from $X_f$ for some period of time, which seems intuitively wrong.
 
-Assuming that Conjecture \ref{conj:optimal-position} is true, we will move on to prove some theorems about fastest paths.
+The special case when $d(\bvec{X}_1, \bvec{X}_f), d(\bvec{X}_2, \bvec{X}_f) < (1/2) R_{min} \cos\paren{\theta_0}$ is omitted, because some special strategy will be needed in this situation.
+We leave this case as an open problem in our paper.
+
+Assuming that Conjecture \ref{conj:optimal-position} is true, we will move on to prove one final theorem about fastest paths.
 
 \begin{theorem}
-  Let particle $p$ have initial velocity $\bvec{v_0}$, starting position $\bvec{X}_0$, and ending position $\bvec{X}_f$, such that $d(\bvec{X}_0, \bvec{X}_f) > R_{min}$.
-The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
+  Let  $p$ be a particle with constant speed, bounded centripetal acceleration, initial angle $\theta_0$, starting position $\bvec{X}_0$, and ending position $\bvec{X}_f$, such that $d(\bvec{X}_0, \bvec{X}_f) \ge 2 R_{min} \cos\paren{\theta_0}$.
+The unique fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
   \label{thm:restricted-theta}
 \end{theorem}
-\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta_{p_1}(t)|$ for all times $t \in [T_0(\gamma_{p_1}), T_f(\gamma_{p_1})]$.
-We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.
+\begin{proof}
+Let $p_1$ be a particle whose path $\gamma_1$ minimizes $\abs{\theta_1(t)}$ for all times $t \in [T_0(\gamma_1), T_f(\gamma_1)]$. We shall show that $\gamma_1$ is the unique fastest path.
 
-This lemma does allow us to determine something crucial about the fastest path of $\bhat{\gamma_{p}}$.
-In particular, if the particle $p$ ever obtains $\theta_p(t_s) = 0$ at some time $t_s$, then it will be the case that $\theta_p(t') = 0$ for all $t'$ such that $t_s < t' < T_f(\bhat{\gamma_p})$.
-In words, if $\theta_p(t_s) = 0$ for any $t_s < T_f(\bhat{\gamma_p})$, then the particle will follow a straight line to $\bvec{X}_f$ after time $t_s$.
-Moreover that it must be the case that the particle reaches $\theta_p = 0$ at some time (or else the particle would never reach $\bvec{X}_f$).
-Thus, there must exist time $t_s$ where $\theta_p(t') = 0$ for all $t' > t_s$ in the fastest path $\bhat{\gamma_p}$.
-This is a necessary, but not sufficient condition for being a fastest path.
+Let $t_s$ be the smallest time such that $\theta_p(t) = 0$.
+From \ref{thm:theta-min}, we know that $\theta_p(t) = 0$ for $t \ge t_s$, so the particle moves in a straight line towards $X_f$ for $t \ge t_s$.
+To show that $\gamma_1(t)$ truly is a fastest path, we must examine what happens for $t < t_s$.
 
-To show that $\gamma_{p_1}$ truly is a fastest path, we must examine what happens before $t_s$, i.e.
-for all times $t'$ such that $T_0(\gamma_{p_1}) < t' < t_s$.
-This becomes the important period because we know that after $t_s$ (which necessarily occurs in a fastest path), the motion of the particle is in a straight line.
-
-For particle $p_1$, we know that $|a_c(t')| = \bar{a}_c$ for all $t' < t_s$ because $p_1$ is minimizing $|\theta_{p_1}(t)|$.
+We know that $\abs{a_{c,1}(t)} = \bar{a_c}$ for all $t < t_s$ because $p_1$ follows a path that minimizes $\abs{\theta_1(t)}$.
 Thus, we see that $p_1$ traces out an arc of a circle with radius $R_{min} = \frac{\bar{v}}{\bar{a}_c}$.
 
-Now let us introduce a particle $p_2$ with the same conditions as $p_1$ except that at some time $t_b < t_s$, $p_2$ will choose $a^{p_2}_c$ such that $|a^{p_2}_c| \neq \bar{a}_c$ so that $p_2$'s centripetal acceleration diverges from $p_1$'s centripetal acceleration.
-We shall show that $p_2$'s fastest path after this divergence is worse than $p_1$'s fastest path, which will allow us to conclude that deviations from $\gamma_{p_1}$ are subfastest.
+Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that at some time $t_b < t_s$, $p_2$ will choose $a_{c,2}$ such that $\abs{a_{c,2}} \neq \bar{a}_c$.
+We shall show that $\hat{\gamma_2(t)}$ after this divergence is strictly slower than $\hat{\gamma_1}$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.
 
-We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conj:optimal-position} to finish our proof.
+We can examine the difference in $r$ and $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conj:optimal-position} to finish our proof.
 Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section.
@@
 
-\begin{eqnarray}
-  \frac{d^2 r_{p_1}(t)}{d t^2} - \frac{d^2 r_{p_2}(t)}{d t^2} = - \sin(| \theta(t_b) |) \left( \bar{a}_c - a^{p_2}_c(t_b) \right) < 0
-\end{eqnarray}
+\begin{align*}
+  \frac{d^2 r_1(t)}{d t^2} - \frac{d^2 r_2(t)}{d t^2} = - \sin\paren{\abs{\theta(t_b)}} \paren{\bar{a}_c - a_{c,2}(t_b)}
+  & < 0
+\end{align*}
 
 The inequality was obtained because $\bar{a}_c - a^{p_2}_c(t_b) > 0$.
-This directly implies that $r_{p_1}(t_b + \epsilon) < r_{p_2}(t_b + \epsilon)$ for some small $\epsilon > 0$.
+This directly implies that $r_1(t_b + \epsilon) < r_2(t_b + \epsilon)$ for some small $\epsilon > 0$.
 Therefore the distance left to travel for $p_1$ is less than the distance left for $p_2$ at $t_b + \epsilon$ time, i.e.
-$d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$.
+$d(\gamma_1(t_b + \epsilon), \bvec{X}_f) < d(\gamma_2(t_b + \epsilon), \bvec{X}_f)$.
 
@@
 \begin{eqnarray}
-  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_2} (t_b) |}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
+  \frac{d \abs{\theta_1(t_b)}}{dt} - \frac{\abs{\theta_2 (t_b)}}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
 \end{eqnarray}
 
-Again, we used the fact that $\bar{a}_c - a^{p_2}_c(t_b) > 0$ to show the inequality. This implies that $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
+Again, we used the fact that $\bar{a}_c - a^{p_2}_c(t_b) > 0$ to show the inequality. This implies that $\theta_1(t_b + \epsilon) < \theta_2(t_b + \epsilon)$.
 
-Now, we have satisfied the conditions of Conjecture \ref{conj:optimal-position} since $d(\gamma_{p_1}(t_b + \epsilon), \bvec{X}_f) < d(\gamma_{p_2}(t_b + \epsilon), \bvec{X}_f)$ and $\theta_{p_1}(t_b + \epsilon) < \theta_{p_2}(t_b + \epsilon)$.
-This implies that $T_f(\gamma_{p_1}) < T_f(\gamma_{p_2})$.
-Thus, the fastest path before $t_s$ must be to travel along $\gamma_{p_1}$.
-However, we know that the fastest path after $t_s$ is to travel along the straight line (which $\gamma_{p_1}$ does).
-Therefore, we see that $\gamma_{p_1} = \bhat{\gamma}_p$ is the fastest path.
-\qed
+Now, we have satisfied the conditions of Conjecture \ref{conj:optimal-position} since $d(\gamma_1(t_b + \epsilon), \bvec{X}_f) < d(\gamma_2(t_b + \epsilon), \bvec{X}_f)$ and $\theta_1(t_b + \epsilon) < \theta_2(t_b + \epsilon)$.
+This implies that $T_f(\gamma_1) < T_f(\gamma_2)$.
+Thus, the fastest path before $t_s$ must be to travel along $\gamma_1$.
+However, we know that the fastest path after $t_s$ is to travel along the straight line (which $\gamma_1$ does).
+Therefore, we see that $\gamma_1 = \bhat{\gamma}_p$ is the fastest path.
+\end{proof}

### 2013-10-11 fixed_speed_theorems.tex
More changes to minimizing theta theorem.

@@
   Let particle $p$ have constant speed, bounded centripetal acceleration, an initial angle $\theta_0$, starting position $\bvec{X_0}$, and ending position $\bvec{X_f}$.
-Every valid path where $\theta(t)$ is minimized for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$ has $d(\bvec{X}_0, \bvec{X}_f) \ge 2 R_{min} \cos\paren{\theta_0}$.
+Every valid path where $\theta(t)$ is minimized for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$ has $d(\bvec{X_0}, \bvec{X_f}) \ge 2 R_{min} \cos\paren{\theta_0}$.
 \end{lemma}
@@
 
-  \includefig{valid_trajs.eps}{Valid and invalid final positions for a particle starting at position $X_0 = A$}{valid-traj}
+  \begin{figure}[H]
+    \begin{center}
+      \includegraphics[width=3.5in,height=2.5in,keepaspectratio]{valid_trajs.eps}
+    \end{center}
+  \vspace{-.2in} % corrects bad spacing
+  \caption{\label{fig:valid-traj}}
+  \end{figure}
 
-  Looking at Figure \ref{fig:valid-traj}, one should notice that if $X_f$ is any position inside the circle of radius $R_{min}$, such as point B, then the path is invalid.
+  One should notice that if $X_f$ is any position inside the circle of radius $R_{min}$, such as point B, then the path is invalid.
 It is not possible to turn inside the circle, because the centripetal acceleration is bounded.
@@
 \begin{conjecture}\label{conj:optimal-position}
-  Let $p_1, p_2$ be particles with constant speed, bounded centripetal acceleration, starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and a final position $\bvec{X}_f$, such that $d(\bvec{X}_1, \bvec{X}_f), d(\bvec{X}_2, \bvec{X}_f) \ge 2 R_{min} \cos\paren{\theta_0}$.
+  Let $p_1, p_2$ be particles with constant speed, bounded centripetal acceleration, starting positions $\bvec{X_1}, \bvec{X_2}$ respectively, and a final position $\bvec{X}_f$, such that $d(\bvec{X_1}, \bvec{X}_f), d(\bvec{X_2}, \bvec{X}_f) \ge 2 R_{min} \cos\paren{\theta_0}$.
 If $r_1(T_0) \leq r_2(T_0)$ and $\abs{\theta_1(T_0)} < \abs{\theta_1(T_0)}$, then $T_f(\hat{\gamma_1}) < T_f(\hat{\gamma_2})$.
@@
 
-The special case when $d(\bvec{X}_1, \bvec{X}_f), d(\bvec{X}_2, \bvec{X}_f) < (1/2) R_{min} \cos\paren{\theta_0}$ is omitted, because some special strategy will be needed in this situation.
+The special case when $d(\bvec{X_1}, \bvec{X}_f), d(\bvec{X_2}, \bvec{X}_f) < (1/2) R_{min} \cos\paren{\theta_0}$ is omitted, because some special strategy will be needed in this situation.
 We leave this case as an open problem in our paper.
@@
 
-We know that $\abs{a_{c,1}(t)} = \bar{a_c}$ for all $t < t_s$ because $p_1$ follows a path that minimizes $\abs{\theta_1(t)}$.
-Thus, we see that $p_1$ traces out an arc of a circle with radius $R_{min} = \frac{\bar{v}}{\bar{a}_c}$.
+We know that $\abs{a_{c,1}(t)} = \bar{a}_c$ for all $t < t_s$ because $p_1$ follows a path that minimizes $\abs{\theta_1(t)}$.
 
-Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that at some time $t_b < t_s$, $p_2$ will choose $a_{c,2}$ such that $\abs{a_{c,2}} \neq \bar{a}_c$.
-We shall show that $\hat{\gamma_2(t)}$ after this divergence is strictly slower than $\hat{\gamma_1}$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.
+Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that at some time $t_b < t_s$, $p_2$ will have $a_{c,2}(t) \neq \bar{a}_c$.
+We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after this divergence is strictly slower than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.
 
@@
 \begin{align*}
-  \frac{d^2 r_1(t)}{d t^2} - \frac{d^2 r_2(t)}{d t^2} = - \sin\paren{\abs{\theta(t_b)}} \paren{\bar{a}_c - a_{c,2}(t_b)}
+  \frac{d^2 r_1(t)}{d t^2} - \frac{d^2 r_2(t)}{d t^2}& = - \sin\paren{\abs{\theta(t_b)}} \paren{\bar{a}_c - a_{c,2}(t_b)}\\
   & < 0
@@
 
-The inequality was obtained because $\bar{a}_c - a^{p_2}_c(t_b) > 0$.
+The inequality was obtained because $\bar{a}_c - a_{c,2}(t_b) > 0$.
 This directly implies that $r_1(t_b + \epsilon) < r_2(t_b + \epsilon)$ for some small $\epsilon > 0$.
 Therefore the distance left to travel for $p_1$ is less than the distance left for $p_2$ at $t_b + \epsilon$ time, i.e.
-$d(\gamma_1(t_b + \epsilon), \bvec{X}_f) < d(\gamma_2(t_b + \epsilon), \bvec{X}_f)$.
+$d(\gamma_1(t_b + \epsilon), \bvec{X_f}) < d(\gamma_2(t_b + \epsilon), \bvec{X_f})$.
 
 We can also use equation \ref{eq:theta-diff} to obtain the following for the difference in angles:
-\begin{eqnarray}
-  \frac{d \abs{\theta_1(t_b)}}{dt} - \frac{\abs{\theta_2 (t_b)}}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
-\end{eqnarray}
+\begin{align*}
+  \frac{d \abs{\theta_1(t_b)}}{dt} - \frac{\abs{\theta_2 (t_b)}}{dt}& = - \frac{1}{v(t_b)} \paren{\bar{a}_c - a_{c,2}(t_b)}\\
+  & < 0
+\end{align*}
 
-Again, we used the fact that $\bar{a}_c - a^{p_2}_c(t_b) > 0$ to show the inequality. This implies that $\theta_1(t_b + \epsilon) < \theta_2(t_b + \epsilon)$.
+Again, we used the fact that $\bar{a}_c - a_{c,2}(t_b) > 0$ to show the inequality. This implies that $\abs{\theta_1(t_b + \epsilon)} < \abs{\theta_2(t_b + \epsilon)}$.
 
-Now, we have satisfied the conditions of Conjecture \ref{conj:optimal-position} since $d(\gamma_1(t_b + \epsilon), \bvec{X}_f) < d(\gamma_2(t_b + \epsilon), \bvec{X}_f)$ and $\theta_1(t_b + \epsilon) < \theta_2(t_b + \epsilon)$.
+Now, we have satisfied the conditions of Conjecture \ref{conj:optimal-position} since $d(\gamma_1(t_b + \epsilon), \bvec{X_f}) < d(\gamma_2(t_b + \epsilon), \bvec{X_f})$ and $\abs{\theta_1(t_b + \epsilon)} < \abs{\theta_2(t_b + \epsilon)}$.
 This implies that $T_f(\gamma_1) < T_f(\gamma_2)$.
@@
 However, we know that the fastest path after $t_s$ is to travel along the straight line (which $\gamma_1$ does).
-Therefore, we see that $\gamma_1 = \bhat{\gamma}_p$ is the fastest path.
+Therefore, we see that $\gamma_1$ is the unique fastest path.
 \end{proof}

### 2013-10-11 particle_definitions.tex
More changes to minimizing theta theorem.

@@
 
-\includefig{polar_param.eps}{A particle moving in a B centered particle coordinate system}{polar-param}
+\begin{figure}[H]
+    \begin{center}
+      \includegraphics[width=4in,height=3in,keepaspectratio]{polar_param.eps}
+    \end{center}
+  \vspace{-.2in} % corrects bad spacing
+  \caption{A particle moving in a B centered particle coordinate system.\label{fig:polar-param}}
+  \end{figure}
 
@@
 To find $\frac{d\beta(t)}{dt}$, we can look at a point, $p$, subject to nonzero centripetal acceleration, and zero tangential acceleration.
-The change in $\bvec{v(t)}$ over an infinitesimal time, $dt$, is shown in Figure \ref{fig:theta-deriv} (the two vectors, $\bvec{v(t)}$ and $\paren{\bvec{v(t)}+\bvec{dv(t)}}$, are superimposed).
+The change in $\bvec{v(t)}$ over an infinitesimal time, $dt$, is shown below (the two vectors, $\bvec{v(t)}$ and $\paren{\bvec{v(t)}+\bvec{dv(t)}}$, are superimposed).
 
-\includefig{theta_deriv.eps}{Tangential acceleration}{theta-deriv}
+\begin{figure}[H]
+    \begin{center}
+      \includegraphics[width=3.5in,height=2.5in,keepaspectratio]{theta_deriv.eps}
+    \end{center}
+  \vspace{-.2in} % corrects bad spacing
+  \caption{}
+\end{figure}
 

### 2013-10-11 fixed_speed_theorems.tex
Added paper.pdf.

@@
 
-Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that at some time $t_b < t_s$, $p_2$ will have $a_{c,2}(t) \neq \bar{a}_c$.
-We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after this divergence is strictly slower than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.
+Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that $a_{c,2}(t) < \bar{a}_c$ for some time interval $t \in [t_a, t_b], [t_a, t_b] < t_s$.
+We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after $t_b$ is strictly worse than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.
 
-We can examine the difference in $r$ and $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conj:optimal-position} to finish our proof.
+We will first prove that $r_1(t_b) < r_2(t_b)$ and $\theta_1(t_b) < \theta_2(t_b)$ and then invoke Conjecture \ref{conj:optimal-position} to finish our proof.
 Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section.

### 2013-10-11 particle_definitions.tex
Added paper.pdf.

@@
 
-  \[a_t(t) \coloneqq \frac{dv(t)}{dt}\]
+  \begin{equation}
+    a_t(t) \coloneqq \frac{dv(t)}{dt}
+  \end{equation}
 \end{definition}
@@
 
-The proof of the lemma in the case where $a_t(t)$ is nonzero is nearly identical, since the component of $\bvec{dv(t)}$ in the direction $\bhat{v}(t)$ is negligible compared to $v(t)$.
+The proof of the lemma in the case where $a_t(t)$ is nonzero is nearly identical, since the component of $\bvec{dv}(t)$ in the direction $\bhat{v}(t)$ is negligible compared to $v(t)$.
 

### 2013-10-11 fixed_speed_theorems.tex
Finished editing.

@@
 
-Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that $a_{c,2}(t) < \bar{a}_c$ for some time interval $t \in [t_a, t_b], [t_a, t_b] < t_s$.
+Now let us introduce a particle $p_2$ with the same conditions as $p_1$, but different centripetal acceleration.
+For some small enough $\epsilon > 0$, we can now find a time interval $t \in [t_b-\epsilon, t_b+\epsilon]$ where that $a_{c,2}(t) < a_{c,1}$.
 We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after $t_b$ is strictly worse than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.
 
-We will first prove that $r_1(t_b) < r_2(t_b)$ and $\theta_1(t_b) < \theta_2(t_b)$ and then invoke Conjecture \ref{conj:optimal-position} to finish our proof.
-Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section.
-We can use equation \ref{eq:r-diff-2} to obtain the following:
+Because $\gamma_1$ minimizes $\abs{\theta(t)}$, $\abs{\theta_1(t_b)} \le \abs{\theta_2(t_b)}$.
+If $t_b > t_s$, then from \ref{thm:theta-min} we know that $\gamma_2(t)$ is worse than $\gamma_1$.
+If $t_b \le t_s$, we will prove that $r_1(t_b) < r_2(t_b)$.
+
+Looking at Equation \ref{eq:r-diff}
 
 \begin{align*}
-  \frac{d^2 r_1(t)}{d t^2} - \frac{d^2 r_2(t)}{d t^2}& = - \sin\paren{\abs{\theta(t_b)}} \paren{\bar{a}_c - a_{c,2}(t_b)}\\
-  & < 0
+  r(t_b)& = r(t_b-\epsilon) - \bar{v} \int_{t' = T_0}^{t} \cos(\abs{\theta(t')}) dt'
 \end{align*}
 
-The inequality was obtained because $\bar{a}_c - a_{c,2}(t_b) > 0$.
-This directly implies that $r_1(t_b + \epsilon) < r_2(t_b + \epsilon)$ for some small $\epsilon > 0$.
-Therefore the distance left to travel for $p_1$ is less than the distance left for $p_2$ at $t_b + \epsilon$ time, i.e.
-$d(\gamma_1(t_b + \epsilon), \bvec{X_f}) < d(\gamma_2(t_b + \epsilon), \bvec{X_f})$.
-
-We can also use equation \ref{eq:theta-diff} to obtain the following for the difference in angles:
-\begin{align*}
-  \frac{d \abs{\theta_1(t_b)}}{dt} - \frac{\abs{\theta_2 (t_b)}}{dt}& = - \frac{1}{v(t_b)} \paren{\bar{a}_c - a_{c,2}(t_b)}\\
-  & < 0
-\end{align*}
-
-Again, we used the fact that $\bar{a}_c - a_{c,2}(t_b) > 0$ to show the inequality. This implies that $\abs{\theta_1(t_b + \epsilon)} < \abs{\theta_2(t_b + \epsilon)}$.
-
-Now, we have satisfied the conditions of Conjecture \ref{conj:optimal-position} since $d(\gamma_1(t_b + \epsilon), \bvec{X_f}) < d(\gamma_2(t_b + \epsilon), \bvec{X_f})$ and $\abs{\theta_1(t_b + \epsilon)} < \abs{\theta_2(t_b + \epsilon)}$.
-This implies that $T_f(\gamma_1) < T_f(\gamma_2)$.
-Thus, the fastest path before $t_s$ must be to travel along $\gamma_1$.
-However, we know that the fastest path after $t_s$ is to travel along the straight line (which $\gamma_1$ does).
-Therefore, we see that $\gamma_1$ is the unique fastest path.
+Since $\cos(\abs{\theta_1(t)}) \ge \cos(\abs{\theta_2(t)})$, $r_1(t_b) \le r_2(t_b)$, so we can invoke Conjecture \ref{conj:optimal-position} to show that $\gamma_1$ is a fastest path which finishes the proof.
 \end{proof}

### 2013-10-11 fixed_speed_theorems.tex
Fix final thm.

@@
 
-Looking at Equation \ref{eq:r-diff}
+Looking at Equation \ref{eq:theta-diff}
 
 \begin{align*}
-  r(t_b)& = r(t_b-\epsilon) - \bar{v} \int_{t' = T_0}^{t} \cos(\abs{\theta(t')}) dt'
+  \abs{\theta(t_b)}& = \abs{\theta(t_b - \epsilon)} + \int_{t' = t_b-\epsilon}^{t_b} \paren{\frac{\bar{v}}{r(t)} \sin(\abs{\theta(t)}) - \frac{a_c(t)}{\bar{v}}} dt'\\
+  \intertext{Now we can find the difference of the two $\theta$'s and take the limit as $\epsilon \to 0$}
+  \abs{\theta_2(t_b)} - \abs{\theta_1(t_b)}& \to \int_{t' = t_b-\epsilon}^{t_b} - \frac{a_{c,2}(t) - a_{c,1}(t)}{\bar{v}} dt' \quad \text{as} \quad \epsilon \to 0\\
+  & \ge 0 \quad \text{as} \quad \epsilon \to 0
 \end{align*}
 
-Since $\cos(\abs{\theta_1(t)}) \ge \cos(\abs{\theta_2(t)})$, $r_1(t_b) \le r_2(t_b)$, so we can invoke Conjecture \ref{conj:optimal-position} to show that $\gamma_1$ is a fastest path which finishes the proof.
+Furthermore,
+
+\begin{align}
+  r(t_b)& = r(t_b - \epsilon) + \int_{t' = t_b - \epsilon}^{t_b} - v(t') \cos(\abs{\theta(t')}) dt'\\
+  \intertext{Taking the limit of the difference again}
+  r_2(t_b) - r_1(t_b)& \to \int_{t' = t_b - \epsilon}^{t_b} - v(t') \paren{\cos(\abs{\theta_2(t')}) - \cos(\abs{\theta_1(t')})} dt' \quad \text{as} \quad \epsilon \to 0\\
+  \intertext{We know that $\theta_2(t_b) \ge \theta_1(t_b)$ as $\epsilon \to 0$, so}
+  r_2(t_b) - r_1(t_b)& \ge 0 \quad \text{as} \quad \epsilon \to 0
+\end{align}
+
+Now we can invoke Conjecture \ref{conj:optimal-position} to show that $\gamma_1$ is a faster path than $\gamma_2$, which finishes the proof.
 \end{proof}

### 2013-10-11 fixed_speed_theorems.tex
Edits

@@
 \]
-\end{proof}
-
-At the beginning of our paper we mentioned that there is a case when a particle is too close to the ending position and can't turn fast enought, so it ends up passing by it.
-We formalize this notion in the following lemma.
-
-\begin{lemma}\label{lem:too-close}
-  Let particle $p$ have constant speed, bounded centripetal acceleration, an initial angle $\theta_0$, starting position $\bvec{X_0}$, and ending position $\bvec{X_f}$.
-Every valid path where $\theta(t)$ is minimized for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$ has $d(\bvec{X_0}, \bvec{X_f}) \ge 2 R_{min} \cos\paren{\theta_0}$.
-\end{lemma}
-
-\begin{proof}
-
-  The following figure will help illustrate the theorem.
-
-  \begin{figure}[H]
-    \begin{center}
-      \includegraphics[width=3.5in,height=2.5in,keepaspectratio]{valid_trajs.eps}
-    \end{center}
-  \vspace{-.2in} % corrects bad spacing
-  \caption{\label{fig:valid-traj}}
-  \end{figure}
-
-  One should notice that if $X_f$ is any position inside the circle of radius $R_{min}$, such as point B, then the path is invalid.
-It is not possible to turn inside the circle, because the centripetal acceleration is bounded.
-Thus, C is the closest valid ending position.
-C is a distance $2 R_{min} \cos\paren{\theta_0}$ away from A.
-
 \end{proof}
@@
 
-Now let us introduce a particle $p_2$ with the same conditions as $p_1$, but different centripetal acceleration.
-For some small enough $\epsilon > 0$, we can now find a time interval $t \in [t_b-\epsilon, t_b+\epsilon]$ where that $a_{c,2}(t) < a_{c,1}$.
+Now let us introduce a particle $p_2$ with the same conditions as $p_1$, but different centripetal acceleration at some time $t_b$.
+Suppose for some small $\epsilon > 0$, we have a time interval $t \in [t_b-\epsilon, t_b+\epsilon]$ where that $a_{c,2}(t) < a_{c,1}$.
 We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after $t_b$ is strictly worse than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.
@@
 
-Looking at Equation \ref{eq:theta-diff}
+Looking at Equation \ref{eq:theta-diff} and recalling that $a_{c,2}(t_b) - a_{c,1}(t_b) < 0$.
 

### 2013-10-11 introduction.tex
Edits

@@
 The problem of finding fastest paths between two points (let's call them A and B) is interesting because many attributes of a fastest path are intuitively obvious, but rigorously proving them is much more difficult.
-One's first assumption would be that the fastest path between A and B, would be to travel in a straight line from A to B.
-This would be true in the simple case where the turning rate is not constrained, but it is not true in the general case when a particle has a constrained turning rate and starts with some nonzero velocity not directed towards B.
-In the general case, it is easier to turn towards B, the further one is away from it, so there is the possibility that it would be fastest for the particle to turn away from B for a short period of time, so that it can then turn towards it more quickly.
-In fact, if the particle is too close to B, it won't have time to turn towards it, and will pass by B.
+One's first assumption would be that the fastest path between A and B would be to travel in a straight line from A to B.
+This would be true in the simple case where the turning rate is not constrained, but it is not true in the general case when a particle has a constrained turning rate and starts with some nonzero velocity which is not directed towards B.
+In the general case, it is easier to turn towards B the further one is away from it.
 
@@
 
-Given a particle in $\R^2$ starts at a position A in with an initial velocity, what is the path in for the particle to take to reach a final position B, such that the time spent traveling from A to B is minimized.
+Our problem is the following: given a particle in $\R^2$ starting at position A with some initial velocity, what is the path that the particle must take to reach a final position B such that the time spent traveling from A to B is minimized?
 The particle can have restrictions on its position, velocity, and acceleration.

### 2013-10-11 path_theorems.tex
Added paper.pdf.
Fix final thm.
Edits

@@
 A path $\gamma_1$ to $\bvec{X_f}$ is a fastest path if, for every other valid path $\gamma_2$ to $\bvec{X_f}$, $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$.
-The fastest path is unique if all the inequalities are strict.
+The fastest path is unique if one of the inequalities is strict.
 
@@
 
-  \[r(t) = r(T_0) + \int_{t' = T_0}^{t} - v(t) \cos(\abs{\theta(t)})\]
+  \[r(t) = r(T_0) + \int_{t' = T_0}^{t} - v(t') \cos(\abs{\theta(t')}) dt'\]
 
-  Thus, if $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$, then $r_1(t) \le r_2(t)$, and $T_f(\gamma_1) \le T_f(\gamma_2)$, so $\gamma_1$ is a fastest path.
+  Thus, if $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$, then $r_1(t) \le r_2(t)$.
+Because the distance that needs to be traveled by $p_2$ is greater at time any $t$, and because $v_1(t) \le v_2(t)$, then we know that $T_f(\gamma_1) \le T_f(\gamma_2)$.
+Therefore $\gamma_1$ is a fastest path.
 If all the inequalities are strict, then $T_f(\gamma_1) < T_f(\gamma_2)$, so every other path is longer, and thus $\gamma_1$ is the unique fastest path.
@@
   \begin{align*}
-    v_2(t)& = \int_{t'=T_0(\gamma_2(t))}^{t} a_{t, 2} dt\\
+    v_2(t)& = \int_{t'=T_0(\gamma_2}^{t} a_{t, 2}(t') dt'\\
     & \le \bar{a_t} t\\
